### 2017-05-18 paper-main.tex
convert UHI text into ITAT style

\documentclass{itatnew}

\usepackage{paralist} % inparaenum support
\usepackage{varioref} % added by Viliam for \vref
\usepackage{xcolor} % added by Viliam for \textcolor

\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{textcomp} % used for degrees celsius
\usepackage{booktabs}
\usepackage[british]{babel}

% ==========================================
% Support for \FOCAL{R}{M}{op} (by Viliam)
% ==========================================
\newcommand{\FOCALMMODE}[3]{
  #1{\stackrel{\mathtt{#3}}{\circ}}#2
}
\newcommand{\FOCAL}[3]{
  \ifmmode
  \FOCALMMODE{#1}{#2}{#3}
  \else
  \begin{math}\FOCALMMODE{#1}{#2}{#3}\end{math}%
  \fi
}
% ==========================================

\begin{document}

\title{Stable Hot Spot Analysis (Draft)}

\author{
  Marc Gassenschmidt \and
  Viliam Simko  \and
  Julian Bruns
  \\
  \email{todo@fzi.de},
  \email{simko@fzi.de},
  \email{bruns@fzi.de}
}

\institute{
  FZI Forschungszentrum Informatik\\
  am Karlsruher Institut f\"ur Technologie\\
  76131, Haid-und-Neu-Str. 10-14\\
  Karlsruhe, Germany
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
  The Urban Heat Island (UHI) effect describes the difference in temperature
  between cities and their surrounding areas. However, temperature differences
  within city limits, so-called Intra Urban Heat Islands (IUHI), affect human
  health as well as the energy demands in local areas. In order to anticipate
  and mitigate the resulting impacts of heat trough urban planing, a method to
  reliably detect these local areas is needed. Existing methods from the
  geo-statistical field can identify those areas. But these statistics can be
  unstable in their detection of hot spots, in particular for temperature hot
  spots, depending on their parametrization. In this paper, we propose a
  modification of the well known Getis-Ord ($G^*$) statistic, called the
  \emph{Focal $G^*$} statistic. This modification replaces the computation of
  the global mean and standard deviation with their focal counterparts. We
  define the stability of our approach by introducing a stability metric called
  \emph{Stability of Hot spot} (SoH), which requires that hot spots have to be
  in similar areas regardless of the chosen weight matrix. The results are
  evaluated on real world temperature data for the city of Karlsruhe.
\end{abstract}

\section{Introduction}

For urban city planers, the detection of Intra Urban Heat Islands (IUHI) is of
high interest as high temperatures impact energy
consumption~\cite{Hassid.2001.Electricity_UHI} as well as human
health~\cite{Ye.2012}. The effect that the temperatures between an urban area
and its surroundings differ, called the Urban Heat Island effect
\cite{Oke1982energetic}, has long been the subject of research. Most historical
studies conducted had to rely on few, fixed weather stations, low
spatio-temporal resolution of satellites or small-scale mobile measurements by
car, preventing the modelling of finer-grained temperature differences within an
urban area itself. With the advent of inexpensive mobile sensors, higher
spatio-temporal resolution of satellites and volunteered geographic
informations, to name just a small selection, it is now feasible to focus on the
temperature differences in a city as the subject of interest.

Hot spot analysis is a tool which is suited to detect such areas. In the context
of IUHI we can detect those areas where the temperature is significantly
different from the mean temperature of our study area. This enables us to
identify points of interest without the need to pre-process the data.

Although existing methods are independent of concrete values, their results are
highly dependent on the size of the study area and their parametrization such as
the weight matrix in the case of the Getis-Ord statistic. This dependency can
lead to unstable hot spots, where the identified hot spots only appear in one 
specific combination of parameter. The generalization of insights gained from
unstable hot spots is suboptimal. A city planer who has to rely on those
insights will most likely prioritize the wrong area to invest his limited
resources. Given the increasing importance to detect extreme local temperatures
in cites, see e.g. \cite{Hansen.2010, GRL:GRL22143, department2014world}, means
to reliably detect and mitigate the effect of temperature extremes in a
proactive fashion are needed.

To solve this problem, we first propose a metric to measure the stability of a
hot spot analysis regarding its parametrization of the weight matrix called the
\emph{Stability of Hot spot} (SoH). This metric measures whether a hot spot
found for a given weight matrix is carried over to the found hot spots with a
different weight matrix. This enables us to quantify the stability of any hot
spot analysis. Based on our reasoning behind the instability of existing hot
spot analyses, we propose a modification of the well known Getis-Ord statistic
($G^*$): the \emph{Focal Getis-Ord} statistic (Focal $G^*$). Instead of the
global mean and variance used by $G^*$, it only uses the mean and variance of a
predefined region around each point. This region is a subset of the whole study
area. By doing this, the instability is contained within a smaller region and
thereby independent of the parametrization of the weight matrix. We test our
stability metric as well as this modified approach on data given by two
temperature snapshots of the city of Karlsruhe taken in 2008.

\section{Related Work}

\subsection{Urban Heat Island}

The scientific interest in the phenomena of UHI is well established. One of the
earliest known overviews of the scientific literature of the city climates is
given by Albert Kratzer 1937~\cite{dieckmann1938stadtklima}. At that time
already, relations between temperature, humidity, human heat fluxes and air
pollution are investigated.

A more recent overview comes from Arnfied~\cite{Arnfield.2003}. The focus here
lies on the development in the field of climatology between 1980 and 2003. In
particular, the rise of simulations and modelling is lauded, but, to quote
Arnfield, ``simple methods are still needed to estimate UHI intensity within
urban areas''~\cite{Arnfield.2003}.

Schwarz~et~al.~\cite{Schwarz.2011} compare 11 different Surface Urban Heat
Island (SUHI) indicators on a dataset of 263 European cities with monthly mean
temperatures. They show that the selection of indicators is important for the
detection of UHI due to possible instabilities of each indicator.

A more recent development is the focus on IUHI. The definition for IUHI comes
from Martin et al.~\cite{Martin.2015}. By defining thresholds with respect to
spatial reference, these enable the detection of hot spots in a city, which
Martin et al. call surface intra-UHI. This boils down to five steps, i.e.
essentially a comparison of absolute deviation from the mean temperature given a
survey area. The results can then be used to detect areas of interest in a city
and potentially trigger alerts for a much finer spatial granularity.

While the proposition to examine urban micro-climates can be traced back as far
as 1937~\cite{dieckmann1938stadtklima}, we have found only few works in this
field. Schwarz et al.~\cite{Schwarz.2012} state that the reduction of an UHI to
a single value for a whole city is questionable regarding its explanatory power.
But also that there is currently no other way to quantify the differences
amongst cities.

The difficulties presented by comparing the UHI values between different cities
are the topic of Stewart and Oke~\cite{Stewart2012}. They propose the use of
local climate zones (LCZ) to standardise the methodology and terminology.

Another area where urbanizations affects the temperature distribution are
subsurface temperatures. Menberg et al.~\cite{Menberg.2013} look into the
distribution of the temperatures below the surface -- the subsurface
temperature. They find local hot spots of heat with deviations of up to
+20\textdegree{K} in some areas related to local heat sources.

\subsection{Hot Spot Analysis}

The goal of an analysis of temperatures in a city is to find the most
interesting, significant areas: Hot spots~\cite{Martin.2015}. This goal is
similar to the hot spot analysis in the field of geo-statistics. One of the most
fundamental approach is Moran´s I~\cite{MoranI}. There it is tested whether or
not a spatial dependency exists. This gives the information on global
dependencies in a data set. Upon this hypothesis test several geo-statistical
tests are based. The most well known are the Getis-Ord statistic~\cite{Ord.1995}
and LISA~\cite{Anselin.1995}. In both cases the general, the global statistic of
Moran´s I is applied in a local context. The goal is to detect not only global
values, but instead to focus on local hot spots and to measure the significance
of those local areas.

The local Getis-Ord statistic~\cite{Ord.1995} is defined as follow:
\begin{definition}[Getis-Ord $G^*_i$ statistic] \label{def:Gstar}
  Assuming a study area with $n$ measurements, let $X = [x_1, \ldots,
  x_n]$ be all values measured in this area. Let $w_{i,j}$ be a spatial weight
  between two points $i$ and $j$ for all $i,j \in \{ 1, \ldots, n\}$. The 
  Getis-Ord $G^*_i$ statistic is given as:
  \begin{equation} \label{eq:Gstar}
  G^*_i = \frac{
    \sum_{j=1}^{n}w_{i,j}x_j - \bar{X}\sum_{j=1}^{n}w_{i,j}
  }{
  S \sqrt{
    \frac{
      n \sum_{j=1}^{n}w_{i,j}^2 - (\sum_{j=1}^{n}w_{i,j})^2
    }{n-1}
  }
}
\end{equation}
where:
\begin{itemize}
  \item $\bar{X}$ is the mean of all measurements,
  \item $S$ is the standard deviation of all measurements.
\end{itemize}
\end{definition}

As it is known, this statistic creates a z-score, which denotes the significance
of an area in relation to its surrounding areas.

LISA is quite similar, as it is the local statistic for Moran's
I~\cite{Anselin.1995}, but the z-score has a different meaning. Apart from
$G^*_i$, LISA does not distinguish between cold spots and hot spots as it
assigns high z-score to most similar areas.

Two other well known method are the kernel density estimation~\cite{KDE_Hotspot}
and kriging~\cite{Kriging_Hotspot}. These do not provide significance levels.
Instead, they estimate the values for each location based on the rest of the
study area and a threshold value \cite{Thakali2015}. Therefore, results for
different areas are not comparable, especially in the case of differing
temperature distributions. Kriging was developed for the estimation of ore
deposits~\cite{krige1951statistical}, but today, applications for geo-temporal
forecasts with this approach can be found, e.g. for the city of
Zurich.~\footnote{https://r-video-tutorial.blogspot.de/2015/08/spatio-temporal-kriging-in-r.html}

All of the aforementioned methods use weights between pairs of points, usually
based on their geographical distance. However, in real applications, the points
are aggregated into rasters and the weights are represented as a weight matrix.
This allows for expressing the algorithms in terms of map algebra operations, a
term first coined by Dana~Tomlin~\cite{Tomlin1990} and computed in a distributed
fashion (e.g. using Geotrellis framework running on
Apache~Spark~\cite{github:Geotrellis}).

In this work, we focus on the Getis-Ord statistic applied to rasters of land
surface temperature. This enables us to transform the formula for the $G^*$
statistic into a computationally more efficient form. We then propose a
modification of the standard $G^*$ statistics, to increase the stability of the
hot spots found.

\section{Stability of Hot Spot Analysis}
\label{sec:Metric}

Existing methods to determine hot spots are dependent on the parametrization of
the weight matrix as well as on the size of the study area.

Consider the real-world example depicted in Fig.~\ref{fig:TempMaps}. The
temperature map of a morning thermal flight dataset (Fig.~\ref{fig:TempMaps:a})
has been processed using $G^*$.

\begin{figure}[htp]
  \begin{subfigure}{1\linewidth}
    \caption{Morning temperatures}
    \includegraphics[width=\linewidth]{images/hotspot-rawtemp-1}
    \label{fig:TempMaps:a}
  \end{subfigure}

  \caption{
    Karlsruhe city center.
    Selected area of $2.4{\times}1.4\,km$.
    Pixel size $5{\times}5\,m$.
  }
  \label{fig:TempMaps}
\end{figure}

% Bild besteht aus orginal, weight matrix a und weight matrix b
As we can see, hot spots are oftentimes disappearing or appearing unrelated to
previously found hot spots. While these computations indeed show hot spots and
the results are correct, they lack stability.

For a data analyst, when exploring the data interactively by choosing different
filter sizes (in form matrices), it is important that the hot spot's position
and size changes in a predictable manner. This intuition is the basis for our
stability metric.

We define a hot spot found in comparably more coarse resolutions as
\emph{parent} (larger weight matrix) and in finer resolutions as \emph{child}
(smaller weight matrix). To be stable, one assumes that every parent has at
least one child and that each child has one parent. For a perfectly stable
interaction, it can be easily seen that the connection between parent and child
is a injective function and between child and parent a surjective function. To
measure the closeness of connection, we propose a metric called the
\emph{Stability of Hot spot} (SoH). It measures the deviation from a perfectly
stable transformation of resolutions.

%TODO: what about the other direction?
In its downward property (from parent to child, injective) it is defined as:
\begin{equation}
\label{eq:SoH-down}
SoH^\downarrow = \frac{ParentsWithChildNodes}{Parents} = \frac{|Parents \cap 
Children|}{|Parents|}
\end{equation}
And for its upward property (from child to parent, surjective):
\begin{equation}
\label{eq:SoH-up}
SoH^\uparrow = \frac{ChildrenWithParent}{Children} = 1 - \frac{|Children - 
Parents|}{|Children|}
\end{equation}
where $ParentsWithChildNodes$ is the number of parents that have at least one 
\emph{child}, $Parents$ is the total number of \emph{parent}, 
$ChildrenWithParent$ is the number of children and $Children$ as the total 
number of children.
The SoH is defined for a range between 0 and 1, where 1 represents a perfectly 
stable transformation while 0 would be a transformation with no stability at 
all.

\section{Focal Getis-Ord} \label{sec:FocalGetisOrd}

\subsection{Dataset}

% extent
The two datasets (morning and evening flights) depicted in
Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} were
obtained from a thermal flight over the city of Karlsruhe on 26.09.2008 at
6:30--7:45 and 20:00--21:30. The flights were executed by the
Nachbarschaftsverband
Karlsruhe\footnote{http://www.nachbarschaftsverband-karlsruhe.de/}. A single
pixel in the raster represents an area of approximately $5{\times}5m$. The whole
dataset of size $35{\times}25\,km$ was cropped into the inner city area of
$2.4{\times}1.4\,km$. % temp range
The temperatures in our dataset range from -1.7°C to 18.3°C.
% missing values = NAs
Missing values in the dataset were interpolated using a focal median function
with a square matrix of 11x11 pixels, mainly for speeding up further
computations and to avoid special handling of NA values.

\subsection{Method}

In the following text, we use the notation \FOCAL{R}{M}{op} to denote
a focal operation $op$ applied on a raster $R$ with a focal window determined 
by a
matrix $M$. This is rougly eqivalent to a command \verb|focal(x=R, w=M, fun=op)|
from package \emph{raster} in the R programming language \cite{cran:raster}.

\begin{definition}[$G^*$ function on rasters]
  \label{def:GenericGetisOrdFunc}

  The function $G^*$ can be expressed as a raster operation:

  \begin{displaymath}
  G^*(R, W, st) =
  \frac{
    \FOCAL{R}{W}{sum} - M*\sum_{w \in W}{w}
  }{
  S \sqrt{
    \frac{
      N*\sum_{w \in W}{w^2} - (\sum_{w \in W}{w})^2
    }{
    N - 1
  }
}
}
\end{displaymath}
\noindent where:
\begin{itemize}

  \item $R$ is the input raster.

  \item $W$ is a weight matrix of values between 0 and 1.

  \item $st = (N, M, S)$ is a parametrization specific to a particular version
  of the $G^*$ function. (Def.\vref{def:StdGetisOrdVersion} and
  \vref{def:FocalGetisOrdVersion}).

\end{itemize}
\end{definition}

\begin{definition}[Standard $G^*$ parametrization]
  \label{def:StdGetisOrdVersion}

  Computes the parametrization $st$ as global statistics for all pixels in the
  raster $R$:

  \begin{itemize}
    \item $N$ represents the number of all pixels in $R$.
    \item $M$ represents the global mean of $R$.
    \item $S$ represents the global standard deviation of all pixels in $R$.
  \end{itemize}
\end{definition}

\begin{definition}[Focal $G^*$ parametrization]
  \label{def:FocalGetisOrdVersion}

  Let $F$ be a boolean matrix such that: $all(dim(F) \geq dim(W))$.
  This version uses focal operations to compute per-pixel statistics given by 
  the focal neighbourhood $F$ as follows:

  \begin{itemize}

    \item $N$ is a raster computed as a focal operation \FOCAL{R}{F}{sum}. Each
    pixel represents the number of pixels from $R$ convoluted with the matrix
    $F$.

    \item $M$ is a raster computed as a focal mean \FOCAL{R}{F}{mean}, thus each
    pixel represents a mean value of its $F$-neighbourhood.

    \item $S$ is a raster computed as a focal standard deviation
    \FOCAL{R}{F}{sd}, thus each pixel represents a standard deviation of its
    $F$-neighbourhood.

  \end{itemize}

\end{definition}

Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} show
Standard and Focal $G^*$ computations for both morning and eventing datasets
with weight matrix $W$ of size 3, 5, 7, 9, 15 and 31. In this figures, when 
computing Focal
$G^*$, the focal matrix $F$ has a constant size of $61{\times}61$ cells. 
Example weight matrix $W$ and focal matrix $F$ are depicted in 
Fig.~\ref{fig:ExampleMatrices}.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Morning}
    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-1}
    \label{fig:EvalMorning}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Eveninig}
    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-2}
    \label{fig:EvalEvening}
  \end{subfigure}
  \caption{Evaluation results - Standard vs Focal $G^*$}
  \label{fig:EvalResults}
\end{figure}

%We used square weight matrices of nrow=ncol= 3, 5, 7, \ldots, 41.
%
%- We experimented with different sizes of matrix $F$.
%- The most stable results were achieved when $all(dim(F) == dim(W))$.

To evaluate the stability of our proposed Focal $G^*$, we compare it to two 
baselines:
\begin{itemize}
  \item Standard $G^*$, which uses the same weight matrix $W$ as our focal 
  version.
  \item Standard $G^*$, which uses square weight matrix with all cells set to 1.
\end{itemize}

The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
the graph represents the $SoH^\uparrow$ metric (Eq.\ref{eq:SoH-up}) between two
$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
has a fixed size of $41{\times}41$

\begin{displaymath}
SoH^\uparrow( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
\end{displaymath}

\begin{figure}[htp]
  \centering
  \begin{subfigure}{.45\columnwidth}
    \centering
    \caption{Weight matrix $W$}
    \includegraphics[width=9em]{images/hotspot-weight-matrix-1}
  \end{subfigure}
  \begin{subfigure}{.45\columnwidth}
    \centering
    \caption{Focal matrix $F$}
    \includegraphics[width=9em]{images/hotspot-eval-gstar-focus-matrix-1}
  \end{subfigure}
  \caption{Example matrices $W$ and $F$}
  \label{fig:ExampleMatrices}
\end{figure}

\subsection{Results and Discussion}

The results for the hot spot analysis are found in
Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} for a
comparison of $G^*$ and the Focal $G^*$ statistic. It can easily be seen that
both versions produce similar results, but the focal versions produces a more
differentiated picture for larger weight matrices. Small differences on a
global scale are more pronounced on a regional scale and result in smaller and
finer areas for hot spots. This enables the detection of additional hot spots
and interesting areas which are most easily observable for the weight matrix of
size $7{\times}7$ in the evening (Fig.~\ref{fig:ComparisonEvening}). This
enables the detection of significant deviations from the surrounding area. 
In contrast the Standard $G^*$ statistic shows larger areas as important.
Therefore, depending on the need of a planner, the Focal $G^*$ statistic
is more helpful to identify individual areas of interest whereas the standard
$G^*$ statistic gives a more broad overview. For the identification of IUHI this
is quite important. As a city planer wishes to detect critical areas, it is
important to detect not only general hot areas, but also those points where the
most extreme differences in a local context exist. Finding those areas can help 
identify the underlying reasons or plan individual solutions.

Based on these images one can also see that the hot spots found by the Focal
$G^*$ statistic seem to be more stable. We compare their stability using only
the $ SoH^\uparrow$ for lack of space. A plot of the results can be found in
Fig.~\ref{fig:EvalResults}. Fig.~\ref{fig:EvalResults} compares the $
SoH^\uparrow$ between each increasing size of the weight matrix W. At a first
glance, one can see that the typical implementation with a square weight matrix
is the most unstable hot spot analysis, regardless of time of day. This is to be
expected as the binary weights increase the dependence on the weight matrix. The
use of a decreasing weight matrix perform better. As the more outlying data
points get less weight, this reduces the dependence on the weight matrix and
leads therefore to more stable results. Our proposed Focal $G^*$ statistic
achieves the most stable results in almost all cases. Only data points in a
restricted region around the area of interest may influence the significance
result. Through this restriction high values at key points gains more weight
regardless of the weight matrix and are therefore more independent of the weight
matrix. This increases the stability. The decrease in stability for the largest
weight matrices is most likely a result of the parametrization of the focal
matrix. With increasing size of the weight matrix in relation to the focal
matrix the value of each pixel is approaching to the mean of the area of the
weight matrix. As can be easily seen from Def.~\ref{def:GenericGetisOrdFunc}
then the value for every pixel would be zero.

\section{Conclusions and Future Work} \label{sec:Conclusion}

In this work, we generalized the Getis-Ord statistic to deal with the problem of
stability inherent in hot spot analysis. We identified possible underlying
reasons for this instability: The weight matrix as well as the size of the study
area. We developed a modified approach that deals with those two factors. The
result is a modified $G^*$ statistic called the \emph{Focal $G^*$ statistic}. It
reduces the study area used for comparison into regions and achieves through
this an increase in stability. To determine the effectiveness of our approach,
we propose a stability metric for hot spots called \emph{SoH}. To our knowledge
no such metric existed before this work. The SoH computes the ratio of
dependence of hot spots for different parametrizations of weight matrices. It
enables to express the stability between each parametrization using single value
restricted between zero and one. Based on this number one can decide which
parametrization to use and researchers can compare the stability of their
methods for unsupervised hot spot analyses. In particular, for temperature
values one wishes to detect those areas which have high differences regardless
of a particular parametrization. If a hot spot only appears for one
parametrization, the information gained for general use is quite small and can
even lead to an inefficient allocation of resources.

This research has several restrictions which have to be taken into account.
First, we only tested the $SoH^\uparrow$ metric. While we assume, based on our
graphical analysis, that the  $SoH^\downarrow$ stability should be similar, we
have no hard results. The results themselves are tested on two events in time
for a fixed area of the city of Karlsruhe. We have not tested it on smaller or
larger study areas, but we assume that the stability of the Focal $G^*$ would
stay the same whereas the stability of the $G^*$ statistic would increase with a
smaller study area and decrease with a larger study area. This follows the
reasoning that the impact of a singular point increases with a decrease of the
study area. To test this dependency is an interesting task for future work. The
last restriction is the fixed size in this work of the focal matrix for the
Focal $G^*$ approach. We only tested one size in this work, but it is highly
probable that the size of the focal matrix has an impact on the stability as
could be seen in Fig.~\ref{fig:EvalResults}. While an overall trend can be seen
in this work when the size of the weight matrix W and the focal matrix F are
almost identical, the exact ratio is beyond the scope of this work. The optimal
ratio as well as when the stability suffers from a too similar size are
interesting question for future work.

\section{Acknowledgements}
This work is part of the research project BigGIS (reference number: 01IS14012)
funded by the Federal Ministry of Education and Research (BMBF) within the
frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
Research for Innovations".
We thank the Nachbarschaftsverband Karlsruhe for the data of the thermal flight
over Karlsruhe. %
\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
\verb|knitr|~\cite{cran:knitr}

\bibliographystyle{plain}
\bibliography{bibfile}  % sigproc.bib is the name of the

\end{document}

### 2017-06-08 paper-main.tex
Added First Structure

@@
 
-Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} show
-Standard and Focal $G^*$ computations for both morning and eventing datasets
-with weight matrix $W$ of size 3, 5, 7, 9, 15 and 31. In this figures, when 
-computing Focal
-$G^*$, the focal matrix $F$ has a constant size of $61{\times}61$ cells. 
-Example weight matrix $W$ and focal matrix $F$ are depicted in 
-Fig.~\ref{fig:ExampleMatrices}.
+\section{Results}
+\subsection{Heatmap}
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{FocalRelation}
+    \includegraphics[width=\linewidth]{images/FocalRealationUp}
+    \label{fig:FocalRelation}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{WeightRealtion}
+    \includegraphics[width=\linewidth]{images/WeightRelationUp}
+    \label{fig:WeightRealtion}
+  \end{subfigure}
+  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
+  \label{fig:RealtionUp}
+\end{figure}
 
@@
   \begin{subfigure}{\linewidth}
-    \caption{Morning}
-    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-1}
-    \label{fig:EvalMorning}
+    \caption{FocalRelation}
+    \includegraphics[width=\linewidth]{images/FocalRealationDown}
+    \label{fig:FocalRelation}
   \end{subfigure}
@@
   \begin{subfigure}{\linewidth}
-    \caption{Eveninig}
-    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-2}
-    \label{fig:EvalEvening}
+    \caption{WeightRealtion}
+    \includegraphics[width=\linewidth]{images/WeightRelationDown}
+    \label{fig:WeightRealtion}
   \end{subfigure}
-  \caption{Evaluation results - Standard vs Focal $G^*$}
-  \label{fig:EvalResults}
+  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
+  \label{fig:RealtionDown}
+\end{figure}
+\subsection{Clumping}
+
+\subsection{Zoom}
+
+Blueline is Focal $G^*$. Redline is $G^*$
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{Upward}
+    \includegraphics[width=\linewidth]{images/SoHZoomUp}
+    \label{fig:UpwardZoom}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{Downward}
+    \includegraphics[width=\linewidth]{images/SoHZoomDown}
+    \label{fig:DownwardZoom}
+  \end{subfigure}
+  \caption{TODO}
+  \label{fig:Zoom}
 \end{figure}
 
-%We used square weight matrices of nrow=ncol= 3, 5, 7, \ldots, 41.
-%
-%- We experimented with different sizes of matrix $F$.
-%- The most stable results were achieved when $all(dim(F) == dim(W))$.
-
-To evaluate the stability of our proposed Focal $G^*$, we compare it to two 
-baselines:
-\begin{itemize}
-  \item Standard $G^*$, which uses the same weight matrix $W$ as our focal 
-  version.
-  \item Standard $G^*$, which uses square weight matrix with all cells set to 1.
-\end{itemize}
-
-The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
-the graph represents the $SoH^\uparrow$ metric (Eq.\ref{eq:SoH-up}) between two
-$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
-has a fixed size of $41{\times}41$
-
-\begin{displaymath}
-SoH^\uparrow( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
-\end{displaymath}
+\subsection{Blur}
 
 \begin{figure}[htp]
-  \centering
-  \begin{subfigure}{.45\columnwidth}
-    \centering
-    \caption{Weight matrix $W$}
-    \includegraphics[width=9em]{images/hotspot-weight-matrix-1}
+  \begin{subfigure}{\linewidth}
+    \caption{Upward}
+    \includegraphics[width=\linewidth]{images/SoHUpBlur}
+    \label{fig:UpwardBlur}
   \end{subfigure}
-  \begin{subfigure}{.45\columnwidth}
-    \centering
-    \caption{Focal matrix $F$}
-    \includegraphics[width=9em]{images/hotspot-eval-gstar-focus-matrix-1}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{Downward}
+    \includegraphics[width=\linewidth]{images/SoHDownBlur}
+    \label{fig:DownwardBlur}
   \end{subfigure}
-  \caption{Example matrices $W$ and $F$}
-  \label{fig:ExampleMatrices}
+  \caption{TODO}
+  \label{fig:Blur}
 \end{figure}

### 2017-06-08 paper-main.tex
abstract almost finished

@@
 \begin{abstract}
-  The Urban Heat Island (UHI) effect describes the difference in temperature
-  between cities and their surrounding areas. However, temperature differences
-  within city limits, so-called Intra Urban Heat Islands (IUHI), affect human
-  health as well as the energy demands in local areas. In order to anticipate
-  and mitigate the resulting impacts of heat trough urban planing, a method to
-  reliably detect these local areas is needed. Existing methods from the
-  geo-statistical field can identify those areas. But these statistics can be
-  unstable in their detection of hot spots, in particular for temperature hot
-  spots, depending on their parametrization. In this paper, we propose a
-  modification of the well known Getis-Ord ($G^*$) statistic, called the
-  \emph{Focal $G^*$} statistic. This modification replaces the computation of
-  the global mean and standard deviation with their focal counterparts. We
-  define the stability of our approach by introducing a stability metric called
-  \emph{Stability of Hot spot} (SoH), which requires that hot spots have to be
-  in similar areas regardless of the chosen weight matrix. The results are
-  evaluated on real world temperature data for the city of Karlsruhe.
+Hotspot analysis is an essential in geo-statistics.
+It supports decision making by detecting points as well as areas of interest in comparison to their neighbourhood.
+But these methods are dependent on different parameters, ranging from the resolution of the study area to the size of their neighbourhood.
+This dependence can lead to instabilities of the detected hotspots, where the results can highly vary between different parameters.
+A decision maker can therefore not be sure of the validity of analysis.
+In this study, we examine the impact of key parameter on the stability of the hotspots, namely the size of the neighbourhood (blurr), the resolution (zoom) and the size of the study area, as well as the influence of the ratio between those parameter.
+We compute the hotspots with the well known Getis-Ord ($G^*$) statistic as well as an modification, the \emph{Focal $G^*$} statistic.
+The stability of the hotspot analysis is measured with the recently introduced \emph{stability of hotspots} (SoH) metric and by visual analysis.
+We evaluate the results on real world data with the well-known yellow cab taxi data set from New York, Manhattan.
+It can be shown that
+
 \end{abstract}

### 2017-06-08 paper-main.tex
abstract added
abstract finished

@@
 \begin{abstract}
-Hotspot analysis is an essential in geo-statistics.
-It supports decision making by detecting points as well as areas of interest in comparison to their neighbourhood.
+Hotspot analysis is an essential in geo-statistics. It supports decision making by detecting points as well as areas of interest in comparison to their neighbourhood. 
 But these methods are dependent on different parameters, ranging from the resolution of the study area to the size of their neighbourhood. 
@@
 A decision maker can therefore not be sure of the validity of analysis. 
-In this study, we examine the impact of key parameter on the stability of the hotspots, namely the size of the neighbourhood (blurr), the resolution (zoom) and the size of the study area, as well as the influence of the ratio between those parameter.
+In this study, we examine the impact of key parameter on the stability of the hotspots, namely the size of the neighbourhood, the resolution and the size of the study area, as well as the influence of the ratio between those parameter.
  We compute the hotspots with the well known Getis-Ord ($G^*$) statistic as well as an modification, the \emph{Focal $G^*$} statistic. 
@@
  We evaluate the results on real world data with the well-known yellow cab taxi data set from New York, Manhattan. 
-It can be shown that
+ Our results indicate a negative impact on the stability with an increase of the size of the neighbourhood as well as a reduction of the size of the study area, regardless of the resolution.
 

### 2017-06-08 paper-main.tex
Create paper-main.tex

@@
 \begin{abstract}
-Hotspot analysis is an essential in geo-statistics. It supports decision making by detecting points as well as areas of interest in comparison to their neighbourhood. 
-But these methods are dependent on different parameters, ranging from the resolution of the study area to the size of their neighbourhood. 
-This dependence can lead to instabilities of the detected hotspots, where the results can highly vary between different parameters. 
-A decision maker can therefore not be sure of the validity of analysis. 
-In this study, we examine the impact of key parameter on the stability of the hotspots, namely the size of the neighbourhood, the resolution and the size of the study area, as well as the influence of the ratio between those parameter.
- We compute the hotspots with the well known Getis-Ord ($G^*$) statistic as well as an modification, the \emph{Focal $G^*$} statistic. 
- The stability of the hotspot analysis is measured with the recently introduced \emph{stability of hotspots} (SoH) metric and by visual analysis. 
- We evaluate the results on real world data with the well-known yellow cab taxi data set from New York, Manhattan. 
- Our results indicate a negative impact on the stability with an increase of the size of the neighbourhood as well as a reduction of the size of the study area, regardless of the resolution.
-
+Hotspot analysis is essential for geo-statistics.
+It supports decision making by detecting points
+as well as areas of interest in comparison to their
+neighbourhood. However, these methods are dependent
+on different parameters, ranging from the resolution
+of the study area to the size of their neighbourhood.
+This dependence can lead to instabilities of the detected
+hotspots, where the results can highly vary between
+different parameters. A decision maker can therefore ask
+how valid the analysis actually is.
+%
+In this study, we examine the impact of key parameter
+on the stability of the hotspots, namely the size of
+the neighbourhood, the resolution and the size of the
+study area, as well as the influence of the ratio between
+those parameter.
+%
+We compute the hotspots with the well known Getis-Ord ($G^*$)
+statistic as well as its modification, the \emph{Focal $G^*$} statistic.
+We measure the stability of the hotspot analysis using
+a recently introduced \emph{stability of hotspots} metric (SoH)
+and compare the results to intuitive visual analysis.
+%
+We evaluate the results on real world data with the well-known
+yellow cab taxi data set from New York, Manhattan.
+Our results indicate a negative impact on the stability with
+an increase of the size of the neighbourhood as well as
+a reduction of the size of the study area, regardless of
+the resolution.
 \end{abstract}

### 2017-06-09 paper-main.tex
I think there is an s missing?

@@
 %
-In this study, we examine the impact of key parameter
+In this study, we examine the impact of key parameters
 on the stability of the hotspots, namely the size of
@@
 study area, as well as the influence of the ratio between
-those parameter.
+those parameters.
 %

### 2017-06-12 paper-main.tex

@@
 % ==========================================
-% Support for \FOCAL{R}{M}{op} (by Viliam)
+% Custom commands (by Viliam)
 % ==========================================
-\newcommand{\FOCALMMODE}[3]{
+\newcommand{\FOCAL}[3]{ % usage: \FOCAL{R}{M}{op}
+  \ifmmode
     #1{\stackrel{\mathtt{#3}}{\circ}}#2
+  \else
+    \begin{math}\FOCAL{#1}{#2}{#3}\end{math}
+  \fi
 }
-\newcommand{\FOCAL}[3]{
+\newcommand{\SOHUP}{
   \ifmmode
-  \FOCALMMODE{#1}{#2}{#3}
+    SoH^\uparrow
   \else
-  \begin{math}\FOCALMMODE{#1}{#2}{#3}\end{math}%
+  \begin{math}\SOHUP\end{math}
+  \fi
+}
+\newcommand{\SOHDOWN}{
+  \ifmmode
+    SoH^\downarrow
+  \else
+  \begin{math}\SOHDOWN\end{math}
   \fi
@@
 
-Existing methods to determine hot spots are dependent on the parametrization of
-the weight matrix as well as on the size of the study area.
+Existing methods for determining hot spots are dependent on the parametrization
+of the weight matrix as well as on the size of the study area. Intuitively,
+increasing the size of a weight matrix has a "blurring" effect on the raster
+(Fig.~\ref{def:TODO}a) whereas decreasing the size can be seen as a form of
+"sharpening" (Fig.~\ref{def:TODO}b).
 
-Consider the real-world example depicted in Fig.~\ref{fig:TempMaps}. The
-temperature map of a morning thermal flight dataset (Fig.~\ref{fig:TempMaps:a})
-has been processed using $G^*$.
+%TODO: add image showing and blurring/sharpening effects
 
-\begin{figure}[htp]
-  \begin{subfigure}{1\linewidth}
-    \caption{Morning temperatures}
-    \includegraphics[width=\linewidth]{images/hotspot-rawtemp-1}
-    \label{fig:TempMaps:a}
-  \end{subfigure}
-
-  \caption{
-    Karlsruhe city center.
-    Selected area of $2.4{\times}1.4\,km$.
-    Pixel size $5{\times}5\,m$.
-  }
-  \label{fig:TempMaps}
-\end{figure}
-
-% Bild besteht aus orginal, weight matrix a und weight matrix b
-As we can see, hot spots are oftentimes disappearing or appearing unrelated to
-previously found hot spots. While these computations indeed show hot spots and
-the results are correct, they lack stability.
+%As we can see, hot spots are oftentimes disappearing or appearing unrelated to
+%previously found hot spots. While these computations indeed show hot spots and
+%the results are correct, they lack stability.
 
 For a data analyst, when exploring the data interactively by choosing different
-filter sizes (in form matrices), it is important that the hot spot's position
-and size changes in a predictable manner. This intuition is the basis for our
-stability metric.
+filter sizes (weight matrices) or point aggregation strategies (pixel sizes), it
+is important that the position and size of a hotspot changes in a predictable
+manner. We formalize the intuition in our stability metric.
+
+%
+%Consider the real-world example depicted in Fig.~\ref{fig:TempMaps}.
+%%TODO: thermal flight -> NY taxi
+%The temperature map of a morning thermal flight dataset 
+%(Fig.~\ref{fig:TempMaps:a}) has been processed using $G^*$.
+%
+%%TODO: thermal flight -> NY taxi
+%%TODO: need two images - G* and FocalG*
+%\begin{figure}[htp]
+%  \begin{subfigure}{1\linewidth}
+%    \caption{Morning temperatures}
+%    \includegraphics[width=\linewidth]{images/hotspot-rawtemp-1}
+%    \label{fig:TempMaps:a}
+%  \end{subfigure}
+%  
+%  \caption{
+%    Karlsruhe city center.
+%    Selected area of $2.4{\times}1.4\,km$.
+%    Pixel size $5{\times}5\,m$.
+%  }
+%  \label{fig:TempMaps}
+%\end{figure}
 
 We define a hot spot found in comparably more coarse resolutions as
-\emph{parent} (larger weight matrix) and in finer resolutions as \emph{child}
-(smaller weight matrix). To be stable, one assumes that every parent has at
+\emph{parent} (larger weight matrix or larger pixel size) and in finer
+resolutions as \emph{child} (smaller weight matrix or smaller pixel size).
+
+That is
+
+To be stable, one assumes that every parent has at
 least one child and that each child has one parent. For a perfectly stable
@@
 
-%TODO: what about the other direction?
 In its downward property (from parent to child, injective) it is defined as:
@@
   \label{eq:SoH-down}
-SoH^\downarrow = \frac{ParentsWithChildNodes}{Parents} = \frac{|Parents \cap 
-Children|}{|Parents|}
+  \SOHDOWN
+    = \frac{ParentsWithChildNodes}{Parents}
+    = \frac{|Parents \cap Children|}{|Parents|}
 \end{equation}
@@
   \label{eq:SoH-up}
-SoH^\uparrow = \frac{ChildrenWithParent}{Children} = 1 - \frac{|Children - 
-Parents|}{|Children|}
+  \SOHUP
+    = \frac{ChildrenWithParent}{Children}
+    = 1 - \frac{|Children - Parents|}{|Children|}
 \end{equation}
@@
 
-In the following text, we use the notation \FOCAL{R}{M}{op} to denote
-a focal operation $op$ applied on a raster $R$ with a focal window determined 
-by a
+In the following text, we use the notation \FOCAL{R}{M}{op} to denote a focal
+operation $op$ applied on a raster $R$ with a focal window determined by a
 matrix $M$. This is rougly eqivalent to a command \verb|focal(x=R, w=M, fun=op)|
@@
 
+\section{Evaluation}
+
+- To evaluate, we compare G* with FocalG* on the same dataset.
+- We use NY taxi dropoffs
+- a single evaluation run is defined in Def.~\ref{def:EvalRun}.
+- In an ideal case, we could produce a 3D-plot:
+  - x-axis would be growing pixel sizes 100..1000 by 100 (aka zoom-out)
+  - y-axis would be growing weight matrix sizes (e.g. 5..41 by 2)
+  - z-axis would be performance of G* vs FocalG* x and y coordinates
+  - we could also repeat the computation for multiple datasets to obtain 
+  multiple samples and to compute error bars.
+- due to paper size limit, we choose projection in which matrix size is set to 
+constant 7x7 pixels and the only variable is the pixel size. This way, we 
+produce a 2D plot. We also generate just a single sample.
+
+\begin{definition}[Evaluation Run]
+  \label{def:EvalRun}
+  We define a single evaluation run as a tuple:
+  \begin{displaymath}
+    E = (V, m, p, w)
+  \end{displaymath}
+  \noindent where:
+  \begin{itemize}
+
+    \item $V$ is the input dataset of points, representing the taxi dropoffs in 
+    our case.
+
+    \item $m$ is the metric used, in our case either \SOHUP or \SOHDOWN.
+
+    \item $p$ represents the pixel size for aggregating points from $V$, 
+    e.g. $100 \times 100$ meters.
+
+    \item $w$ represents the size of a weight matrix.
+    In our case, we chose a weight matrix depicted in 
+    Figure~\ref{fig:ExampleMatrices}(a) for both the G* and FocalG* cases.
+  \end{itemize}
+\end{definition}
+
+%Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} show
+%Standard and Focal $G^*$ computations for both morning and eventing datasets
+%with weight matrix $W$ of size 3, 5, 7, 9, 15 and 31. In this figures, when 
+%computing Focal
+%$G^*$, the focal matrix $F$ has a constant size of $61{\times}61$ cells. 
+%Example weight matrix $W$ and focal matrix $F$ are depicted in 
+%Fig.~\ref{fig:ExampleMatrices}.
+
 \begin{figure}[htp]
@@
 \subsection{Blur}
+
+The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
+the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
+$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
+has a fixed size of $41{\times}41$
+
+\begin{displaymath}
+\SOHUP( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
+\end{displaymath}
 

### 2017-06-12 paper-main.tex
raw idea of intro and related work

@@
 
-For urban city planers, the detection of Intra Urban Heat Islands (IUHI) is of
-high interest as high temperatures impact energy
-consumption~\cite{Hassid.2001.Electricity_UHI} as well as human
-health~\cite{Ye.2012}. The effect that the temperatures between an urban area
-and its surroundings differ, called the Urban Heat Island effect
-\cite{Oke1982energetic}, has long been the subject of research. Most historical
-studies conducted had to rely on few, fixed weather stations, low
-spatio-temporal resolution of satellites or small-scale mobile measurements by
-car, preventing the modelling of finer-grained temperature differences within an
-urban area itself. With the advent of inexpensive mobile sensors, higher
-spatio-temporal resolution of satellites and volunteered geographic
-informations, to name just a small selection, it is now feasible to focus on the
-temperature differences in a city as the subject of interest.
-
-Hot spot analysis is a tool which is suited to detect such areas. In the context
-of IUHI we can detect those areas where the temperature is significantly
-different from the mean temperature of our study area. This enables us to
-identify points of interest without the need to pre-process the data.
-
-Although existing methods are independent of concrete values, their results are
-highly dependent on the size of the study area and their parametrization such as
-the weight matrix in the case of the Getis-Ord statistic. This dependency can
-lead to unstable hot spots, where the identified hot spots only appear in one 
-specific combination of parameter. The generalization of insights gained from
-unstable hot spots is suboptimal. A city planer who has to rely on those
-insights will most likely prioritize the wrong area to invest his limited
-resources. Given the increasing importance to detect extreme local temperatures
-in cites, see e.g. \cite{Hansen.2010, GRL:GRL22143, department2014world}, means
-to reliably detect and mitigate the effect of temperature extremes in a
-proactive fashion are needed.
-
-To solve this problem, we first propose a metric to measure the stability of a
-hot spot analysis regarding its parametrization of the weight matrix called the
-\emph{Stability of Hot spot} (SoH). This metric measures whether a hot spot
-found for a given weight matrix is carried over to the found hot spots with a
-different weight matrix. This enables us to quantify the stability of any hot
-spot analysis. Based on our reasoning behind the instability of existing hot
-spot analyses, we propose a modification of the well known Getis-Ord statistic
-($G^*$): the \emph{Focal Getis-Ord} statistic (Focal $G^*$). Instead of the
-global mean and variance used by $G^*$, it only uses the mean and variance of a
-predefined region around each point. This region is a subset of the whole study
-area. By doing this, the instability is contained within a smaller region and
-thereby independent of the parametrization of the weight matrix. We test our
-stability metric as well as this modified approach on data given by two
-temperature snapshots of the city of Karlsruhe taken in 2008.
+\begin{itemize}
+\item hot spot analysis is important
+\item similar to cluster analysis
+\item is important to identify interesting areas 
+\item typical problem is the correct detection method and parametrization
+\item inital work of bruns and viliam 2017 show the instability and present simple metric and stable  method
+\item here, we build upon that work and examine in more detail the impact of the different parameter with the standard $G^*$ and focal $G^*$, in particular the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix)
+\item in particular, we compare the stability for all possible combinations and isolate the effect of single parameter by clever aggregation
+\item We test on well-known taxi data set for easy comparison and so that in can be easily replicated
+\end{itemize}
 
@@
 
-\subsection{Urban Heat Island}
-
-The scientific interest in the phenomena of UHI is well established. One of the
-earliest known overviews of the scientific literature of the city climates is
-given by Albert Kratzer 1937~\cite{dieckmann1938stadtklima}. At that time
-already, relations between temperature, humidity, human heat fluxes and air
-pollution are investigated.
-
-A more recent overview comes from Arnfied~\cite{Arnfield.2003}. The focus here
-lies on the development in the field of climatology between 1980 and 2003. In
-particular, the rise of simulations and modelling is lauded, but, to quote
-Arnfield, ``simple methods are still needed to estimate UHI intensity within
-urban areas''~\cite{Arnfield.2003}.
-
-Schwarz~et~al.~\cite{Schwarz.2011} compare 11 different Surface Urban Heat
-Island (SUHI) indicators on a dataset of 263 European cities with monthly mean
-temperatures. They show that the selection of indicators is important for the
-detection of UHI due to possible instabilities of each indicator.
-
-A more recent development is the focus on IUHI. The definition for IUHI comes
-from Martin et al.~\cite{Martin.2015}. By defining thresholds with respect to
-spatial reference, these enable the detection of hot spots in a city, which
-Martin et al. call surface intra-UHI. This boils down to five steps, i.e.
-essentially a comparison of absolute deviation from the mean temperature given a
-survey area. The results can then be used to detect areas of interest in a city
-and potentially trigger alerts for a much finer spatial granularity.
-
-While the proposition to examine urban micro-climates can be traced back as far
-as 1937~\cite{dieckmann1938stadtklima}, we have found only few works in this
-field. Schwarz et al.~\cite{Schwarz.2012} state that the reduction of an UHI to
-a single value for a whole city is questionable regarding its explanatory power.
-But also that there is currently no other way to quantify the differences
-amongst cities.
-
-The difficulties presented by comparing the UHI values between different cities
-are the topic of Stewart and Oke~\cite{Stewart2012}. They propose the use of
-local climate zones (LCZ) to standardise the methodology and terminology.
-
-Another area where urbanizations affects the temperature distribution are
-subsurface temperatures. Menberg et al.~\cite{Menberg.2013} look into the
-distribution of the temperatures below the surface -- the subsurface
-temperature. They find local hot spots of heat with deviations of up to
-+20\textdegree{K} in some areas related to local heat sources.
-
-\subsection{Hot Spot Analysis}
+\begin{itemize}
+\item goal Here: some cluster analysis
+\item typical clustering apporaches -> phd symposium as examples
+\end{itemize}
 

### 2017-06-13 paper-main.tex
First draft of introduction Added little related work paper

@@
 \section{Introduction}
+The goal of hotspot analysis is the detection and identification of interesting areas.
+It achieves this goal by computing statistically significant deviations from the mean value of a given study area.
+This allows a decision maker to easily identify those areas of interest and allows further focus in sub-sequential data analysis or the decision focus.
+Typical applications range from crime detection over identification of disease outbreaks to urban heat islands.
+In such applications, scarce resources are then often applied in only those identified hot spots or used as the basis for the allocation.
+The general approach is an unsupervised learning method similar to a cluster analysis.
 
-\begin{itemize}
-\item hot spot analysis is important
-\item similar to cluster analysis
-\item is important to identify interesting areas 
-\item typical problem is the correct detection method and parametrization
-\item inital work of bruns and viliam 2017 show the instability and present simple metric and stable  method
-\item here, we build upon that work and examine in more detail the impact of the different parameter with the standard $G^*$ and focal $G^*$, in particular the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix)
-\item in particular, we compare the stability for all possible combinations and isolate the effect of single parameter by clever aggregation
-\item We test on well-known taxi data set for easy comparison and so that in can be easily replicated
-\end{itemize}
+But, similar to a cluster analysis, there does exist a high dependency of the identified hotspots on the detection method and in particular the parametrization of this method.
+The identified areas as well as their shape can vary highly.
+This volatility can lead to a decrease in trust in the result or in suboptimal allocations of scarce resources.
+Therefore it is necessary to measure and evaluate the stability of a hotspot analysis as well as the different parametrizations.
+In our initial work (Hier Bruns and VIliam 2017), we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .
+Here, we build upon that work and examine in more detail the impact of the different instantiations of the most typical parameter.
+We use the well known Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of this statistic, the focal $G^*$ (citate bruns and viliam).
+Those parameter are the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix).
+By varying over these parameter, we can compare the stability for all possible combinations and isolate the effect of single parameter by aggregation over the other parameter.
+We evaluate on the well-known taxi data set to show the applicability on real world use cases as well as to enable a simple replication.
 
@@
 \item goal Here: some cluster analysis
-\item typical clustering apporaches -> phd symposium as examples
+\item typical clustering apporaches -> phd symposium as examples (possible to cite =) )
 \end{itemize}

### 2017-06-13 paper-main.tex
first draft related work TODO: Citations ...

@@
 \begin{abstract}
-Hotspot analysis is essential for geo-statistics.
+Hot spot analysis is essential for geo-statistics.
 It supports decision making by detecting points
@@
 Typical applications range from crime detection over identification of disease outbreaks to urban heat islands.
-In such applications, scarce resources are then often applied in only those identified hot spots or used as the basis for the allocation.
+In such applications, scarce resources are then often applied in only those identified hotspots or used as the basis for the allocation.
 The general approach is an unsupervised learning method similar to a cluster analysis.
@@
 
-\begin{itemize}
-\item goal Here: some cluster analysis
-\item typical clustering apporaches -> phd symposium as examples (possible to cite =) )
-\end{itemize}
+\subsection{Quality of Clustering}
+The problem of assessing the quality in unsupervised learning is well known.
+In the case of the k-mean algorithm, the quality of the clustering is mostly dependent on the value of the \emph{k} and a miss-specification can lead to highly irregular clusters.
+In a simple 2D clustering, they can be easily recognized by visual analysis, but in higher dimensionality, this is impossible.
+One method, to measure the quality of such a clustering is the compactness of the clusters, see e.g.
+Song 2010 (http://ieeexplore.ieee.org/document/5558958/?part=1).
+This enables the comparison between different clusters.
+Another possibility is the Silhouette Coefficient by Kaufman et Rousseeuw 1990.
+This metric measures the similarity of objects in a cluster in comparison to other clusters.
+For density based clustering, e.g.
+for DBSCAN, OPTICS (Ankerst et al 1999) gives a simple method to tune the essential parameter for this clustering.
+This is only a small overview of methods to influence and measure the quality of different clustering methods.
+But it shows that this problem is not easily solved and dependent on the chosen algorithm.
+To our knowledge, there does not exist a method to overall measure the stability of a clustering.
 
-The goal of an analysis of temperatures in a city is to find the most
-interesting, significant areas: Hot spots~\cite{Martin.2015}. This goal is
-similar to the hot spot analysis in the field of geo-statistics. One of the most
-fundamental approach is Moran´s I~\cite{MoranI}. There it is tested whether or
+\subsection{Hot Spot Analysis}
+The goal of hotspot analysis is the detection of interesting areas as well as patterns in spatial information.
+One of the most fundamental approach is Moran´s I~\cite{MoranI}.
+There it is tested whether or
 not a spatial dependency exists. This gives the information on global
@@
 Moran´s I is applied in a local context. The goal is to detect not only global
-values, but instead to focus on local hot spots and to measure the significance
-of those local areas.
-
-The local Getis-Ord statistic~\cite{Ord.1995} is defined as follow:
-\begin{definition}[Getis-Ord $G^*_i$ statistic] \label{def:Gstar}
-  Assuming a study area with $n$ measurements, let $X = [x_1, \ldots,
-  x_n]$ be all values measured in this area. Let $w_{i,j}$ be a spatial weight
-  between two points $i$ and $j$ for all $i,j \in \{ 1, \ldots, n\}$. The 
-  Getis-Ord $G^*_i$ statistic is given as:
-  \begin{equation} \label{eq:Gstar}
-  G^*_i = \frac{
-    \sum_{j=1}^{n}w_{i,j}x_j - \bar{X}\sum_{j=1}^{n}w_{i,j}
-  }{
-  S \sqrt{
-    \frac{
-      n \sum_{j=1}^{n}w_{i,j}^2 - (\sum_{j=1}^{n}w_{i,j})^2
-    }{n-1}
-  }
-}
-\end{equation}
-where:
-\begin{itemize}
-  \item $\bar{X}$ is the mean of all measurements,
-  \item $S$ is the standard deviation of all measurements.
-\end{itemize}
-\end{definition}
-
-As it is known, this statistic creates a z-score, which denotes the significance
-of an area in relation to its surrounding areas.
-
-LISA is quite similar, as it is the local statistic for Moran's
-I~\cite{Anselin.1995}, but the z-score has a different meaning. Apart from
-$G^*_i$, LISA does not distinguish between cold spots and hot spots as it
-assigns high z-score to most similar areas.
-
-Two other well known method are the kernel density estimation~\cite{KDE_Hotspot}
-and kriging~\cite{Kriging_Hotspot}. These do not provide significance levels.
-Instead, they estimate the values for each location based on the rest of the
-study area and a threshold value \cite{Thakali2015}. Therefore, results for
-different areas are not comparable, especially in the case of differing
-temperature distributions. Kriging was developed for the estimation of ore
-deposits~\cite{krige1951statistical}, but today, applications for geo-temporal
-forecasts with this approach can be found, e.g. for the city of
-Zurich.~\footnote{https://r-video-tutorial.blogspot.de/2015/08/spatio-temporal-kriging-in-r.html}
-
-All of the aforementioned methods use weights between pairs of points, usually
-based on their geographical distance. However, in real applications, the points
-are aggregated into rasters and the weights are represented as a weight matrix.
-This allows for expressing the algorithms in terms of map algebra operations, a
-term first coined by Dana~Tomlin~\cite{Tomlin1990} and computed in a distributed
-fashion (e.g. using Geotrellis framework running on
-Apache~Spark~\cite{github:Geotrellis}).
-
-In this work, we focus on the Getis-Ord statistic applied to rasters of land
-surface temperature. This enables us to transform the formula for the $G^*$
-statistic into a computationally more efficient form. We then propose a
-modification of the standard $G^*$ statistics, to increase the stability of the
-hot spots found.
+values, but instead to focus on local hotspots and to measure the significance
+of those local areas. A more in depth overview of methods to identify and visualize spatial patterns and areas of interest can be found in Shekhar et al (2011).
 
@@
 filter sizes (weight matrices) or point aggregation strategies (pixel sizes), it
-is important that the position and size of a hotspot changes in a predictable
+is important that the position and size of a hot spot changes in a predictable
 manner. We formalize the intuition in our stability metric.

### 2017-06-13 paper-main.tex
First version of Results

@@
 
-% extent
-The two datasets (morning and evening flights) depicted in
-Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} were
-obtained from a thermal flight over the city of Karlsruhe on 26.09.2008 at
-6:30--7:45 and 20:00--21:30. The flights were executed by the
-Nachbarschaftsverband
-Karlsruhe\footnote{http://www.nachbarschaftsverband-karlsruhe.de/}. A single
-pixel in the raster represents an area of approximately $5{\times}5m$. The whole
-dataset of size $35{\times}25\,km$ was cropped into the inner city area of
-$2.4{\times}1.4\,km$. % temp range
-The temperatures in our dataset range from -1.7°C to 18.3°C.
-% missing values = NAs
-Missing values in the dataset were interpolated using a focal median function
-with a square matrix of 11x11 pixels, mainly for speeding up further
-computations and to avoid special handling of NA values.
+Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
+We used only the dataset of January 2016. From that
+dataset we used the $pickup_longitude$ and $pickup_latitude$ column. 
+The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
+Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
+In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
+%
+For our measurements we specified the following data series:
+\begin{itemize}
+ \item The weight matrix W is from 3 to 43 with a stepsize of 4.
+ \item The focal matrix F is from  17 to 125 with a stepsize of 12.
+ \item The zoom level is from 1 to 5 with a stepsize of 1.
+\end{itemize}
+Therefore we calculate around 10*10*5=500 results for each fixed x.
+The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.
 
@@
 \section{Results}
+
 \subsection{Heatmap}
@@
 
-The results for the hot spot analysis are found in
-Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} for a
-comparison of $G^*$ and the Focal $G^*$ statistic. It can easily be seen that
-both versions produce similar results, but the focal versions produces a more
-differentiated picture for larger weight matrices. Small differences on a
-global scale are more pronounced on a regional scale and result in smaller and
-finer areas for hot spots. This enables the detection of additional hot spots
-and interesting areas which are most easily observable for the weight matrix of
-size $7{\times}7$ in the evening (Fig.~\ref{fig:ComparisonEvening}). This
-enables the detection of significant deviations from the surrounding area. 
-In contrast the Standard $G^*$ statistic shows larger areas as important.
-Therefore, depending on the need of a planner, the Focal $G^*$ statistic
-is more helpful to identify individual areas of interest whereas the standard
-$G^*$ statistic gives a more broad overview. For the identification of IUHI this
-is quite important. As a city planer wishes to detect critical areas, it is
-important to detect not only general hot areas, but also those points where the
-most extreme differences in a local context exist. Finding those areas can help 
-identify the underlying reasons or plan individual solutions.
-
-Based on these images one can also see that the hot spots found by the Focal
-$G^*$ statistic seem to be more stable. We compare their stability using only
-the $ SoH^\uparrow$ for lack of space. A plot of the results can be found in
-Fig.~\ref{fig:EvalResults}. Fig.~\ref{fig:EvalResults} compares the $
-SoH^\uparrow$ between each increasing size of the weight matrix W. At a first
-glance, one can see that the typical implementation with a square weight matrix
-is the most unstable hot spot analysis, regardless of time of day. This is to be
-expected as the binary weights increase the dependence on the weight matrix. The
-use of a decreasing weight matrix perform better. As the more outlying data
-points get less weight, this reduces the dependence on the weight matrix and
-leads therefore to more stable results. Our proposed Focal $G^*$ statistic
-achieves the most stable results in almost all cases. Only data points in a
-restricted region around the area of interest may influence the significance
-result. Through this restriction high values at key points gains more weight
-regardless of the weight matrix and are therefore more independent of the weight
-matrix. This increases the stability. The decrease in stability for the largest
-weight matrices is most likely a result of the parametrization of the focal
-matrix. With increasing size of the weight matrix in relation to the focal
-matrix the value of each pixel is approaching to the mean of the area of the
-weight matrix. As can be easily seen from Def.~\ref{def:GenericGetisOrdFunc}
-then the value for every pixel would be zero.
+% Focal size  
+%	Increase of focal size leads to better results in the upward property
+% 	Standard deviation decrease with higher focal size 
+%	No standard deviation af F 17x17 because of missing clusters
+%	The downward property reaches its maximum at 65x65
+%
+%	Conclusion: F should be around 65x65 or higher
+In figure ~\ref{TODO Up} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
+The standard deviation decreases also with a higher focal size. Only 
+at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
+missing, because the weight size W must be smaller than F. When F and W have similar
+size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
+$SoH^{\downarrow}$ in figure ~\ref{TODO Down} reaches its maximum for focal size F 65x65 in the regarded area.
+%
+% Weight size
+%	Increase of weight leads to increase of downward property
+%	Small break downs for G* for upward and downward property
+%	For the upward property Focal G* is better than G*
+%
+%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
+In figure ~\ref{TODO wDown} one can see that an increase of the weight size leads to better results.
+Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
+that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
+The standard deviation is in this area higher than in the other points.
+In figure ~\ref{TODO wUp} the break downs are also visible.
+The high standard deviation indicates that it is possible to use this parametrisation for better results
+The $SoH^{\uparrow}$ in ~\ref{TODO wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
+%
+% Zoom
+%	G* alwas better than Focal G* for upward and downward property
+%	Focal G* has different focal sizes because zoom is compared
+%	At zoom level 4 G* increase much more than Focal G*
+%
+%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
+%	influence on the value
+The last variation we examined was the zoom level. One can see that $G^*$ is always better than Focal $G^*$.
+The target area of Focal $G^*$ increases if you zoom out.
 

### 2017-06-14 paper-main.tex
Added conclusion

@@
 We used only the dataset of January 2016. From that
-dataset we used the $pickup_longitude$ and $pickup_latitude$ column. 
+dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
 The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
@@
 
-\subsection{Heatmap}
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{FocalRelation}
-    \includegraphics[width=\linewidth]{images/FocalRealationUp}
-    \label{fig:FocalRelation}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{WeightRealtion}
-    \includegraphics[width=\linewidth]{images/WeightRelationUp}
-    \label{fig:WeightRealtion}
-  \end{subfigure}
-  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
-  \label{fig:RealtionUp}
-\end{figure}
-
 \section{Evaluation}
@@
 
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{FocalRelation}
-    \includegraphics[width=\linewidth]{images/FocalRealationDown}
-    \label{fig:FocalRelation}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{WeightRealtion}
-    \includegraphics[width=\linewidth]{images/WeightRelationDown}
-    \label{fig:WeightRealtion}
-  \end{subfigure}
-  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
-  \label{fig:RealtionDown}
-\end{figure}
 \subsection{Clumping}
@@
 %	Conclusion: F should be around 65x65 or higher
-In figure ~\ref{TODO Up} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
+In figure ~\ref{fig:fUp} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
 The standard deviation decreases also with a higher focal size. Only 
@@
 size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
-$SoH^{\downarrow}$ in figure ~\ref{TODO Down} reaches its maximum for focal size F 65x65 in the regarded area.
+$SoH^{\downarrow}$ in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area.
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{SoH up for focal size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/fUp}
+    \label{fig:fUp}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{SoH down for focal size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/fDown}
+    \label{fig:fDown}
+  \end{subfigure}
+  \caption{SoH for focal size}
+  \label{fig:SoHFocal}
+\end{figure}
+
 %
@@
 %	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
-In figure ~\ref{TODO wDown} one can see that an increase of the weight size leads to better results.
+In figure ~\ref{fig:wDown} one can see that an increase of the weight size leads to better results.
 Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
@@
 The standard deviation is in this area higher than in the other points.
-In figure ~\ref{TODO wUp} the break downs are also visible.
+In figure ~\ref{fig:wUp} the break downs are also visible.
 The high standard deviation indicates that it is possible to use this parametrisation for better results
-The $SoH^{\uparrow}$ in ~\ref{TODO wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
+The $SoH^{\uparrow}$ in ~\ref{fig:wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{SoH up for weight size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
+    \label{fig:wUp}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{SoH down for weight size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
+    \label{fig:wDown}
+  \end{subfigure}
+  \caption{SoH for weight size}
+  \label{fig:SoHWeight}
+\end{figure}
 %
@@
 %	influence on the value
-The last variation we examined was the zoom level. One can see that $G^*$ is always better than Focal $G^*$.
-The target area of Focal $G^*$ increases if you zoom out.
+The last variation we examined was the zoom level. The results can seen in figure ~\ref{fig:SoHZoom}. One can see that $G^*$ is always better than Focal $G^*$.
+The target area of Focal $G^*$ increases with every zoom step.
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{SoH up for focal size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/zUp}
+    \label{fig:zUp}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{SoH down for focal size}
+    \includegraphics[width=\linewidth]{images/whiskerPlot/zDown}
+    \label{fig:zDown}
+  \end{subfigure}
+  \caption{SoH for focal size}
+  \label{fig:SoHZoom}
+\end{figure}
 
 \section{Conclusions and Future Work} \label{sec:Conclusion}
+In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic on a different dataset.
+We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
+is higher.
+Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
+Therefore F should be not less than 65x65. 
+If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
+has the least influence if $G^*$ or Focal $G^*$ performe better.
+We assume that if Focal $G^*$ has a different Focal size for a different zoom level, it performes better, but this is beyond the
+scope of this work.
 
-In this work, we generalized the Getis-Ord statistic to deal with the problem of
-stability inherent in hot spot analysis. We identified possible underlying
-reasons for this instability: The weight matrix as well as the size of the study
-area. We developed a modified approach that deals with those two factors. The
-result is a modified $G^*$ statistic called the \emph{Focal $G^*$ statistic}. It
-reduces the study area used for comparison into regions and achieves through
-this an increase in stability. To determine the effectiveness of our approach,
-we propose a stability metric for hot spots called \emph{SoH}. To our knowledge
-no such metric existed before this work. The SoH computes the ratio of
-dependence of hot spots for different parametrizations of weight matrices. It
-enables to express the stability between each parametrization using single value
-restricted between zero and one. Based on this number one can decide which
-parametrization to use and researchers can compare the stability of their
-methods for unsupervised hot spot analyses. In particular, for temperature
-values one wishes to detect those areas which have high differences regardless
-of a particular parametrization. If a hot spot only appears for one
-parametrization, the information gained for general use is quite small and can
-even lead to an inefficient allocation of resources.
-
-This research has several restrictions which have to be taken into account.
-First, we only tested the $SoH^\uparrow$ metric. While we assume, based on our
-graphical analysis, that the  $SoH^\downarrow$ stability should be similar, we
-have no hard results. The results themselves are tested on two events in time
-for a fixed area of the city of Karlsruhe. We have not tested it on smaller or
-larger study areas, but we assume that the stability of the Focal $G^*$ would
-stay the same whereas the stability of the $G^*$ statistic would increase with a
-smaller study area and decrease with a larger study area. This follows the
-reasoning that the impact of a singular point increases with a decrease of the
-study area. To test this dependency is an interesting task for future work. The
-last restriction is the fixed size in this work of the focal matrix for the
-Focal $G^*$ approach. We only tested one size in this work, but it is highly
-probable that the size of the focal matrix has an impact on the stability as
-could be seen in Fig.~\ref{fig:EvalResults}. While an overall trend can be seen
-in this work when the size of the weight matrix W and the focal matrix F are
-almost identical, the exact ratio is beyond the scope of this work. The optimal
-ratio as well as when the stability suffers from a too similar size are
-interesting question for future work.
+With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
+All our results are based on the SoH. Further work should validate or improve this metric and compare if
+Focal $G^*$ can have better results than $G^*$ in all dimension with fixed weight and focal size.
 

### 2017-06-14 paper-main.tex
Included correct citations Our paper i tried to cite it correctly; contacted editors

@@
 Therefore it is necessary to measure and evaluate the stability of a hotspot analysis as well as the different parametrizations.
-In our initial work (Hier Bruns and VIliam 2017), we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .
+In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .
 Here, we build upon that work and examine in more detail the impact of the different instantiations of the most typical parameter.
-We use the well known Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of this statistic, the focal $G^*$ (citate bruns and viliam).
+We use the well known Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of this statistic, the focal $G^*$~\cite{SoH-GI-Forum}.
 Those parameter are the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix).
@@
 One method, to measure the quality of such a clustering is the compactness of the clusters, see e.g.
-Song 2010 (http://ieeexplore.ieee.org/document/5558958/?part=1).
+\cite{CompactnessDataClustering}.
 This enables the comparison between different clusters.
@@
 For density based clustering, e.g.
-for DBSCAN, OPTICS (Ankerst et al 1999) gives a simple method to tune the essential parameter for this clustering.
+for DBSCAN~\cite{Ester96adensity-based}, OPTICS~\cite{Ankerst:1999:OOP:304181.304187} gives a simple method to tune the essential parameter for this clustering.
 This is only a small overview of methods to influence and measure the quality of different clustering methods.
@@
 values, but instead to focus on local hotspots and to measure the significance
-of those local areas. A more in depth overview of methods to identify and visualize spatial patterns and areas of interest can be found in Shekhar et al (2011).
+of those local areas. A more in depth overview of methods to identify and visualize spatial patterns and areas of interest can be found in \cite{shekhar2011identifying}.
 

### 2017-06-14 paper-main.tex
Updatet conclusion

--- 2017-06-14 paper-main.tex
@@
 Our results indicate a negative impact on the stability with
-an increase of the size of the neighbourhood as well as
+a reduction of the size of the neighbourhood as well as
 a reduction of the size of the study area, regardless of
@@
 
-Our results are based on the cab taxi data set from New York, Manhattan \cite{TODO}. 
+Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
 We used only the dataset of January 2016. From that
@@
 \end{itemize}
-Therefore we calculate around 10*10*5=500 results for each fixed x.
+Therefore we calculate around $10 \cdot 10 \cdot 5=500$ results for each fixed x.
 The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.
@@
 
-\section{Results}
-
 \section{Evaluation}
@@
 %Fig.~\ref{fig:ExampleMatrices}.
-
-\subsection{Clumping}
-
-\subsection{Zoom}
-
-Blueline is Focal $G^*$. Redline is $G^*$
-
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{Upward}
-    \includegraphics[width=\linewidth]{images/SoHZoomUp}
-    \label{fig:UpwardZoom}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{Downward}
-    \includegraphics[width=\linewidth]{images/SoHZoomDown}
-    \label{fig:DownwardZoom}
-  \end{subfigure}
-  \caption{TODO}
-  \label{fig:Zoom}
-\end{figure}
-
-\subsection{Blur}
-
-The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
-the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
-$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
-has a fixed size of $41{\times}41$
-
-\begin{displaymath}
-\SOHUP( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
-\end{displaymath}
-
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{Upward}
-    \includegraphics[width=\linewidth]{images/SoHUpBlur}
-    \label{fig:UpwardBlur}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{Downward}
-    \includegraphics[width=\linewidth]{images/SoHDownBlur}
-    \label{fig:DownwardBlur}
-  \end{subfigure}
-  \caption{TODO}
-  \label{fig:Blur}
-\end{figure}
 
@@
 
+\subsection{Clumping}
+
+\subsection{Zoom}
+
+TODO settings and images
+The zoom level is a slice plane through our three dimensional space. 
+TODO define parent child
+The results can be found in figure ~\ref{fig:Zoom}.
+For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
+\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
+For the downward property, Focal $G^*$ leads to better results at zoom level 5.
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{Upward for zoom}
+    \includegraphics[width=\linewidth]{images/SoHZoomUp}
+    \label{fig:UpwardZoom}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{Downward for zoom}
+    \includegraphics[width=\linewidth]{images/SoHZoomDown}
+    \label{fig:DownwardZoom}
+  \end{subfigure}
+  \caption{SoH zoom}
+  \label{fig:Zoom}
+\end{figure}
+
+\subsection{Blur}
+
+The evaluation results are plotted in Fig.~\ref{fig:Blur}, each point in
+the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
+$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
+has a fixed size of $41{\times}41$
+
+\begin{displaymath}
+\SOHUP( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
+\end{displaymath}
+
+The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
+Higher weight leads in general to better results for Focal $G^*$. $G^*$ doesn't fit to the mean of our whiskerplot.
+
+\begin{figure}[htp]
+  \begin{subfigure}{\linewidth}
+    \caption{Upward for blur}
+    \includegraphics[width=\linewidth]{images/SoHUpBlur}
+    \label{fig:UpwardBlur}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}{\linewidth}
+    \caption{Downward for blur}
+    \includegraphics[width=\linewidth]{images/SoHDownBlur}
+    \label{fig:DownwardBlur}
+  \end{subfigure}
+  \caption{SoH blur}
+  \label{fig:Blur}
+\end{figure}
+
 \section{Conclusions and Future Work} \label{sec:Conclusion}
@@
 With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
-All our results are based on the SoH. Further work should validate or improve this metric and compare if
-Focal $G^*$ can have better results than $G^*$ in all dimension with fixed weight and focal size.
+Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
+stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
+It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
+for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
+All our results are based on the SoH. Further work should validate or improve this metric.
 

### 2017-06-14 paper-main.tex
Extended Results

@@
 The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
-Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
+Zoom size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
 In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
@@
 
-\subsection{Results and Discussion}
+\section{Methode}
+
+The weight size W, focal size F and the zoom level are the 3 parameters we vary.
+Therefore we have a 3 dimensional space. The SoH is defined for every tuple of points.
+We choose to fix one dimension and used the other dimension as our sample group. 
+Out of the sample group we calculate the mean and the standard deviation. 
+In our graph we show the mean and the standard deviation from the mean. 
+We define as a child the previous image out of the fixed dimension.
+
+\section{Results and Discussion}
 
@@
 %	Conclusion: F should be around 65x65 or higher
-In figure ~\ref{fig:fUp} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
-The standard deviation decreases also with a higher focal size. Only 
-at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
-missing, because the weight size W must be smaller than F. When F and W have similar
-size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
-$SoH^{\downarrow}$ in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area.
+
+First we fixed the focal size F as our x-axis. Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
+To evaluate this dimension is essential because if it is not known how big the study area needs to be. Based on these results we want to fix the focal size F
+so that in most cases focal $G^*$ is better than $G^*$.
+In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shwon for $G^*$ and Focal $G^*$.
+Higher values mean that the found hot spots are more stable. The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
+It can see that an increase of the focal size leads to better results for \SOHUP. 
+With a higher focal size you can see that the dotted line which represent the standard deviation is getting smaller.
+Therefore the standard deviation decreases with a higher focal size. Only 
+at focal size F of 17x17 there is no standard deviation. Which is presented with the absent of the dotted line.
+At focal size F 17x17 the standard deviation is missing, because the weight size W must be smaller than F. 
+And for focal size F the values for W which are caluclated are only 3,7,11.
+When F and W have similar size, there are no clusters. Because the values have no much variation. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
+\SOHDOWN can also be calculated with the same images. 
+\SOHDOWN in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area. The standard deviation is not decreasing with an increase of the 
+focal size. Also the standard deviation is missing for the first point.
 
@@
 %	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
-In figure ~\ref{fig:wDown} one can see that an increase of the weight size leads to better results.
-Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
-that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
+Next we fixed the weight dimension as our x-axis. The values are increasing with an increase of the weight size W. 
+Higher values means the results are more stable.
+In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results forh the \SOHUP. 
+We compare $G^*$ (blue line) wiht Focal $G^*$ (red line). The read line is not always above the blue line.
+Therefore Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. It seems 
+that $G^*$ has at 23 and 39 some small break downs. At first glance one would say that some parametrisation leads to that result
+but the standard deviation is decreasing which indicate the opposite.
 The standard deviation is in this area higher than in the other points.
-In figure ~\ref{fig:wUp} the break downs are also visible.
-The high standard deviation indicates that it is possible to use this parametrisation for better results
-The $SoH^{\uparrow}$ in ~\ref{fig:wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.
+In figure ~\ref{fig:wDown} the break downs are also visible which uses the same images as before but calculate the \SOHDOWN.
+The high standard deviation in general indicates that it is possible to use better parametrisation for better results. Which would be the zoom size.
+The break downs at 23 and 39 are also visible but this time the standard deviation is increasing.
+The \SOHDOWN and \SOHUP is mostly better than $G^*$ with fixed x-axis for the weight. 
+Which was the conclusion in \ref{TODO last paper}.
 
@@
 %	influence on the value
-The last variation we examined was the zoom level. The results can seen in figure ~\ref{fig:SoHZoom}. One can see that $G^*$ is always better than Focal $G^*$.
-The target area of Focal $G^*$ increases with every zoom step.
+
+The last variation we examined was the zoom level. There we fixed the x-axis as our zoom level. And the focal size and weight size variation lead to a sample set.
+The results can seen in figure ~\ref{fig:SoHZoom}. For the \SOHUP there is a huge increase between zoom level 3 and 4. This increase can't be seen for \SOHDOWN.
+One can see that $G^*$ is always better than Focal $G^*$. This could be beacause the target area of Focal $G^*$ increases with every zoom step.
 

### 2017-06-14 analysis.Rmd
renamed Rmd file

---
title: "FocalGstar"
author: "Viliam Simko"
date: "June 2, 2017"
output:
  pdf_document: default
  html_document: default
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r setup, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(rgdal)
library(readr)
library(corrplot)

knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/gen-"
)

source("R/hotspot_analysis_lib.R")
set.seed(0)

ZOOM_WMATRIX_SIZE <- 11
FOCAL_MATRIX_SIZE <- 41
MAX_AGGREG_LEVEL <- 8
ZOOMLEVEL <- 3
```

## Loading hi-res raster

Generating new rasters by aggregation
```{r loadraster, cache=TRUE}
hires <- raster("data/hires-raster.tif")

rast <- list()
rast[[1]] <- hires
for (i in 2:MAX_AGGREG_LEVEL) {
  rast[[i]] <- aggregate(hires, fact = i, fun = sum, na.rm = TRUE)
}
```

Rendering the aggregated rasters:
```{r rawdata, cache=TRUE, fig.width=5, fig.height=5}
op <- par(mar = rep(0, 4))
for (i in seq_along(rast)) {
  plot(rast[[i]], xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```
## Demo: Variable resolution (zoom)

### Weight matrix
```{r zoom-wmatrix, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
ZOOM_WMATRIX <- weight_matrix_circular_fade(ZOOM_WMATRIX_SIZE, 0)
ZOOM_WMATRIX[is.na(ZOOM_WMATRIX)] <- 0 # removing any NAs from the weight matrix
plot_weight_matrix(ZOOM_WMATRIX)
```

### Standard G* (zoom)

First, we compute all the gstar rasters.
```{r, echo=FALSE, cache=TRUE}
zoom_gstar <- list()
pb <- txtProgressBar(max = length(rast), style = 3)
for (i in 1:length(rast)) {
  setTxtProgressBar(pb, i)
  r <- rast[[i]]
  zoom_gstar[[i]] <- GetisOrd(r, ZOOM_WMATRIX)
}
close(pb)
```
This code can be used for saving rasters as geotiffs, useful for external processing.
We don't execute the code when generating this document.
```{r, echo=FALSE, eval=FALSE}
z <- 0
for (g in zoom_gstar) {
  z <- z + 1
  writeRaster(g, sprintf("data/zoom/gstar-%03dx%03d-z%02d-w%d.tif",
                         nrow(g), ncol(g), z, nrow(ZOOM_WMATRIX)),
              overwrite = TRUE)

}
```

Now, we want to generate plain images out of the G* rasters:
```{r raw-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_gstar) {
  plot(g, xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```

```{r demo-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
z <- 0
for (g in zoom_gstar) {
  z <- z + 1
  plot_zscore(g,
              title = sprintf("Standard G*: zoom=%d", z),
              sigma_thresh = 2)
}
```

### Focal G* (zoom)

First, we compute all the Focal G* rasters.
```{r, echo=FALSE, cache=TRUE}
zoom_focalgstar <- list()
pb <- txtProgressBar(max = length(rast), style = 3)
for (i in seq_along(rast)) {
  setTxtProgressBar(pb, i)
  r <- rast[[i]]
  st <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
  zoom_focalgstar[[i]] <- GetisOrd(r, ZOOM_WMATRIX, st)
}
close(pb)
```

This code can be used for saving rasters as geotiffs, useful for external processing.
We don't execute the code when generating this document.
```{r, echo=FALSE, eval=FALSE}
z <- 0
for (g in zoom_focalgstar) {
  z <- z + 1
  writeRaster(g, sprintf("data/zoom/focalgstar-%03dx%03d-z%02d-w%d.tif",
                         nrow(g), ncol(g), z, nrow(ZOOM_WMATRIX)),
              overwrite = TRUE)

}
```

Now, we want to generate plain images out of the Focal G* rasters:
```{r raw-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_focalgstar) {
  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```

```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
z <- 0
for (g in zoom_focalgstar) {
  z <- z + 1
  plot_zscore(g,
              title = sprintf("Focal G*: zoom=%d", z),
              sigma_thresh = 2)
}
```

## Demo: Variable weight matrix (blur)
### Weight matrix sizes
```{r}
r <- rast[[ZOOMLEVEL]]
wsizes <- (1:12)*2 + 5
wsizes
```

### Standard G* (blur)
```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
for (ws in wsizes) {

  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix

  g <- GetisOrd(r, w)
  plot_zscore(g,
              title = sprintf("Standard G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/gstar-%03dx%03d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```

### Focal G* (blur)
```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
st <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
for (ws in wsizes) {

  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```
## Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```

## Eval SoH-up
```{r, eval=FALSE}
# expand.grid(
#   zoom = seq_along(rast),
#   wsize = wsizes,
#   soh = NA
# ) ->
#   soh_up_gstar ->
#   soh_up_focalgstar ->
#   soh_down_gstar ->
#   soh_down_focalgstar

# zooms <- 5:length(rast)

# pbmax <- length(wsizes) * length(zooms)
# pbidx <- 0
# pb <- txtProgressBar(max = pbmax, style = 3)

# wgen <- function(ws) {
#   w <- weight_matrix_circular_fade(ws, 0)
#   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
#   w
# }
# 
# results <- matrix(nrow = 0, ncol = 4)
# colnames(results) <- c("zoom",
#                        "wm size",
#                        "soh_up(G*)",
#                        "soh_up(Focal G*)")
# 
# for (zoom in zooms) {
#   
#   r <- rast[[zoom]]
#   st_std <- GetisOrdStandardStats(r)
#   st_foc <- GetisOrdLocalStats(r, weight_matrix_circular(51))
#   
#   std_up <- eval_getisord(r, st_std, wsizes, wgen = wgen)
#   foc_up <- eval_getisord(r, st_foc, wsizes, wgen = wgen)
#   
#   results <- rbind(results, cbind(zoom, wsizes[-1], std_up[,2], foc_up[,2]))

  # plot(res_std, type = "n", ylim = c(0,1))
  # lines(res_std, col = "red")
  # lines(res_foc, col = "blue")

  # for (ws in wsizes) {
  #   w <- weight_matrix_circular_fade(ws, 0)
  #   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  #   
  #   
  #   pbidx <- pbidx + 1
  #   setTxtProgressBar(pb, pbidx)
  # }
# }
# close(pb)
```

```{r, echo=FALSE, message=FALSE}
glob <- read_csv("data/heatmap/aggregatedGlobal.csv")
foc <- read_csv("data/heatmap/aggregatedFocal.csv")
```

```{r, eval=FALSE}
foc %>%
  cor(use = "pairwise.complete.obs") %>%
  corrplot.mixed(order = "FPC", diag = "n", outline = "gray")
```

```{r, eval=FALSE, message=FALSE}
glob %>%
  select(W,Z,Down,Up) %>%
  cor(use = "pairwise.complete.obs") %>%
  corrplot.mixed(diag = "n", outline = "gray")
```

```{r zoom-sohup, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
zoom_soh <- read_csv("data/zoom_soh.csv")

zoom_soh %>% dplyr::select(Zoom, "G*" = UpZoomGstar) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = UpFocalGstar) -> y2

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Zoom level",
     main = "Variable zoom: G* vs Focal G*")

lines(y1, col = "red")
lines(y2, col = "blue")
legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```
```{r zoom-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
zoom_soh <- read_csv("data/zoom_soh.csv")

zoom_soh %>% dplyr::select(Zoom, "G*" = DownZoomGstar) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = DownZoomFocalGstar) -> y2

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Zoom level",
     main = "Variable zoom: G* vs Focal G*")

lines(y1, col = "red")
lines(y2, col = "blue")
legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```

### 2017-06-14 analysis.Rmd
updated colors for G* vs FocalG*

@@
      ylab = expression(SoH[up]),
-     xlab = "Zoom level",
-     main = "Variable zoom: G* vs Focal G*")
+     xlab = "Zoom level")
 
-lines(y1, col = "red")
-lines(y2, col = "blue")
-legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
+lines(y1, col = "blue", lw = 2)
+lines(y2, col = "red", lw = 2)
+legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
 mtext("CI: FMsize and WMsize", line = -1, adj = .98)
 ```
+
 ```{r zoom-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
@@
      ylab = expression(SoH[down]),
-     xlab = "Zoom level",
-     main = "Variable zoom: G* vs Focal G*")
+     xlab = "Zoom level")
 
-lines(y1, col = "red")
-lines(y2, col = "blue")
-legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
+lines(y1, col = "blue", lw = 2)
+lines(y2, col = "red", lw = 2)
+legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
 mtext("CI: FMsize and WMsize", line = -1, adj = .98)

### 2017-06-14 paper-main.tex
updated colors for G* vs FocalG*

@@
     \caption{Upward for zoom}
-    \includegraphics[width=\linewidth]{images/SoHZoomUp}
+    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
     \label{fig:UpwardZoom}
@@
     \caption{Downward for zoom}
-    \includegraphics[width=\linewidth]{images/SoHZoomDown}
+    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
     \label{fig:DownwardZoom}
@@
 
+\begin{figure*}[htp]
+  \centering
+
+  \begin{tabular}{cccccccc}
+    \hline
+    \multicolumn{8}{l}{Multiple aggregation levels} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \hline
+    \multicolumn{8}{l}{G*Multiple aggregation levels} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}
+  \end{tabular}
+
+\end{figure*}
+
 \section{Conclusions and Future Work} \label{sec:Conclusion}

### 2017-06-14 paper-main.tex
Updated conclusion

--- 2017-06-14 paper-main.tex
@@
 
-\subsection{Zoom}
+\subsection{Aggregate}
 
@@
 \section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic on a different dataset.
+In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
+dataset an with a larger dataset. The dataset was only one month projected in one raster. 
 We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
@@
 has the least influence if $G^*$ or Focal $G^*$ performe better.
-We assume that if Focal $G^*$ has a different Focal size for a different zoom level, it performes better, but this is beyond the
-scope of this work.
+We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
+it performes better, but this is beyond the scope of this work.
 
@@
 for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
-All our results are based on the SoH. Further work should validate or improve this metric.
+$G^*$ can also be applied to spatio-temporal data.
+Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
+We now have a good indication which weight and focal size is usefull.
+We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
+One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
+All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.
 

### 2017-06-14 paper-main.tex

@@
 \end{figure}
+
+\begin{figure*}[htp]
+  \centering
+
+  \begin{tabular}{cccccccc}
+    \hline
+    \multicolumn{8}{l}{Multiple aggregation levels} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \hline
+    \multicolumn{8}{l}{G*Multiple aggregation levels} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}
+  \end{tabular}
+
+\end{figure*}
 

### 2017-06-14 analysis.Rmd
Extended script but not testet

@@
 ```
+
+```{r weight, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/w_focal_trued3.csv")
+d3global <- read.csv("data/w_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$W), mean)
+sd <- aggregate(d3$Up, by = list(d3$W), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$W), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$W), sd)
+plot(NA, ylab="Up", xlim=c(0,40), ylim=c(0,1), xlab=sprintf("Weight"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal","Global") , fill=c("red","blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$W), mean)
+sd <- aggregate(d3$Down, by = list(d3$W), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$W), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$W), sd)
+plot(NA, ylab="Down", xlim=c(0,40), ylim=c(0,1), xlab=sprintf("Weight"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+```
+
+```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/a_focal_trued3.csv")
+d3global <- read.csv("data/a_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$Z), mean)
+sd <- aggregate(d3$Up, by = list(d3$Z), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$Z), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$Z), sd)
+plot(NA, ylab="Up", xlim=c(1,5), ylim=c(0,1), xlab=sprintf("Aggregation"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$Z), mean)
+sd <- aggregate(d3$Down, by = list(d3$Z), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$Z), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$Z), sd)
+plot(NA, ylab="Down", xlim=c(1,5), ylim=c(0,1), xlab=sprintf("Aggregation"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+```
+
+```{r focal, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/f_focal_trued3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$F), mean)
+sd <- aggregate(d3$Up, by = list(d3$F), sd)
+plot(NA, ylab="Up", xlim=c(0,150), ylim=c(0,1), xlab=sprintf("Focal"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+legend("topleft", c("Focal G*") , fill=c("red"))
+
+mean <- aggregate(d3$Down, by = list(d3$F), mean)
+sd <- aggregate(d3$Down, by = list(d3$F), sd)
+plot(NA, ylab="Down", xlim=c(0,150), ylim=c(0,1), xlab=sprintf("Focal"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+legend("topleft", c("Focal G*") , fill=c("red"))
+
+```

### 2017-06-15 paper-main.tex
Updated Dataset

@@
 all.
+If $|Children|=0$ or $|Parents|=0$ SoH is 0.
 
@@
 The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
-Zoom size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
-In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
+Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
+For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
 %
@@
 \begin{itemize}
- \item The weight matrix W is from 3 to 43 with a stepsize of 4.
- \item The focal matrix F is from  17 to 125 with a stepsize of 12.
- \item The zoom level is from 1 to 5 with a stepsize of 1.
+ \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
+ \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
+ \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
 \end{itemize}
-Therefore we calculate around $10 \cdot 10 \cdot 5=500$ results for each fixed x.
-The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.
+\begin{definition}
+The SoH for a singled evalution run in the weight dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+The SoH for a singled evalution run in the focal dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+The SoH for a singled evalution run in the aggregation dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+
+\end{definition}
+
+Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
+The following conditions must hold dim(F)>dim(W) and dim(F)<dim(R) which leads e.g. to 460 results in the z dimension.
+The weight size W, focal size F and the aggregation level are the 3 parameters we vary.
+Therefore we have a 3 dimensional space. 
+We choose to fix one dimension and used the other dimension as our sample group. 
+Out of the sample group we calculate the mean and the standard deviation. 
+In our graph we show the mean and the standard deviation from the mean.
 
@@
 
-\section{Methode}
-
-The weight size W, focal size F and the zoom level are the 3 parameters we vary.
-Therefore we have a 3 dimensional space. The SoH is defined for every tuple of points.
-We choose to fix one dimension and used the other dimension as our sample group. 
-Out of the sample group we calculate the mean and the standard deviation. 
-In our graph we show the mean and the standard deviation from the mean. 
-We define as a child the previous image out of the fixed dimension.
-
 \section{Results and Discussion}
@@
 
-First we fixed the focal size F as our x-axis. Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
-To evaluate this dimension is essential because if it is not known how big the study area needs to be. Based on these results we want to fix the focal size F
+First we fixed the focal size F as our x-axis. 
+Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
+To evaluate this dimension is essential because if it is not 
+known how big the study area needs to be. Based on these results we want to fix the focal size F
 so that in most cases focal $G^*$ is better than $G^*$.
 In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shwon for $G^*$ and Focal $G^*$.
-Higher values mean that the found hot spots are more stable. The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
+Higher values mean that the found hot spots are more stable. 
+The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
 It can see that an increase of the focal size leads to better results for \SOHUP. 
@@
 And for focal size F the values for W which are caluclated are only 3,7,11.
-When F and W have similar size, there are no clusters. Because the values have no much variation. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
+When F and W have similar size, there are no clusters. Because the values have no much variation. 
 \SOHDOWN can also be calculated with the same images. 
-\SOHDOWN in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area. The standard deviation is not decreasing with an increase of the 
+\SOHDOWN in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area. 
+The standard deviation is not decreasing with an increase of the 
 focal size. Also the standard deviation is missing for the first point.
@@
 In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results forh the \SOHUP. 
-We compare $G^*$ (blue line) wiht Focal $G^*$ (red line). The read line is not always above the blue line.
+We compare $G^*$ wiht Focal $G^*$ . The Focal $G^*$ is not always above the $G^*$.
 Therefore Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. It seems 
-that $G^*$ has at 23 and 39 some small break downs. At first glance one would say that some parametrisation leads to that result
+that $G^*$ has at 23 and 39 some small break downs. 
+At first glance one would say that some parametrisation leads to that result
 but the standard deviation is decreasing which indicate the opposite.
 The standard deviation is in this area higher than in the other points.
-In figure ~\ref{fig:wDown} the break downs are also visible which uses the same images as before but calculate the \SOHDOWN.
-The high standard deviation in general indicates that it is possible to use better parametrisation for better results. Which would be the zoom size.
+In figure ~\ref{fig:wDown} the break downs are also visible 
+which uses the same images as before but calculate the \SOHDOWN.
+The high standard deviation in general indicates that it is possible 
+to use better parametrisation for better results. Which would be the zoom size.
 The break downs at 23 and 39 are also visible but this time the standard deviation is increasing.
@@
 
-The last variation we examined was the zoom level. There we fixed the x-axis as our zoom level. And the focal size and weight size variation lead to a sample set.
-The results can seen in figure ~\ref{fig:SoHZoom}. For the \SOHUP there is a huge increase between zoom level 3 and 4. This increase can't be seen for \SOHDOWN.
-One can see that $G^*$ is always better than Focal $G^*$. This could be beacause the target area of Focal $G^*$ increases with every zoom step.
+The last variation we examined was the aggregation level. There we fixed the x-axis as our aggregation level. 
+And the focal size and weight size variation lead to a sample set.
+The results can seen in figure ~\ref{fig:SoHZoom}. 
+For the \SOHUP there is a huge increase between aggregation level 4 and 5. This increase can't be seen for \SOHDOWN.
+One can see that $G^*$ is always better than Focal $G^*$. 
+This could be beacause the target area of Focal $G^*$ increases with every aggregation step.
 

### 2017-06-15 paper-main.tex
Updated definitions for blur and aggregation

@@
 
-TODO settings and images
-The zoom level is a slice plane through our three dimensional space. 
-TODO define parent child
+The aggregation level is a slice plane through our three dimensional space. 
+We evalute only the aggregation with fixed W and fixed F.
+\begin{definition} Aggregation run:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
+\end{displaymath}
+\end{definition}
+
 The results can be found in figure ~\ref{fig:Zoom}.
@@
 
-The evaluation results are plotted in Fig.~\ref{fig:Blur}, each point in
-the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
-$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
-has a fixed size of $41{\times}41$
-
+Blur is a slice plane through our three dimensional space. 
+W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
+\begin{definition} Blur run:
 \begin{displaymath}
-\SOHUP( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
+\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
 \end{displaymath}
-
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
+\end{displaymath}
+\begin{displaymath}
+z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
+\end{displaymath}
+\end{definition}
+The blur results are plotted in Fig.~\ref{fig:Blur}.
 The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
-Higher weight leads in general to better results for Focal $G^*$. $G^*$ doesn't fit to the mean of our whiskerplot.
+Higher weight leads in general to better results for Focal $G^*$. 
+$G^*$ doesn't fit to the mean of our whiskerplot.
 

### 2017-06-15 paper-main.tex
Updated aggregation and blur

@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
+
 The SoH for a singled evalution run in the focal dimension is defined as:
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
+
 The SoH for a singled evalution run in the aggregation dimension is defined as:
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
-
 \end{definition}
@@
 
-The results can be found in figure ~\ref{fig:Zoom}.
-For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
-\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
-For the downward property, Focal $G^*$ leads to better results at zoom level 5.
+The results can be found in Fig.~\ref{fig:Zoom}.
+For the upward property, $G^*$ is better than Focal $G^*$ in most cases, compared to the results from figure
+\ref{fig:SoHZoom}. At aggregation level 5 $G^*$ is worse than Focal $G^*$, but at this point $G^*$ was extrem 
+good if you compare it to the whiskerplot in Fig.~\ref{fig:zUp}.
+For \SOHDOWN $G^*$ has its peak for aggregation level 5, which is consistent with Fig.~\ref{fig:zDown}.
+The result in Fig.~\ref{fig:Zoom} where consitent that $G^*$ is always better than Focal $G^*$ but suprisingly 
+we found an outlier.
 
@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
+\SOHUP( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
+\SOHDOWN( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
 \end{displaymath}
@@
 The blur results are plotted in Fig.~\ref{fig:Blur}.
-The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
-Higher weight leads in general to better results for Focal $G^*$. 
-$G^*$ doesn't fit to the mean of our whiskerplot.
+In this slice one can see that $G^*$ leads to better results compared to Focal $G^*$ for \SOHDOWN. 
+This is because focal size F is set
+to 41x41. We saw that a higher focal size leads to better results. We saw in Fig.~\ref{images/whiskerPlot/wDown}
+that an increas of the weight leads to better results. This slice plane is not consistent. Focal $G^*$ is even decreasing.
+For the \SOHUP Focal $G^*$ compared to $G^*$ is equal good if the points are counted. But $G^*$ has a poor performance with the smallest 
+weights. Foal $G^*$ is mostly above 0.4.
 

### 2017-06-15 paper-main.tex
Replaced zoom with aggregation

@@
   \begin{subfigure}{\linewidth}
-    \caption{Upward for zoom}
+    \caption{Upward for aggregation}
     \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
@@
   \begin{subfigure}{\linewidth}
-    \caption{Downward for zoom}
+    \caption{Downward for aggregation}
     \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
@@
   \end{subfigure}
-  \caption{SoH zoom}
+  \caption{SoH aggregation}
   \label{fig:Zoom}
@@
 Therefore F should be not less than 65x65. 
-If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
+If we calculate the SoH for the aggregation level, Getis-Ord leads to better results. In general the aggregation level 
 has the least influence if $G^*$ or Focal $G^*$ performe better.
-We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
+We assume that if Focal $G^*$ has a different focal size for a different aggregation level, 
 it performes better, but this is beyond the scope of this work.
@@
 stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
-It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
+It can also lead to bad result, \SOHUP in the aggregation dimension reaches nearly zero. Therefore we shown that it is important to have a metric
 for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.

### 2017-06-15 paper-main.tex
Fixed spelling

@@
 Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
-We used only the dataset of January 2016. From that
+We only used the dataset of January 2016. From that
 dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
@@
  \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
- \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
- \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
+ \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$, but not for Focal $G^*$.
+ \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster.
 \end{itemize}
@@
 
-Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
+Therefore, we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
 The following conditions must hold dim(F)>dim(W) and dim(F)<dim(R) which leads e.g. to 460 results in the z dimension.
 The weight size W, focal size F and the aggregation level are the 3 parameters we vary.
-Therefore we have a 3 dimensional space. 
+Therefore, we have a 3 dimensional space. 
 We choose to fix one dimension and used the other dimension as our sample group. 
@@
 First we fixed the focal size F as our x-axis. 
-Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
-To evaluate this dimension is essential because if it is not 
-known how big the study area needs to be. Based on these results we want to fix the focal size F
+Therefore, we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
+To evaluate this dimension it is essential to 
+know how big the study area needs to be. Based on these results we want to fix the focal size F
 so that in most cases focal $G^*$ is better than $G^*$.
-In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shwon for $G^*$ and Focal $G^*$.
-Higher values mean that the found hot spots are more stable. 
+In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and Focal $G^*$.
+Higher values means that the found hot spots are more stable. 
 The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
-It can see that an increase of the focal size leads to better results for \SOHUP. 
-With a higher focal size you can see that the dotted line which represent the standard deviation is getting smaller.
-Therefore the standard deviation decreases with a higher focal size. Only 
-at focal size F of 17x17 there is no standard deviation. Which is presented with the absent of the dotted line.
+We can see that an increase of the focal size leads to better results for \SOHUP. 
+With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller.
+Therefore, the standard deviation decreases with a higher focal size. Only 
+at focal size F of 17x17 there is no standard deviation. This is presented with the absent of the dotted line.
 At focal size F 17x17 the standard deviation is missing, because the weight size W must be smaller than F. 
-And for focal size F the values for W which are caluclated are only 3,7,11.
-When F and W have similar size, there are no clusters. Because the values have no much variation. 
+And for focal size F the values for W, which are caluclated, are only 7,11,15.
+When F and W have similar size, there are no clusters because the values have no much variation. 
 \SOHDOWN can also be calculated with the same images. 
@@
 Higher values means the results are more stable.
-In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results forh the \SOHUP. 
+In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results for the \SOHUP. 
 We compare $G^*$ wiht Focal $G^*$ . The Focal $G^*$ is not always above the $G^*$.
-Therefore Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. It seems 
-that $G^*$ has at 23 and 39 some small break downs. 
-At first glance one would say that some parametrisation leads to that result
-but the standard deviation is decreasing which indicate the opposite.
+Therefore, Focal $G^*$ is not always better than $G^*$, which would be a perfect result we hoped for. It seems 
+that $G^*$ has at 27 and 43 some small break downs. 
+At first glance one would say that some parametrisation leads to that result,
+but the standard deviation is decreasing, which indicate the opposite.
 The standard deviation is in this area higher than in the other points.
 In figure ~\ref{fig:wDown} the break downs are also visible 
-which uses the same images as before but calculate the \SOHDOWN.
+The same images as before are used, but the \SOHDOWN is calculated.
 The high standard deviation in general indicates that it is possible 
-to use better parametrisation for better results. Which would be the zoom size.
-The break downs at 23 and 39 are also visible but this time the standard deviation is increasing.
+to use better parametrisation for better results, which would be the aggregation size.
+The break downs at 27 and 43 are also visible, but this time the standard deviation is increasing.
 The \SOHDOWN and \SOHUP is mostly better than $G^*$ with fixed x-axis for the weight. 
-Which was the conclusion in \ref{TODO last paper}.
+That was the conclusion in \ref{TODO last paper}.
 
@@
 And the focal size and weight size variation lead to a sample set.
-The results can seen in figure ~\ref{fig:SoHZoom}. 
+The results can be seen in figure ~\ref{fig:SoHZoom}. 
 For the \SOHUP there is a huge increase between aggregation level 4 and 5. This increase can't be seen for \SOHDOWN.
@@
 The results can be found in Fig.~\ref{fig:Zoom}.
-For the upward property, $G^*$ is better than Focal $G^*$ in most cases, compared to the results from figure
-\ref{fig:SoHZoom}. At aggregation level 5 $G^*$ is worse than Focal $G^*$, but at this point $G^*$ was extrem 
+For the upward property $G^*$ is better than Focal $G^*$ in most cases, compared to the results from figure
+\ref{fig:SoHZoom}. At aggregation level 5 $G^*$ is worse than Focal $G^*$, but at this point $G^*$ is extreme 
 good if you compare it to the whiskerplot in Fig.~\ref{fig:zUp}.
 For \SOHDOWN $G^*$ has its peak for aggregation level 5, which is consistent with Fig.~\ref{fig:zDown}.
-The result in Fig.~\ref{fig:Zoom} where consitent that $G^*$ is always better than Focal $G^*$ but suprisingly 
+The result in Fig.~\ref{fig:Zoom} are consistent that $G^*$ is always better than Focal $G^*$, but suprisingly 
 we found an outlier.
@@
 Blur is a slice plane through our three dimensional space. 
-W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
+W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level are fixed.
 \begin{definition} Blur run:
@@
 to 41x41. We saw that a higher focal size leads to better results. We saw in Fig.~\ref{images/whiskerPlot/wDown}
-that an increas of the weight leads to better results. This slice plane is not consistent. Focal $G^*$ is even decreasing.
-For the \SOHUP Focal $G^*$ compared to $G^*$ is equal good if the points are counted. But $G^*$ has a poor performance with the smallest 
-weights. Foal $G^*$ is mostly above 0.4.
+that an increase of the weight leads to better results. This slice plane is not consistent. Focal $G^*$ is even decreasing.
+For the \SOHUP Focal $G^*$ compared to $G^*$ is equal good if the points are counted, but $G^*$ has a poor performance with the smallest 
+weights. Focal $G^*$ is mostly above 0.4.
 
@@
 \section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
-dataset an with a larger dataset. The dataset was only one month projected in one raster. 
+In this work we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
+We validated the results from \ref{TODO last paper} with a real world 
+dataset and with a larger dataset. The dataset was only one month projected in one raster. 
 We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
@@
 Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
-Therefore F should be not less than 65x65. 
+Therefore, F should be not less than 65x65. 
 If we calculate the SoH for the aggregation level, Getis-Ord leads to better results. In general the aggregation level 
@@
 With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
-Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
-stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
-It can also lead to bad result, \SOHUP in the aggregation dimension reaches nearly zero. Therefore we shown that it is important to have a metric
-for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
+Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child,
+has a huge impact on the
+stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension 
+around 0.6.
+It can also lead to bad results, \SOHUP in the aggregation dimension reaches nearly zero. Therefore, we shown that it is important 
+to have a metric
+for the stability of hotspots. We also presented indication which parametrisation should be avoided and which parametrisations 
+are promising.
 $G^*$ can also be applied to spatio-temporal data.
-Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
+Therefore, Focal $G^*$ should be also applied to the spatio-temporal data. 
 We now have a good indication which weight and focal size is usefull.
-We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
-One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
+We didn't evaluate the results on other months because we assume that they are similar, but it is interesting to find clusters 
+for the different times in the day.
+One could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
 All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.

### 2017-06-15 paper-main.tex
restructured chapters and reewrote stuff in evaluation and discussiion as all as added reference to our original SoH paper in the focal G* descritpion

--- 2017-06-15 paper-main.tex
@@
 
-\subsection{Dataset}
-
-Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
-We used only the dataset of January 2016. From that
-dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
-The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
-Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
-For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
-%
-For our measurements we specified the following data series:
-\begin{itemize}
- \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
- \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
- \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
-\end{itemize}
-\begin{definition}
-The SoH for a singled evalution run in the weight dimension is defined as:
-\begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-\end{displaymath}
-
-The SoH for a singled evalution run in the focal dimension is defined as:
-\begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-\end{displaymath}
-
-The SoH for a singled evalution run in the aggregation dimension is defined as:
-\begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-\end{displaymath}
-\end{definition}
-
-Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
-The following conditions must hold dim(F)>dim(W) and dim(F)<dim(R) which leads e.g. to 460 results in the z dimension.
-The weight size W, focal size F and the aggregation level are the 3 parameters we vary.
-Therefore we have a 3 dimensional space. 
-We choose to fix one dimension and used the other dimension as our sample group. 
-Out of the sample group we calculate the mean and the standard deviation. 
-In our graph we show the mean and the standard deviation from the mean.
-
-\subsection{Method}
-
-In the following text, we use the notation \FOCAL{R}{M}{op} to denote a focal
+Section is analog to \cite{SoH-GI-Forum} and incorporates the most important definitions for the computation.
+We use the notation \FOCAL{R}{M}{op} to denote a focal
 operation $op$ applied on a raster $R$ with a focal window determined by a
@@
 
-- To evaluate, we compare G* with FocalG* on the same dataset.
-- We use NY taxi dropoffs
-- a single evaluation run is defined in Def.~\ref{def:EvalRun}.
-- In an ideal case, we could produce a 3D-plot:
-  - x-axis would be growing pixel sizes 100..1000 by 100 (aka zoom-out)
-  - y-axis would be growing weight matrix sizes (e.g. 5..41 by 2)
-  - z-axis would be performance of G* vs FocalG* x and y coordinates
-  - we could also repeat the computation for multiple datasets to obtain 
-  multiple samples and to compute error bars.
-- due to paper size limit, we choose projection in which matrix size is set to 
-constant 7x7 pixels and the only variable is the pixel size. This way, we 
-produce a 2D plot. We also generate just a single sample.
+\subsection{Dataset}
+
+We evaluate our data on the New York city yellow cab data set \footnote{http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml}.
+This data set includes all taxi drives from the yellow cabs in New York City, from location, to passengers and many more informations.
+In this study, we compare the total pickups over January from 2016 in the Manhattan area.
+The borders of the rasters are (40.699607, -74.020265) and (40.769239, -73.948286).
+By using this data set, we reduce the computational effort while still being able to show the applicability on real world data and problems.
+\subsection{Treatments}
 
@@
 
+Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
+For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
+%
+For our measurements we specified the following data series:
+\begin{itemize}
+ \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
+ \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
+ \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
+\end{itemize}
+\begin{definition}
+The SoH for a singled evalution run in the weight dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+The SoH for a singled evalution run in the focal dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+The SoH for a singled evalution run in the aggregation dimension is defined as:
+\begin{displaymath}
+\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\end{displaymath}
+\begin{displaymath}
+z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+\end{displaymath}
+
+\end{definition}
+
+Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
+The following conditions must hold dim(F)>dim(W) and dim(F)<dim(R) which leads e.g. to 460 results in the z dimension.
+We vary over the weight matrix W, the focal matrix F and the aggregation level, as motivated in the introduction.
+To compare the impact each of these parameters has we compute all variations over two parameter and holding one parameter fix.
+We then calculate the mean as well as the standard deviation for the SoH for the fixed value based on the two other parameters.
+This allows us to isolate the impact of the variation in the single parameter.
+The results are then plotted in Fig.
+1-6, one graphic for each fixed parameter and the direction of the SoH.
+The hotspots to use the SoH on are computed by the focal $G^*$ and standard $G^*$ method.
+The focal $G^*$ allows us, to isolate the impact that the size of the study area has on the stability of the results without recomputing the total dataset.
+
 \section{Results and Discussion}
@@
 %	Conclusion: F should be around 65x65 or higher
-
-First we fixed the focal size F as our x-axis. 
-Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
-To evaluate this dimension is essential because if it is not 
-known how big the study area needs to be. Based on these results we want to fix the focal size F
-so that in most cases focal $G^*$ is better than $G^*$.
-In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shwon for $G^*$ and Focal $G^*$.
-Higher values mean that the found hot spots are more stable. 
+\subsection{Impact of study area}
+The first parameter we want to isolate is the size of the study area. This enables us to discuss the optimal size of the study area for the given research/decision question. 
+To do so, we have to fix the focal size F and use it as the x-axis and plot the mean value as well as the mean +- the standard deviations of the SoH for all other parameter combinations as the y-axis.
+In this scenario, only the Focal $G^*$ can produce varied results as the standard $G^*$ has by definition a fixed study area by always using the total size of the study area. 
+In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and Focal $G^*$.
+Higher values indicate that the found hot spots are more stable. 
 The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
 It can see that an increase of the focal size leads to better results for \SOHUP. 
-With a higher focal size you can see that the dotted line which represent the standard deviation is getting smaller.
+With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller. This indicates that
+
 Therefore the standard deviation decreases with a higher focal size. Only 
@@
 %	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
+\subsection{Impact of Weight matrix}
 Next we fixed the weight dimension as our x-axis. The values are increasing with an increase of the weight size W. 
@@
 %	influence on the value
-
+\subsection{Impact of Aggregation level}
 The last variation we examined was the aggregation level. There we fixed the x-axis as our aggregation level. 
@@
 
-The results can be found in Fig.~\ref{fig:Zoom}.
-For the upward property, $G^*$ is better than Focal $G^*$ in most cases, compared to the results from figure
-\ref{fig:SoHZoom}. At aggregation level 5 $G^*$ is worse than Focal $G^*$, but at this point $G^*$ was extrem 
-good if you compare it to the whiskerplot in Fig.~\ref{fig:zUp}.
-For \SOHDOWN $G^*$ has its peak for aggregation level 5, which is consistent with Fig.~\ref{fig:zDown}.
-The result in Fig.~\ref{fig:Zoom} where consitent that $G^*$ is always better than Focal $G^*$ but suprisingly 
-we found an outlier.
+The results can be found in figure ~\ref{fig:Zoom}.
+For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
+\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
+For the downward property, Focal $G^*$ leads to better results at zoom level 5.
 
@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
+\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{7+(i-1) \cdot 2}, st, F), G^*(R_{z}, W_{7+i \cdot 2}, st, F) )
+\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
 \end{displaymath}
@@
 The blur results are plotted in Fig.~\ref{fig:Blur}.
-In this slice one can see that $G^*$ leads to better results compared to Focal $G^*$ for \SOHDOWN. 
-This is because focal size F is set
-to 41x41. We saw that a higher focal size leads to better results. We saw in Fig.~\ref{images/whiskerPlot/wDown}
-that an increas of the weight leads to better results. This slice plane is not consistent. Focal $G^*$ is even decreasing.
-For the \SOHUP Focal $G^*$ compared to $G^*$ is equal good if the points are counted. But $G^*$ has a poor performance with the smallest 
-weights. Foal $G^*$ is mostly above 0.4.
+The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
+Higher weight leads in general to better results for Focal $G^*$. 
+$G^*$ doesn't fit to the mean of our whiskerplot.
 

### 2017-06-15 analysis.Rmd

--- 2017-06-14 analysis.Rmd
@@
 ```
+
+```{r weight, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/w_focal_trued3.csv")
+d3global <- read.csv("data/w_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$W+4), mean)
+sd <- aggregate(d3$Up, by = list(d3$W+4), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$W+4), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$W+4), sd)
+plot(NA, ylab="Up", xlim=c(7,43), ylim=c(0,1), xlab=sprintf("Weight"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal","Global") , fill=c("red","blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$W+4), mean)
+sd <- aggregate(d3$Down, by = list(d3$W+4), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$W+4), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$W+4), sd)
+plot(NA, ylab="Down", xlim=c(7,43), ylim=c(0,1), xlab=sprintf("Weight"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+```
+
+```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/a_focal_trued3.csv")
+d3global <- read.csv("data/a_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$Z+1), mean)
+sd <- aggregate(d3$Up, by = list(d3$Z+1), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$Z+1), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$Z+1), sd)
+plot(NA, ylab="Up", xlim=c(2,6), ylim=c(0,1), xlab=sprintf("Aggregation"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$Z+1), mean)
+sd <- aggregate(d3$Down, by = list(d3$Z+1), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$Z+1), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$Z+1), sd)
+plot(NA, ylab="Down", xlim=c(2,6), ylim=c(0,1), xlab=sprintf("Aggregation"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+plotCI(x=meanG$Group.1, y=meanG$x, uiw=sdG$x, err="y", pch=20, slty=3, scol = "blue", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+lines(meanG$Group.1, meanG$x, col="blue", lw=4)
+legend("topleft", c("Focal G*","G*") , fill=c("red","blue"))
+
+```
+
+```{r focal, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/f_focal_trued3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$F+12), mean)
+sd <- aggregate(d3$Up, by = list(d3$F+12), sd)
+plot(NA, ylab="Up", xlim=c(29,137), ylim=c(0,1), xlab=sprintf("Focal"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+legend("topleft", c("Focal G*") , fill=c("red"))
+
+mean <- aggregate(d3$Down, by = list(d3$F+12), mean)
+sd <- aggregate(d3$Down, by = list(d3$F+12), sd)
+plot(NA, ylab="Down", xlim=c(29,137), ylim=c(0,1), xlab=sprintf("Focal"))
+plotCI(x=mean$Group.1, y=mean$x, uiw=sd$x, err="y", pch=20, slty=3, scol = "red", add=TRUE)
+lines(mean$Group.1, mean$x, col="red", lw=4)
+legend("topleft", c("Focal G*") , fill=c("red"))
+
+```

### 2017-06-15 paper-main.tex
Rewrote 2 subsesctions in results + discussion

@@
 
-We evaluate our data on the New York city yellow cab data set \footnote{http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml}.
+We evaluate our data on the New York city yellow cab data set \footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}.
 This data set includes all taxi drives from the yellow cabs in New York City, from location, to passengers and many more informations.
@@
 It can see that an increase of the focal size leads to better results for \SOHUP. 
-With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller. This indicates that
-
-Therefore the standard deviation decreases with a higher focal size. Only 
-at focal size F of 17x17 there is no standard deviation. Which is presented with the absent of the dotted line.
-At focal size F 17x17 the standard deviation is missing, because the weight size W must be smaller than F. 
-And for focal size F the values for W which are caluclated are only 3,7,11.
+With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller.
+This indicates that an increase in the size of the study area does not only lead to an overall increase of stability but also that the it reduces the volatility of the variations in other parameters.
 When F and W have similar size, there are no clusters. Because the values have no much variation. 
-\SOHDOWN can also be calculated with the same images. 
-\SOHDOWN in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area. 
+\SOHDOWN (figure ~\ref{fig:fDown})shows a different picture then the \SOHUP.
+It reaches its maximum SoH for a focal size F of 65x65 in our evaluation set. 
 The standard deviation is not decreasing with an increase of the 
-focal size. Also the standard deviation is missing for the first point.
+focal size.
 
@@
 %	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
-\subsection{Impact of Weight matrix}
-Next we fixed the weight dimension as our x-axis. The values are increasing with an increase of the weight size W. 
-Higher values means the results are more stable.
-In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results forh the \SOHUP. 
-We compare $G^*$ wiht Focal $G^*$ . The Focal $G^*$ is not always above the $G^*$.
-Therefore Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. It seems 
-that $G^*$ has at 23 and 39 some small break downs. 
-At first glance one would say that some parametrisation leads to that result
-but the standard deviation is decreasing which indicate the opposite.
-The standard deviation is in this area higher than in the other points.
-In figure ~\ref{fig:wDown} the break downs are also visible 
-which uses the same images as before but calculate the \SOHDOWN.
-The high standard deviation in general indicates that it is possible 
-to use better parametrisation for better results. Which would be the zoom size.
-The break downs at 23 and 39 are also visible but this time the standard deviation is increasing.
-The \SOHDOWN and \SOHUP is mostly better than $G^*$ with fixed x-axis for the weight. 
-Which was the conclusion in \ref{TODO last paper}.
+\subsection{Impact of Neighbourhood size}
+Next, we want to isolate the effect of the neighbourhood size by fixing the weight matrix size W and using it as x-axis.
+With the impact of the weight matrix W we gain information on how far the interconnectness is between different points as indicated in \cite{Getis.1992}.
+The results for the weight matrix can be seen in figure ~\ref{fig:wUp} for \SOHUP and figure ~\ref{fig:wDown} for \SOHDOWN.
+Here it can be seen that in general for both evaluations metrics as well as the different hot spot methods an increase in the size of the weight matrix W leads to more stable results as well as that the Focal $G^*$ matrix is slightly more stable in most cases for the mean values.
+An interesting phenomena is the dip in stability for the standard $G^*$ for the value of 39.
+Despite our effort we could not determine the reason behind this result, as no overall trend could be extracted.
+The standard deviation shows similar no particular trend, but for the values above 37 is increasing.
+We assume that the reason behind this effect is the inclusion of the water near Manhattan, which leads to a stronger differentiation between areas near water and areas more in the inner city.
+by increasing the weight matrix, the number of points which are influenced increase in number.
+The other parameter can regulate this impact and therefore the variance is stronger.
 

### 2017-06-15 paper-main.tex
subsections

@@
 \subsection{Impact of Aggregation level}
-The last variation we examined was the aggregation level. There we fixed the x-axis as our aggregation level. 
-And the focal size and weight size variation lead to a sample set.
-The results can seen in figure ~\ref{fig:SoHZoom}. 
+Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis.
+We fix the aggregation and use it as x-axis.
+This allows us to examine the impact the resolution of a data set has on the results and allow us indirectly to reduce the computational effort on future computations by using the maximal aggregation as useful.
+The results can seen in figure ~\ref{fig:SoHZoom} and ~\ref{fig:DownwardZoom}.
+First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.
+
 For the \SOHUP there is a huge increase between aggregation level 4 and 5. This increase can't be seen for \SOHDOWN.

### 2017-06-15 paper-main.tex
row of images

@@
   \centering
-
   \begin{tabular}{cccccccc}
-    \hline
     \multicolumn{8}{l}{Multiple aggregation levels} \\
@@
   \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{G* Multiple aggregation levels} \\
     \hline
-    \multicolumn{8}{l}{G*Multiple aggregation levels} \\
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Focal G* Multiple aggregation levels} \\
     \hline
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
   \end{tabular}
 
+  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohup-1}
+  \hspace{1em}
+  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohdown-1}
+
+  \caption{
+    This image shows all aggregation levels for G* and Focal G* together 
+    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
 \end{figure*}

### 2017-06-15 analysis.Rmd
minor code refactoring

--- 2017-06-14 analysis.Rmd
@@
 library(corrplot)
+library(plotrix)
 
@@
 
+```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
+for(ws in wsizes) {
+  w <- weight_matrix_circular_fade(ws, 0)
+  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
+  plot_weight_matrix(w)
+}
+```
+
 ### Standard G* (blur)
@@
 ```
-## Parent-Child Clumping Difference
+## Example of Parent-Child Clumping Difference
 ```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
@@
 
-## Eval SoH-up
-```{r, eval=FALSE}
-# expand.grid(
-#   zoom = seq_along(rast),
-#   wsize = wsizes,
-#   soh = NA
-# ) ->
-#   soh_up_gstar ->
-#   soh_up_focalgstar ->
-#   soh_down_gstar ->
-#   soh_down_focalgstar
-
-# zooms <- 5:length(rast)
-
-# pbmax <- length(wsizes) * length(zooms)
-# pbidx <- 0
-# pb <- txtProgressBar(max = pbmax, style = 3)
-
-# wgen <- function(ws) {
-#   w <- weight_matrix_circular_fade(ws, 0)
-#   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
-#   w
-# }
-# 
-# results <- matrix(nrow = 0, ncol = 4)
-# colnames(results) <- c("zoom",
-#                        "wm size",
-#                        "soh_up(G*)",
-#                        "soh_up(Focal G*)")
-# 
-# for (zoom in zooms) {
-#   
-#   r <- rast[[zoom]]
-#   st_std <- GetisOrdStandardStats(r)
-#   st_foc <- GetisOrdLocalStats(r, weight_matrix_circular(51))
-#   
-#   std_up <- eval_getisord(r, st_std, wsizes, wgen = wgen)
-#   foc_up <- eval_getisord(r, st_foc, wsizes, wgen = wgen)
-#   
-#   results <- rbind(results, cbind(zoom, wsizes[-1], std_up[,2], foc_up[,2]))
-
-  # plot(res_std, type = "n", ylim = c(0,1))
-  # lines(res_std, col = "red")
-  # lines(res_foc, col = "blue")
-
-  # for (ws in wsizes) {
-  #   w <- weight_matrix_circular_fade(ws, 0)
-  #   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
-  #   
-  #   
-  #   pbidx <- pbidx + 1
-  #   setTxtProgressBar(pb, pbidx)
-  # }
-# }
-# close(pb)
-```
-
 ```{r, echo=FALSE, message=FALSE}
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, echo=FALSE}
 foc %>%
@@
 
-zoom_soh %>% dplyr::select(Zoom, "G*" = UpZoomGstar) -> y1
-zoom_soh %>% dplyr::select(Zoom, "Focal G*" = UpFocalGstar) -> y2
+zoom_soh %>% dplyr::select(Zoom, "G*" = UpZoom) -> y1
+zoom_soh %>% dplyr::select(Zoom, "Focal G*" = UpFocalZoom) -> y2
 
@@
 
-zoom_soh %>% dplyr::select(Zoom, "G*" = DownZoomGstar) -> y1
-zoom_soh %>% dplyr::select(Zoom, "Focal G*" = DownZoomFocalGstar) -> y2
+zoom_soh %>% dplyr::select(Zoom, "G*" = DownZoom) -> y1
+zoom_soh %>% dplyr::select(Zoom, "Focal G*" = DownFocalZoom) -> y2
 
@@
 ```
+
+```{r weight, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+d3 <- read.csv("data/w_focal_trued3.csv")
+d3global <- read.csv("data/w_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$W + 4), mean)
+sd <- aggregate(d3$Up, by = list(d3$W + 4), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$W + 4), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$W + 4), sd)
+
+plot(NA,
+     ylab = expression(SoH^Up),
+     xlab = sprintf("Weight matrix size"),
+     xlim = c(7,43), ylim = c(0,1))
+plotCI(x = mean$Group.1,
+       y = mean$x,
+       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
+plotCI(x = meanG$Group.1,
+       y = meanG$x,
+       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
+legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$W + 4), mean)
+sd <- aggregate(d3$Down, by = list(d3$W + 4), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$W + 4), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$W + 4), sd)
+
+plot(NA,
+     ylab = expression(SoH^Down),
+     xlab = sprintf("Weight matrix size"),
+     xlim = c(7,43), ylim = c(0,1))
+plotCI(x = mean$Group.1,
+       y = mean$x,
+       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
+plotCI(x = meanG$Group.1,
+       y = meanG$x,
+       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
+legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
+
+```
+
+```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+d3 <- read.csv("data/a_focal_trued3.csv")
+d3global <- read.csv("data/a_focal_falsed3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
+sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
+meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
+sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
+plot(NA,
+     ylab = expression(SoH^Up),
+     xlab = sprintf("Aggregation levels"),
+     xlim = c(2,6), ylim = c(0,1))
+plotCI(x = mean$Group.1,
+       y = mean$x,
+       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
+plotCI(x = meanG$Group.1,
+       y = meanG$x,
+       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
+legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
+
+mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
+sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
+meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
+sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
+plot(NA, 
+     ylab = expression(SoH^Down),
+     xlab = sprintf("Aggregation levels"),
+     xlim = c(2,6), ylim = c(0,1))
+plotCI(x = mean$Group.1,
+       y = mean$x,
+       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
+plotCI(x = meanG$Group.1,
+       y = meanG$x,
+       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
+legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
+```
+
+```{r focal, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+
+d3 <- read.csv("data/f_focal_trued3.csv")
+
+mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
+sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
+plot(NA,
+     ylab = expression(SoH^Up),
+     xlab = "Focal matrix size",
+     xlim = c(29, 137), ylim = c(0, 1))
+plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
+       scol = "red", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+legend("topleft", c("Focal G*") , fill = c("red"))
+
+mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
+sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
+plot(NA,
+     ylab = expression(SoH^Down),
+     xlab = "Focal matrix size",
+     xlim = c(29,137), ylim = c(0,1))
+plotCI(x = mean$Group.1,
+       y = mean$x,
+       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
+lines(mean$Group.1, mean$x, col = "red", lw = 4)
+legend("topleft", c("Focal G*") , fill = c("red"))
+
+```

### 2017-06-15 R/hotspot_analysis_lib.R
added missing library

@@ -1,0 +1,550 @@
+library(raster)
+library(scales)
+
+# Preprocessing ----------------------------------------------------------------
+
+#' Helper function that can be used for picking the extend manually from
+#' a plotted raster. (use mouse to pick coordinates on the map)
+#' @param r raster
+#' @return \link{Extent} object representing the selected area
+select_extent_manually <- function(r) {
+  plot(r)
+  drawExtent()
+}
+
+
+# Plotting functions -----------------------------------------------------------
+
+plot_color_table <- function(ct) {
+  x <- raster(nrows = length(ct), ncols = 1, vals = 0:(length(ct) - 1))
+  par(mar = c(0,1,0,1))
+  plot(x, col = ct, axes = FALSE, box = FALSE)
+}
+
+interpolate_colortable <- function(howmany, ...) {
+  cmap <- colorRampPalette(c(...))
+  scols <- col2rgb(cmap(howmany))
+  apply(scols, 2, function(c) rgb(c[1]/255, c[2]/255, c[3]/255))
+}
+
+plot_temp_map <- function(
+  r, title,
+  colorscale_title = "",
+  contour_thresh = NULL,
+  contour_quantiles = NULL,
+  contour_col = c("blue", "red"),
+  ctable = interpolate_colortable(howmany = 100,
+                                  "blue", "green", "yellow", "red"),
+  topn = 0, bottomn = 0)
+{
+  if (!is.null(contour_quantiles)) {
+    contour_thresh <- quantile(r, probs = contour_quantiles, na.rm = TRUE)
+  }
+
+  alpha_of_map <- ifelse( is.null(contour_thresh), 1, .4)
+
+  # plot
+  par(mar = c(4,5,4,2) + .1)
+  plot(r, col = alpha(ctable, alpha_of_map),
+       axes = FALSE,
+       #main = title,
+       legend.args = list(text = colorscale_title,
+                          side = 3, font = 2, line = 0, cex = 0.8)
+  )
+
+  # top-order
+  xyFromCell(r, 1:ncell(r)) %>%
+    as.data.frame %>%
+    dplyr::select(lon = x, lat = y) %>%
+    mutate(score = values(r)) -> XY
+
+  if (topn > 0) {
+    XY %>% arrange(-score) %>% head(topn) %>%
+      points(pch = "O", cex = 3, col = "#aa0000")
+  }
+
+  if (bottomn > 0) {
+    XY %>% arrange(score) %>% head(bottomn) %>%
[…]

### 2017-06-15 paper-main.tex
using the auto-generated images
updated images

@@
     \caption{SoH up for focal size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/fUp}
+    \includegraphics[width=\linewidth]{images/gen-focal-1}
     \label{fig:fUp}
@@
     \caption{SoH down for focal size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/fDown}
+    \includegraphics[width=\linewidth]{images/gen-focal-2}
     \label{fig:fDown}
   \end{subfigure}
-  \caption{SoH for focal size}
+  \caption{SoH for focal matrix size}
   \label{fig:SoHFocal}
@@
     \caption{SoH up for weight size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
+    \includegraphics[width=\linewidth]{images/gen-weight-1}
     \label{fig:wUp}
@@
     \caption{SoH down for weight size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
+    \includegraphics[width=\linewidth]{images/gen-weight-2}
     \label{fig:wDown}
@@
     \caption{SoH up for focal size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/zUp}
+    \includegraphics[width=\linewidth]{images/gen-aggregation-1}
     \label{fig:zUp}
@@
     \caption{SoH down for focal size}
-    \includegraphics[width=\linewidth]{images/whiskerPlot/zDown}
+    \includegraphics[width=\linewidth]{images/gen-aggregation-2}
     \label{fig:zDown}
@@
 
+\begin{figure*}[htp]
+  \centering
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{G* Multiple weight matrix sizes} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Focal G* Multipleweight matrix sizes} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
+  \end{tabular}
+
+  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohup-1}
+  \hspace{1em}
+  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohdown-1}
+
+  \caption{
+    This image shows all aggregation levels for G* and Focal G* together 
+    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
+\end{figure*}
+
 \section{Conclusions and Future Work} \label{sec:Conclusion}

### 2017-06-15 R/hotspot_analysis_lib.R
new params for plot_weight_matrix()

@@ -274,26 +274,29 @@ eval_getisord <- function(
 
 # Weight matrix ----------------------------------------------------------------
 
-plot_weight_matrix <- function(w, show.legend = TRUE) {
+plot_weight_matrix <- function(w, show.dim = TRUE, show.minmax = TRUE) {
   # sanity check
   stopifnot(is.matrix(w))
-  stopifnot(is.logical(show.legend))
+  stopifnot(is.logical(show.dim))
+  stopifnot(is.logical(show.minmax))
 
   col <- gray.colors(100)
   image(w, col = col, axes = FALSE, asp = 1)
 
-  if (show.legend) {
-    # matrix dimensions
+  # matrix dimensions
+  if (show.dim) {
     legend(1,1,
            xjust = 1,
            yjust = 1,
-           bg = rgb(0,0,0,.3),
-           border = rgb(1,1,1,.5),
+           bg = rgb(0,0,0,.5),
+           border = rgb(1,1,1,.7),
            text.col = "white",
            legend = c( sprintf("%d x %d", nrow(w), ncol(w)) )
            )
+  }
 
-    # min/max values
+  # min/max values
+  if (show.minmax) {
     legend(1,0,
            xjust = 1,
            yjust = 0,

### 2017-06-15 analysis.Rmd
new wmatrix images

@@
   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
-  plot_weight_matrix(w)
+  plot_weight_matrix(w, show.minmax = FALSE)
 }

### 2017-06-15 analysis.Rmd
improved raster colors

@@
 ZOOMLEVEL <- 3
+COLORMAP <- interpolate_colortable(
+  howmany = 100, "black", "blue", "yellow", "red")
+
 ```
@@
 for (i in seq_along(rast)) {
-  plot(rast[[i]], xlab = NA, ylab = NA,
-       legend = FALSE, axes = FALSE, box = FALSE)
+  plot(log(rast[[i]]), xlab = NA, ylab = NA,
+       legend = FALSE, axes = FALSE, box = FALSE,
+       col = COLORMAP, colNA = "black")
 }
@@
   plot(g, xlab = NA, ylab = NA,
-       legend = FALSE, axes = FALSE, box = FALSE)
+       legend = FALSE, axes = FALSE, box = FALSE, col = COLORMAP, colNA = "black")
 }
@@
 for (g in zoom_focalgstar) {
-  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE)
+  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE,
+       col = COLORMAP, colNA = "black")
 }

### 2017-06-15 analysis.Rmd
wmatrix images

@@
 wsizes <- (1:12)*2 + 5
-wsizes
+wsizes # printed
+
+# selection to be rendered for latex inclusion
+RENDERED_IDX <- floor(seq(1, length(wsizes), length.out = 8))
 ```
 
+We render `r length(RENDERED_IDX)` weight matrices that will be included into a LaTeX document. In order to do this, we selected indices `r RENDERED_IDX`:
 ```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
-for(ws in wsizes) {
+for (ws in wsizes[RENDERED_IDX]) {
   w <- weight_matrix_circular_fade(ws, 0)
@@
 ```
+
 ## Example of Parent-Child Clumping Difference

### 2017-06-15 analysis.Rmd
changed code for generating Standard G* (blur)

@@
 
-```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
+```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
 z <- 0
@@
 ### Standard G* (blur)
-```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
+First, we pre-compute the rasters
+```{r, echo=FALSE, cache=TRUE}
+blur_gstar <- list()
+pb <- txtProgressBar(max = last(wsizes), style = 3)
 for (ws in wsizes) {
+  setTxtProgressBar(pb, ws)
 
@@
 
-  g <- GetisOrd(r, w)
+  blur_gstar[[length(blur_gstar) + 1]] <- GetisOrd(r, w)
+}
+close(pb)
+```
+
+```{r, eval=FALSE, echo=FALSE}
+for (i in seq_along(wsizes)) {
+  ws <- wsizes[i]
+  g <- blur_gstar[[i]]
+  writeRaster(g,
+              sprintf("data/blur/gstar-%03dx%03d-z%02d-w%02d.tif",
+                      nrow(g), ncol(g), ZOOMLEVEL, ws),
+              overwrite = TRUE)
+}
+```
+
+```{r raw-blur-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
+op <- par(mar = rep(0, 4))
+for (g in blur_gstar[RENDERED_IDX]) {
+  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE,
+       col = COLORMAP, colNA = "black")
+}
+par(op)
+```
+
+```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
+for (i in seq_along(wsizes)) {
+  ws <- wsizes[i]
+  g <- blur_gstar[[i]]
   plot_zscore(g,
@@
               sigma_thresh = 2)
-  writeRaster(g,
-              sprintf("data/blur/gstar-%03dx%03d-z%02d-w%02d.tif",
-                      nrow(r), ncol(r), ZOOMLEVEL, ws),
-              overwrite = TRUE)
 }

### 2017-06-15 analysis.Rmd
changed code for generating Focal G* (blur)

@@
 ### Focal G* (blur)
-```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
+
+First, we pre-compute the rasters
+```{r, echo=FALSE, cache=TRUE}
+blur_focalgstar <- list()
+pb <- txtProgressBar(max = last(wsizes), style = 3)
 st <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
 for (ws in wsizes) {
+  setTxtProgressBar(pb, ws)
 
@@
 
-  g <- GetisOrd(r, w, st)
+  blur_focalgstar[[length(blur_focalgstar) + 1]] <- GetisOrd(r, w, st)
+}
+close(pb)
+```
+
+```{r, eval=FALSE, echo=FALSE}
+for (i in seq_along(wsizes)) {
+  ws <- wsizes[i]
+  g <- blur_focalgstar[[i]]
+  writeRaster(g,
+              sprintf("data/blur/focalgstar-%03dx%03d-z%02d-w%02d.tif",
+                      nrow(g), ncol(g), ZOOMLEVEL, ws),
+              overwrite = TRUE)
+}
+```
+
+```{r raw-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
+op <- par(mar = rep(0, 4))
+for (g in blur_focalgstar[RENDERED_IDX]) {
+  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE,
+       col = COLORMAP, colNA = "black")
+}
+par(op)
+```
+
+```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
+for (i in seq_along(wsizes)) {
+  ws <- wsizes[i]
+  g <- blur_focalgstar[[i]]
   plot_zscore(g,
@@
               sigma_thresh = 2)
-  writeRaster(g,
-              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
-                      nrow(r), ncol(r), ZOOMLEVEL, ws),
-              overwrite = TRUE)
 }

### 2017-06-15 paper-main.tex
updated title
smaller images
updated images

@@
   \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Multiple aggregation levels} \\
+    \multicolumn{8}{l}{
+      Aggregation levels computed from original raster (log scale)
+    }\\
     \hline
@@
   \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* Multiple aggregation levels} \\
+    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
     \hline
@@
   \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* Multiple aggregation levels} \\
+    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
     \hline
@@
 
-  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohdown-1}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+%  \hspace{1em}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
 
@@
   \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* Multiple weight matrix sizes} \\
+    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
     \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
   \end{tabular}
   \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* Multipleweight matrix sizes} \\
+    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
     \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
   \end{tabular}
 
-  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.48\linewidth]{images/gen-zoom-sohdown-1}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+%  \hspace{1em}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
 

### 2017-06-15 analysis.Rmd
update size of metric-example image

@@
 ## Example of Parent-Child Clumping Difference
-```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
+```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=5, fig.height=4.1}
 r <- rast[[ZOOMLEVEL]]

### 2017-06-15 analysis.Rmd
updated legends for confidence intervals

@@
 legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
-mtext("CI: FMsize and WMsize", line = -1, adj = .98)
 ```
@@
 legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
+mtext("CI: FMsize + Aggregation", line = -1, adj = .98)
 
@@
 legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))
-
+mtext("CI: FMsize + Aggregation", line = -1, adj = .98)
 ```
@@
 legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
+mtext("CI: ??? TODO ???", line = -1, adj = .98)
 
@@
 legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
+mtext("CI: ??? TODO ???", line = -1, adj = .98)
 ```
@@
 legend("topleft", c("Focal G*") , fill = c("red"))
+mtext("CI: ??? TODO ???", line = -1, adj = .98)
 
@@
 legend("topleft", c("Focal G*") , fill = c("red"))
-
+mtext("CI: ??? TODO ???", line = -1, adj = .98)
 ```

### 2017-06-15 analysis.Rmd
Updated images to my imagination

@@
 
+# Slice plane for aggregation dimension SOH-UP
+
 ```{r zoom-sohup, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
@@
      ylab = expression(SoH[up]),
-     xlab = "Zoom level")
+     xlab = "Aggregation level")
 
@@
 ```
+
+# Slice plane for aggregation dimension SOH-DOWN
 
@@
      ylab = expression(SoH[down]),
-     xlab = "Zoom level")
+     xlab = "Aggregation level")
 
@@
 ```
+
+# Slice plane for blur dimension SOH-UP
+
+```{r blur-sohup, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+blur_soh <- read_csv("data/blur_soh.csv")
+
+blur_soh %>% dplyr::select(Blur, "G*" = UpBlur) -> y1
+blur_soh %>% dplyr::select(Blur, "Focal G*" = UpFocalBlur) -> y2
+
+plot(y1, type = "n", ylim = c(0,1),
+     ylab = expression(SoH[up]),
+     xlab = "Weight matrix size")
+
+lines(y1, col = "blue", lw = 2)
+lines(y2, col = "red", lw = 2)
+legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
+```
+
+# Slice plane for blur dimension SOH-DOWN
+
+```{r blur-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
+blur_soh <- read_csv("data/blur_soh.csv")
+
+blur_soh %>% dplyr::select(Blur, "G*" = DownBlur) -> y1
+blur_soh %>% dplyr::select(Blur, "Focal G*" = DownFocalBlur) -> y2
+
+plot(y1, type = "n", ylim = c(0,1),
+     ylab = expression(SoH[down]),
+     xlab = "Weight matrix size")
+
+lines(y1, col = "blue", lw = 2)
+lines(y2, col = "red", lw = 2)
+legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
+```
+
+# X-Axis = Weight for whiskerplot, SOH Up and Down
 
@@
 
+# X-Axis = Aggregation for whiskerplot
+
 ```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
@@
 legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
-mtext("CI: ??? TODO ???", line = -1, adj = .98)
+mtext("CI: FMsize + WMsize", line = -1, adj = .98)
 
@@
 legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
-mtext("CI: ??? TODO ???", line = -1, adj = .98)
+mtext("CI: FMsize + WMsize", line = -1, adj = .98)
 ```
+
+# X-Axis = Focal for whiskerplot
 
@@
 legend("topleft", c("Focal G*") , fill = c("red"))
-mtext("CI: ??? TODO ???", line = -1, adj = .98)
+mtext("CI: WMsize + Aggregation", line = -1, adj = .98)
 
@@
 legend("topleft", c("Focal G*") , fill = c("red"))
-mtext("CI: ??? TODO ???", line = -1, adj = .98)
+mtext("CI: WMsize + Aggregation", line = -1, adj = .98)
 ```

### 2017-06-15 paper-main.tex
updated images
added spacing to some images
Updated images to my imagination
Updated ref to images

@@
 \subsection{Impact of Neighbourhood size}
-Next, we want to isolate the effect of the neighbourhood size by fixing the weight matrix size W and using it as x-axis.
-With the impact of the weight matrix W we gain information on how far the interconnectness is between different points as indicated in \cite{Getis.1992}.
+Next, we want to isolate the effect of the neighbourhood size by fixing the weight matrix size W 
+and using it as x-axis. With the impact of the weight matrix W we gain information on how far the 
+interconnectness is between different points as indicated in \cite{Getis.1992}. 
 The results for the weight matrix can be seen in figure ~\ref{fig:wUp} for \SOHUP and figure ~\ref{fig:wDown} for \SOHDOWN.
-Here it can be seen that in general for both evaluations metrics as well as the different hot spot methods an increase in the size of the weight matrix W leads to more stable results as well as that the Focal $G^*$ matrix is slightly more stable in most cases for the mean values.
-An interesting phenomena is the dip in stability for the standard $G^*$ for the value of 39.
-Despite our effort we could not determine the reason behind this result, as no overall trend could be extracted.
+Here it can be seen that in general for both evaluations metrics as well as the different hot spot methods 
+an increase in the size of the weight matrix W leads to more stable results as well as that the Focal $G^*$ 
+matrix is slightly more stable in most cases for the mean values. 
+An interesting phenomena is the dip in stability for the standard $G^*$ for the value of 39. Despite our 
+effort we could not determine the reason behind this result, as no overall trend could be extracted.
 The standard deviation shows similar no particular trend, but for the values above 37 is increasing. 
@@
 Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. 
-We fix the aggregation and use it as x-axis.
-This allows us to examine the impact the resolution of a data set has on the results and allow us indirectly to reduce the computational effort on future computations by using the maximal aggregation as useful.
-The results can seen in figure ~\ref{fig:SoHZoom} and ~\ref{fig:DownwardZoom}.
+We fix the aggregation and use it as x-axis. This allows us to examine the impact
+the resolution of a data set has on the results and allow us indirectly to reduce the 
+computational effort on future computations by using the maximal aggregation as useful.
+The results can seen in figure ~\ref{fig:SoHZoom}.
 First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.
@@
 
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{Upward for zoom}
-    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
-    \label{fig:UpwardZoom}
-  \end{subfigure}
+\begin{figure*}[htp]
+  \centering
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{
+      Aggregation levels computed from original raster (log scale)
+    }\\
+    \hline
+    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
+    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
+  \end{tabular}
+
+  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
   \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{Downward for zoom}
-    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
-    \label{fig:DownwardZoom}
-  \end{subfigure}
-  \caption{SoH zoom}
+  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+%  \hspace{1em}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+
+  \caption{
+    This image shows all aggregation levels for G* and Focal G* together 
+    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
   \label{fig:Zoom}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{Upward for blur}
-    \includegraphics[width=\linewidth]{images/SoHUpBlur}
-    \label{fig:UpwardBlur}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{Downward for blur}
-    \includegraphics[width=\linewidth]{images/SoHDownBlur}
-    \label{fig:DownwardBlur}
-  \end{subfigure}
-  \caption{SoH blur}
-  \label{fig:Blur}
-\end{figure}
-
-\begin{figure*}[htp]
-  \centering
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{
-      Aggregation levels computed from original raster (log scale)
-    }\\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
-  \end{tabular}
-
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-%  \hspace{1em}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-
-  \caption{
-    This image shows all aggregation levels for G* and Focal G* together 
-    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
-  }
-\end{figure*}
-
 \begin{figure*}[htp]
@@
     \hline
+    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
@@
     \hline
+    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
@@
 
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-%  \hspace{1em}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
+  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
+  \hspace{1em}
+  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
 
   \caption{
-    This image shows all aggregation levels for G* and Focal G* together 
+    This image shows different weight matrix sizes for G* and Focal G* together 
     with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
+  \label{fig:Blur}
+\end{figure*}
+
+\begin{figure*}[htp]
+  \centering
+
+  \begin{subfigure}{.35\linewidth}
+    \caption{G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
+    \label{fig:ClustDiffGstar}
+  \end{subfigure}
+  \hspace{3em}
+  \begin{subfigure}{.35\linewidth}
+    \caption{Focal G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
+    \label{fig:ClustDiffFocalGstar}
+  \end{subfigure}
+
+  \caption{
+    Example clustering for G* and Focal G* used as a input for SoH computation.
   }
@@
 \section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
+In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
+We validate the result from \ref{SoH-GI-Forum} with a real world 
 dataset an with a larger dataset. The dataset was only one month projected in one raster. 

### 2017-06-16 paper-main.tex
Rewrote conclusion

@@
 \section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
-We validate the result from \ref{SoH-GI-Forum} with a real world 
-dataset an with a larger dataset. The dataset was only one month projected in one raster. 
-We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
-is higher.
-Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
-Therefore F should be not less than 65x65. 
-If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
-has the least influence if $G^*$ or Focal $G^*$ performe better.
-We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
-it performes better, but this is beyond the scope of this work.
+In this work we examined the influence of different parameter on the stability of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord statistic.
+We validated our results with the use of the SoH metric on a well known real world data set to ensure external validity and easy replication.
+Based on the result we can show several insights, given the restrictions of this work, for future use of hot spot analysis. 
+First, the greater the area size, the more stable the results seem to be.
+The same relation seem to be given for the size of the weight matrix.
+The greater the comparable area, the more stable are the results.
+Given the study are, the focal range should be at least be a size of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN.  
+In the case of the aggregation level, the stability does not seem to be impacted in the case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase in stability for higher aggregation levels.
+We assume that the high aggregation of data and the inherent increase of examined area reduce the impact of outliers, but reduce the potential to differentiate.
+The worse results for the Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result of the increased focus on a smaller region.
+A more in depth look at the interaction between focal size and zoom level would be an interesting question for the future, but this is beyond the scope of this work.
 
@@
 Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
-stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
-It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
-for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
-$G^*$ can also be applied to spatio-temporal data.
-Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
-We now have a good indication which weight and focal size is usefull.
-We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
-One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
-All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.
+stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
+This emphasizes the importance of a metric for the stability of hotspots.
+But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work.
+Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations.
+As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research.
+We evaluated our data on the aggregate of a singular month, but one could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
+Therefore the impact of time on the results is important and could also influence the metric for stability in profound ways.
+As in the example the question is, how fine grained should the temporal clustering be and when is the result unstable for useful reasons?
+This leads to the final future work: To which hot spots should the comparison be made for the metric?
+In the current state only the next parametrization is compared for computational time reasons.
+How the comparison hot spots should be chosen and how many different comparisons have to be used is another quite interesting question for future work.
 
@@
 Research for Innovations".
-We thank the Nachbarschaftsverband Karlsruhe for the data of the thermal flight
-over Karlsruhe. %
+%
 \noindent R-packages used: \verb|raster|~\cite{cran:raster}, 

### 2017-06-16 paper-main.tex
Added Appendix

--- 2017-06-15 paper-main.tex
@@
 
+\section{Conclusions and Future Work} \label{sec:Conclusion}
+In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
+We validate the result from \ref{SoH-GI-Forum} with a real world 
+dataset an with a larger dataset. The dataset was only one month projected in one raster. 
+We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
+is higher.
+Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
+Therefore F should be not less than 65x65. 
+If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
+has the least influence if $G^*$ or Focal $G^*$ performe better.
+We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
+it performes better, but this is beyond the scope of this work.
+
+With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
+Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
+stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
+It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
+for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
+$G^*$ can also be applied to spatio-temporal data.
+Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
+We now have a good indication which weight and focal size is usefull.
+We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
+One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
+All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.
+
+\section{Acknowledgements}
+This work is part of the research project BigGIS (reference number: 01IS14012)
+funded by the Federal Ministry of Education and Research (BMBF) within the
+frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
+Research for Innovations".
+We thank the Nachbarschaftsverband Karlsruhe for the data of the thermal flight
+over Karlsruhe. %
+\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
+\verb|knitr|~\cite{cran:knitr}
+
+\section{Appendix}
+
 \subsection{Clumping}
+The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
+1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
+For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
+Neigbours are defined if they can be reached with a stepsize of 1 in x and y direction, independent of each other.
+Which can be expressed in R with clumping, TODO which package and parametrisations.
+In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
+It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
+Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
+The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.
+
+\begin{figure*}[htp]
+  \centering
+
+  \begin{subfigure}{.35\linewidth}
+    \caption{G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
+    \label{fig:ClustDiffGstar}
+  \end{subfigure}
+  \hspace{3em}
+  \begin{subfigure}{.35\linewidth}
+    \caption{Focal G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
+    \label{fig:ClustDiffFocalGstar}
+  \end{subfigure}
+
+  \caption{
+    Example clustering for G* and Focal G* used as a input for SoH computation.
+  }
+  \label{fig:Clumping}
+\end{figure*}
 
@@
 The aggregation level is a slice plane through our three dimensional space. 
+This is an example how the results can look with visualize representations of the calculated 
+rasters and the raw data.
 We evalute only the aggregation with fixed W and fixed F.
@@
 
-The results can be found in figure ~\ref{fig:Zoom}.
+The results can be found in figure ~\ref{fig:Zoom}. It can be seen that with an increase of the aggregation level the values 
+increase. TODO if clusters increase/decrease
 For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
@@
 \subsection{Blur}
-
+We also made an example for the variation of the weight size.
 Blur is a slice plane through our three dimensional space. 
@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
+\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
+\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
 \end{displaymath}
@@
 \end{definition}
-The blur results are plotted in Fig.~\ref{fig:Blur}.
+The blur results are plotted in Fig.~\ref{fig:Blur}. We show how the weight matrix is increasing
+and how $G^*$ and Focal $G^*$ changes bases on W.
 The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
@@
 
-\begin{figure*}[htp]
-  \centering
-
-  \begin{subfigure}{.35\linewidth}
-    \caption{G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
-    \label{fig:ClustDiffGstar}
-  \end{subfigure}
-  \hspace{3em}
-  \begin{subfigure}{.35\linewidth}
-    \caption{Focal G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
-    \label{fig:ClustDiffFocalGstar}
-  \end{subfigure}
-
-  \caption{
-    Example clustering for G* and Focal G* used as a input for SoH computation.
-  }
-\end{figure*}
-
-\section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
-We validate the result from \ref{SoH-GI-Forum} with a real world 
-dataset an with a larger dataset. The dataset was only one month projected in one raster. 
-We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
-is higher.
-Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
-Therefore F should be not less than 65x65. 
-If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
-has the least influence if $G^*$ or Focal $G^*$ performe better.
-We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
-it performes better, but this is beyond the scope of this work.
-
-With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
-Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
-stability of hotspots. Wrong parametrisation can lead to good results, the mean reaches for \SOHUP in the weight dimension around 0.6.
-It can also lead to bad result, \SOHUP in the zoom dimension reaches nearly zero. Therefore we shown that it is important to have a metric
-for the stability of hotspots. Also we presented indication which parametrisation should be avoided and which parametrisations are promising.
-$G^*$ can also be applied to spatio-temporal data.
-Therefore Focal $G^*$ should be also applied to the spatio-temporal data. 
-We now have a good indication which weight and focal size is usefull.
-We didn't evaluate the results on other month because we assume that they are similar But it is interesting to find clusters for different times in the day.
-One could asume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
-All our results are based on the SoH. Further work should validate or improve this metric also for the temporal dimension.
-
-\section{Acknowledgements}
-This work is part of the research project BigGIS (reference number: 01IS14012)
-funded by the Federal Ministry of Education and Research (BMBF) within the
-frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
-Research for Innovations".
-We thank the Nachbarschaftsverband Karlsruhe for the data of the thermal flight
-over Karlsruhe. %
-\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr}
-
 \bibliographystyle{plain}

### 2017-06-16 paper-main.tex

--- 2017-06-16 paper-main.tex
@@
 
+\section{Conclusions and Future Work} \label{sec:Conclusion}
+In this work we examined the influence of different parameter on the stability of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord statistic.
+We validated our results with the use of the SoH metric on a well known real world data set to ensure external validity and easy replication.
+Based on the result we can show several insights, given the restrictions of this work, for future use of hot spot analysis. 
+First, the greater the area size, the more stable the results seem to be.
+The same relation seem to be given for the size of the weight matrix.
+The greater the comparable area, the more stable are the results.
+Given the study are, the focal range should be at least be a size of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN.  
+In the case of the aggregation level, the stability does not seem to be impacted in the case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase in stability for higher aggregation levels.
+We assume that the high aggregation of data and the inherent increase of examined area reduce the impact of outliers, but reduce the potential to differentiate.
+The worse results for the Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result of the increased focus on a smaller region.
+A more in depth look at the interaction between focal size and zoom level would be an interesting question for the future, but this is beyond the scope of this work.
+
+With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
+Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
+stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
+This emphasizes the importance of a metric for the stability of hotspots.
+But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work.
+Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations.
+As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research.
+We evaluated our data on the aggregate of a singular month, but one could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
+Therefore the impact of time on the results is important and could also influence the metric for stability in profound ways.
+As in the example the question is, how fine grained should the temporal clustering be and when is the result unstable for useful reasons?
+This leads to the final future work: To which hot spots should the comparison be made for the metric?
+In the current state only the next parametrization is compared for computational time reasons.
+How the comparison hot spots should be chosen and how many different comparisons have to be used is another quite interesting question for future work.
+
+\section{Acknowledgements}
+This work is part of the research project BigGIS (reference number: 01IS14012)
+funded by the Federal Ministry of Education and Research (BMBF) within the
+frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
+Research for Innovations".
+%
+\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
+\verb|knitr|~\cite{cran:knitr}
+
+\section{Appendix}
+
 \subsection{Clumping}
+The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
+1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
+For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
+Neigbours are defined if they can be reached with a stepsize of 1 in x and y direction, independent of each other.
+Which can be expressed in R with clumping, TODO which package and parametrisations.
+In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
+It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
+Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
+The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.
+
+\begin{figure*}[htp]
+  \centering
+
+  \begin{subfigure}{.35\linewidth}
+    \caption{G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
+    \label{fig:ClustDiffGstar}
+  \end{subfigure}
+  \hspace{3em}
+  \begin{subfigure}{.35\linewidth}
+    \caption{Focal G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
+    \label{fig:ClustDiffFocalGstar}
+  \end{subfigure}
+
+  \caption{
+    Example clustering for G* and Focal G* used as a input for SoH computation.
+  }
+  \label{fig:Clumping}
+\end{figure*}
 
@@
 
-\section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work we examined the influence of different parameter on the stability of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord statistic.
-We validated our results with the use of the SoH metric on a well known real world data set to ensure external validity and easy replication.
-Based on the result we can show several insights, given the restrictions of this work, for future use of hot spot analysis. 
-First, the greater the area size, the more stable the results seem to be.
-The same relation seem to be given for the size of the weight matrix.
-The greater the comparable area, the more stable are the results.
-Given the study are, the focal range should be at least be a size of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN.  
-In the case of the aggregation level, the stability does not seem to be impacted in the case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase in stability for higher aggregation levels.
-We assume that the high aggregation of data and the inherent increase of examined area reduce the impact of outliers, but reduce the potential to differentiate.
-The worse results for the Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result of the increased focus on a smaller region.
-A more in depth look at the interaction between focal size and zoom level would be an interesting question for the future, but this is beyond the scope of this work.
-
-With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
-Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
-stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
-This emphasizes the importance of a metric for the stability of hotspots.
-But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work.
-Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations.
-As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research.
-We evaluated our data on the aggregate of a singular month, but one could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
-Therefore the impact of time on the results is important and could also influence the metric for stability in profound ways.
-As in the example the question is, how fine grained should the temporal clustering be and when is the result unstable for useful reasons?
-This leads to the final future work: To which hot spots should the comparison be made for the metric?
-In the current state only the next parametrization is compared for computational time reasons.
-How the comparison hot spots should be chosen and how many different comparisons have to be used is another quite interesting question for future work.
-
-\section{Acknowledgements}
-This work is part of the research project BigGIS (reference number: 01IS14012)
-funded by the Federal Ministry of Education and Research (BMBF) within the
-frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
-Research for Innovations".
-%
-\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr}
-
 \bibliographystyle{plain}

### 2017-06-16 paper-main.tex
Updated Appendix

@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
@@
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
+\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
 \end{displaymath}
 \begin{displaymath}
-z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
+z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
 \end{displaymath}
-
 \end{definition}
@@
 For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
-Neigbours are defined if they can be reached with a stepsize of 1 in x and y direction, independent of each other.
-Which can be expressed in R with clumping, TODO which package and parametrisations.
+Neigbours are are pixels with touching edges which leads for every pixel to 8 neigbours.
+The clustering can be expressed in R with clumping, TODO which package and parametrisations.
 In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
@@
 rasters and the raw data.
-We evalute only the aggregation with fixed W and fixed F.
+We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
+the water had to much influence.
 \begin{definition} Aggregation run:
@@
 \subsection{Blur}
-We also made an example for the variation of the weight size.
+We also made an example for the variation of the weight size W.
 Blur is a slice plane through our three dimensional space. 
 W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
+For blur we also included the negative clusters which resulted in a surprising result.
 \begin{definition} Blur run:
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
+\SOHUP( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
 \end{displaymath}
 \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
+\SOHDOWN( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
 \end{displaymath}
@@
 \end{definition}
-The blur results are plotted in Fig.~\ref{fig:Blur}. We show how the weight matrix is increasing
-and how $G^*$ and Focal $G^*$ changes bases on W.
-The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
-Higher weight leads in general to better results for Focal $G^*$. 
-$G^*$ doesn't fit to the mean of our whiskerplot.
+The blur results are plotted in Fig.~\ref{fig:Blur}. The weight matrix is shown in the first row, with increasing size.
+The scond and thrid row sho how $G^*$ and Focal $G^*$ changes based on W.
+This example is a slice plane of the weight dimension ploted in figure ~\ref{fig:SoHWeight}.
+It can be seen that increase of the weight size leads in general to better results for Focal $G^*$. 
+$G^*$ compared to the mean of our whiskerplot does not fit in the picture because it leads to better results than $G^*$.
 
@@
 
-\begin{figure*}[htp]
-  \centering
-
-  \begin{subfigure}{.35\linewidth}
-    \caption{G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
-    \label{fig:ClustDiffGstar}
-  \end{subfigure}
-  \hspace{3em}
-  \begin{subfigure}{.35\linewidth}
-    \caption{Focal G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
-    \label{fig:ClustDiffFocalGstar}
-  \end{subfigure}
-
-  \caption{
-    Example clustering for G* and Focal G* used as a input for SoH computation.
-  }
-\end{figure*}
-
 \bibliographystyle{plain}

### 2017-06-16 analysis.Rmd
Updated Blur SoH
updated images and analysis code

@@
 RENDERED_IDX <- floor(seq(1, length(wsizes), length.out = 8))
+#RENDERED_IDX <- 1:8
 ```
@@
 
-blur_soh %>% dplyr::select(Blur, "G*" = UpBlur) -> y1
-blur_soh %>% dplyr::select(Blur, "Focal G*" = UpFocalBlur) -> y2
+blur_soh %>% dplyr::select(Weight, "G*" = UpBlur) -> y1
+blur_soh %>% dplyr::select(Weight, "Focal G*" = UpFocalBlur) -> y2
 
@@
 lines(y2, col = "red", lw = 2)
-legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
+legend(7,1, c("G*", "Focal G*"), fill = c("blue", "red"))
 ```
@@
 
-blur_soh %>% dplyr::select(Blur, "G*" = DownBlur) -> y1
-blur_soh %>% dplyr::select(Blur, "Focal G*" = DownFocalBlur) -> y2
+blur_soh %>% dplyr::select(Weight, "G*" = DownBlur) -> y1
+blur_soh %>% dplyr::select(Weight, "Focal G*" = DownFocalBlur) -> y2
 
@@
 plot(NA,
-     ylab = expression(SoH^Up),
+     ylab = expression(SoH[Up]),
      xlab = sprintf("Weight matrix size"),
@@
 plot(NA,
-     ylab = expression(SoH^Down),
+     ylab = expression(SoH[Down]),
      xlab = sprintf("Weight matrix size"),
@@
 plot(NA,
-     ylab = expression(SoH^Up),
+     ylab = expression(SoH[Up]),
      xlab = sprintf("Aggregation levels"),
@@
 plot(NA, 
-     ylab = expression(SoH^Down),
+     ylab = expression(SoH[Down]),
      xlab = sprintf("Aggregation levels"),
@@
 plot(NA,
-     ylab = expression(SoH^Up),
+     ylab = expression(SoH[Up]),
      xlab = "Focal matrix size",
@@
 plot(NA,
-     ylab = expression(SoH^Down),
+     ylab = expression(SoH[Down]),
      xlab = "Focal matrix size",

### 2017-06-16 analysis.Rmd
all legends moved to topleft

@@
 lines(y2, col = "red", lw = 2)
-legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
+legend("topleft", c("G*", "Focal G*"), fill = c("blue", "red"))
 ```
@@
 lines(y2, col = "red", lw = 2)
-legend(7,1, c("G*", "Focal G*"), fill = c("blue", "red"))
+legend("topleft", c("G*", "Focal G*"), fill = c("blue", "red"))
 ```

### 2017-06-16 paper-main.tex
minor latex fix
zoom -> aggregation in the text

@@
 In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .
-Here, we build upon that work and examine in more detail the impact of the different instantiations of the most typical parameter.
-We use the well known Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of this statistic, the focal $G^*$~\cite{SoH-GI-Forum}.
-Those parameter are the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix).
-By varying over these parameter, we can compare the stability for all possible combinations and isolate the effect of single parameter by aggregation over the other parameter.
+Here, we build upon that work and examine in more detail the impact of the 
+different instantiations of the most typical parameter. We use the well known 
+Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
+this statistic, the focal $G^*$~\cite{SoH-GI-Forum}. Those parameter are the 
+size of the study area (focal matrix), the detail of the resolution 
+(aggregation level) and the size of the neighbourhood (weight matrix). By 
+varying over these parameter, we can compare the stability for all possible 
+combinations and isolate the effect of single parameter by aggregation over the 
+other parameter. 
 We evaluate on the well-known taxi data set to show the applicability on real world use cases as well as to enable a simple replication.
@@
 \begin{definition}
-The SoH for a singled evalution run in the weight dimension is defined as:
+
   \begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
+    \SOHUP(child, parent)
   \end{displaymath}
   \begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
+    \SOHDOWN(child, parent)
   \end{displaymath}
+
+  The SoH for a singled evalution run in the weight dimension is defined as:
+  \begin{eqnarray*}
+    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
+    parent & = & G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
+  \end{eqnarray*}
   \begin{displaymath}
@@
   The SoH for a singled evalution run in the focal dimension is defined as:
-\begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
-\end{displaymath}
+  \begin{eqnarray*}
+    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
+    parent & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
+  \end{eqnarray*}
   \begin{displaymath}
@@
   \end{displaymath}
-The SoH for a singled evalution run in the aggregation dimension is defined as:
-\begin{displaymath}
-\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
-\end{displaymath}
+
+  The SoH for a singled evalution run in the aggregation dimension is defined 
+  as:
+  \begin{eqnarray*}
+    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
+    parent & = & G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
+  \end{eqnarray*}
   \begin{displaymath}
@@
 The results can seen in figure ~\ref{fig:SoHZoom}.
-First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.
+First, we can see that for the aggregation level, in contrast to previous 
+results, the standard $G^*$ seems to be more stable.
 
@@
 \section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work we examined the influence of different parameter on the stability of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord statistic.
-We validated our results with the use of the SoH metric on a well known real world data set to ensure external validity and easy replication.
-Based on the result we can show several insights, given the restrictions of this work, for future use of hot spot analysis. 
-First, the greater the area size, the more stable the results seem to be.
-The same relation seem to be given for the size of the weight matrix.
-The greater the comparable area, the more stable are the results.
-Given the study are, the focal range should be at least be a size of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN.  
-In the case of the aggregation level, the stability does not seem to be impacted in the case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase in stability for higher aggregation levels.
-We assume that the high aggregation of data and the inherent increase of examined area reduce the impact of outliers, but reduce the potential to differentiate.
-The worse results for the Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result of the increased focus on a smaller region.
-A more in depth look at the interaction between focal size and zoom level would be an interesting question for the future, but this is beyond the scope of this work.
+In this work we examined the influence of different parameter on the stability
+of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord
+statistic. We validated our results with the use of the SoH metric on a well
+known real world data set to ensure external validity and easy replication.
+Based on the result we can show several insights, given the restrictions of this
+work, for future use of hot spot analysis. First, the greater the area size, the
+more stable the results seem to be. The same relation seem to be given for the
+size of the weight matrix. The greater the comparable area, the more stable are
+the results. Given the study are, the focal range should be at least be a size
+of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN. In the
+case of the aggregation level, the stability does not seem to be impacted in the
+case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase
+in stability for higher aggregation levels. We assume that the high aggregation
+of data and the inherent increase of examined area reduce the impact of
+outliers, but reduce the potential to differentiate. The worse results for the
+Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result
+of the increased focus on a smaller region. A more in depth look at the
+interaction between focal size and aggregation level would be an interesting
+question for the future, but this is beyond the scope of this work.
 
@@
 
-The results can be found in figure ~\ref{fig:Zoom}. It can be seen that with an increase of the aggregation level the values 
-increase. TODO if clusters increase/decrease
-For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
-\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
-For the downward property, Focal $G^*$ leads to better results at zoom level 5.
+The results can be found in figure ~\ref{fig:Zoom}. It can be seen that with an
+increase of the aggregation level the values increase. TODO if clusters
+increase/decrease For the upward property, $G^*$ is always better than Focal
+$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
+reaches the same result as $G^*$ at aggregation level~5 . For the downward
+property, Focal $G^*$ leads to better results at aggregation level~5.
 
@@
 
+  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
+  \hspace{1em}
   \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
-  \hspace{1em}
-  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
 

### 2017-06-16 paper-main.tex
text fixes

@@
 Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
-this statistic, the focal $G^*$~\cite{SoH-GI-Forum}. Those parameter are the 
+this statistic, the Focal $G^*$~\cite{SoH-GI-Forum}. Those parameter are the 
 size of the study area (focal matrix), the detail of the resolution 
@@
 increasing the size of a weight matrix has a "blurring" effect on the raster
-(Fig.~\ref{def:TODO}a) whereas decreasing the size can be seen as a form of
-"sharpening" (Fig.~\ref{def:TODO}b).
+(Figure~\ref{fig:BlurExample:a}) whereas decreasing the size can be 
+seen as a form of "sharpening" (Figure~\ref{fig:BlurExample:b}).
 
@@
 %
-%Consider the real-world example depicted in Fig.~\ref{fig:TempMaps}.
+%Consider the real-world example depicted in Figure~\ref{fig:TempMaps}.
 %%TODO: thermal flight -> NY taxi
 %The temperature map of a morning thermal flight dataset 
-%(Fig.~\ref{fig:TempMaps:a}) has been processed using $G^*$.
+%(Figure~\ref{fig:TempMaps:a}) has been processed using $G^*$.
 %
@@
 %%TODO: need two images - G* and FocalG*
-%\begin{figure}[htp]
-%  \begin{subfigure}{1\linewidth}
-%    \caption{Morning temperatures}
-%    \includegraphics[width=\linewidth]{images/hotspot-rawtemp-1}
-%    \label{fig:TempMaps:a}
-%  \end{subfigure}
-%  
-%  \caption{
-%    Karlsruhe city center.
-%    Selected area of $2.4{\times}1.4\,km$.
-%    Pixel size $5{\times}5\,m$.
-%  }
-%  \label{fig:TempMaps}
-%\end{figure}
+\begin{figure}[htp]
+  \centering
+  \begin{subfigure}{.3\linewidth}
+    \caption{Small matrix}
+    \includegraphics[width=\linewidth]{images/gen-raw-blur-gstar-2}
+    \label{fig:BlurExample:a}
+  \end{subfigure}
+  \begin{subfigure}{.3\linewidth}
+    \caption{Large matrix}
+    \includegraphics[width=\linewidth]{images/gen-raw-blur-gstar-8}
+    \label{fig:BlurExample:b}
+  \end{subfigure}
+  \caption{
+    Example of G* statictics computed for the same raster with different weight 
+    matrix sizes.
+  }
+\end{figure}
 
@@
 
-That is
-
-To be stable, one assumes that every parent has at
-least one child and that each child has one parent. For a perfectly stable
-interaction, it can be easily seen that the connection between parent and child
-is a injective function and between child and parent a surjective function. To
-measure the closeness of connection, we propose a metric called the
-\emph{Stability of Hot spot} (SoH). It measures the deviation from a perfectly
-stable transformation of resolutions.
+Stability assumes that every parent has at least one child and that each child
+has one parent. For a perfectly stable interaction, it can be easily seen that
+the connection between parent and child is a injective function and between
+child and parent a surjective function. To measure the stability,
+we propose a metric called the \emph{Stability of Hot spot} (SoH). It measures
+the deviation from a perfectly stable transformation between the parent and 
+chaild rasters (like frames of an animation).
 
@@
 
-\section{Focal Getis-Ord} \label{sec:FocalGetisOrd}
+%\section{Focal Getis-Ord}
+%\label{sec:FocalGetisOrd}
+%
+%In paper~\cite{SoH-GI-Forum}, we have defined the measure Focal G*.
+%We use the notation \FOCAL{R}{M}{op} to denote a focal
+%operation $op$ applied on a raster $R$ with a focal window determined by a
+%matrix $M$. This is rougly eqivalent to a command \verb|focal(x=R, w=M, 
+%fun=op)|
+%from package \emph{raster} in the R programming language \cite{cran:raster}.
 
-Section is analog to \cite{SoH-GI-Forum} and incorporates the most important definitions for the computation.
-We use the notation \FOCAL{R}{M}{op} to denote a focal
-operation $op$ applied on a raster $R$ with a focal window determined by a
-matrix $M$. This is rougly eqivalent to a command \verb|focal(x=R, w=M, fun=op)|
-from package \emph{raster} in the R programming language \cite{cran:raster}.
-
-\begin{definition}[$G^*$ function on rasters]
-  \label{def:GenericGetisOrdFunc}
-
-  The function $G^*$ can be expressed as a raster operation:
-
-  \begin{displaymath}
-    G^*(R, W, st) =
-    \frac{
-      \FOCAL{R}{W}{sum} - M*\sum_{w \in W}{w}
-    }{
-      S \sqrt{
-        \frac{
-          N*\sum_{w \in W}{w^2} - (\sum_{w \in W}{w})^2
-        }{
-          N - 1
-        }
-      }
-    }
-  \end{displaymath}
-  \noindent where:
-  \begin{itemize}
-
-    \item $R$ is the input raster.
-
-    \item $W$ is a weight matrix of values between 0 and 1.
-
-    \item $st = (N, M, S)$ is a parametrization specific to a particular version
-    of the $G^*$ function. (Def.\vref{def:StdGetisOrdVersion} and
-    \vref{def:FocalGetisOrdVersion}).
-
-  \end{itemize}
-\end{definition}
-
-\begin{definition}[Standard $G^*$ parametrization]
-  \label{def:StdGetisOrdVersion}
-
-  Computes the parametrization $st$ as global statistics for all pixels in the
-  raster $R$:
-
-  \begin{itemize}
-    \item $N$ represents the number of all pixels in $R$.
-    \item $M$ represents the global mean of $R$.
-    \item $S$ represents the global standard deviation of all pixels in $R$.
-  \end{itemize}
-\end{definition}
-
-\begin{definition}[Focal $G^*$ parametrization]
-  \label{def:FocalGetisOrdVersion}
-
-  Let $F$ be a boolean matrix such that: $all(dim(F) \geq dim(W))$.
-  This version uses focal operations to compute per-pixel statistics given by 
-  the focal neighbourhood $F$ as follows:
-
-  \begin{itemize}
-
-    \item $N$ is a raster computed as a focal operation \FOCAL{R}{F}{sum}. Each
-    pixel represents the number of pixels from $R$ convoluted with the matrix
-    $F$.
-
-    \item $M$ is a raster computed as a focal mean \FOCAL{R}{F}{mean}, thus each
-    pixel represents a mean value of its $F$-neighbourhood.
-
-    \item $S$ is a raster computed as a focal standard deviation
-    \FOCAL{R}{F}{sd}, thus each pixel represents a standard deviation of its
-    $F$-neighbourhood.
-
-  \end{itemize}
-
-\end{definition}
+%\begin{definition}[$G^*$ function on rasters]
+%  \label{def:GenericGetisOrdFunc}
+%  
+%  The function $G^*$ can be expressed as a raster operation:
+%  
+%  \begin{displaymath}
+%    G^*(R, W, st) =
+%    \frac{
+%      \FOCAL{R}{W}{sum} - M*\sum_{w \in W}{w}
+%    }{
+%      S \sqrt{
+%        \frac{
+%          N*\sum_{w \in W}{w^2} - (\sum_{w \in W}{w})^2
+%        }{
+%          N - 1
+%        }
+%      }
+%    }
+%  \end{displaymath}
+%  \noindent where:
+%  \begin{itemize}
+%    
+%    \item $R$ is the input raster.
+%    
+%    \item $W$ is a weight matrix of values between 0 and 1.
+%    
+%    \item $st = (N, M, S)$ is a parametrization specific to a particular 
+%version
+%    of the $G^*$ function. (Def.\vref{def:StdGetisOrdVersion} and
+%    \vref{def:FocalGetisOrdVersion}).
+%    
+%  \end{itemize}
+%\end{definition}
+%
+%\begin{definition}[Standard $G^*$ parametrization]
+%  \label{def:StdGetisOrdVersion}
+%  
+%  Computes the parametrization $st$ as global statistics for all pixels in the
+%  raster $R$:
+%  
+%  \begin{itemize}
+%    \item $N$ represents the number of all pixels in $R$.
+%    \item $M$ represents the global mean of $R$.
+%    \item $S$ represents the global standard deviation of all pixels in $R$.
+%  \end{itemize}
+%\end{definition}
+%
+%\begin{definition}[Focal $G^*$ parametrization]
+%  \label{def:FocalGetisOrdVersion}
+%  
+%  Let $F$ be a boolean matrix such that: $all(dim(F) \geq dim(W))$.
+%  This version uses focal operations to compute per-pixel statistics given by 
+%  the focal neighbourhood $F$ as follows:
+%  
+%  \begin{itemize}
+%    
+%    \item $N$ is a raster computed as a focal operation \FOCAL{R}{F}{sum}. Each
+%    pixel represents the number of pixels from $R$ convoluted with the matrix
+%    $F$. 
+%    
+%    \item $M$ is a raster computed as a focal mean \FOCAL{R}{F}{mean}, thus 
+%each
+%    pixel represents a mean value of its $F$-neighbourhood.
+%    
+%    \item $S$ is a raster computed as a focal standard deviation
+%    \FOCAL{R}{F}{sd}, thus each pixel represents a standard deviation of its
+%    $F$-neighbourhood.
+%    
+%  \end{itemize}
+%  
+%\end{definition}
 
@@
 
-\begin{definition}[Evaluation Run]
-  \label{def:EvalRun}
-  We define a single evaluation run as a tuple:
-  \begin{displaymath}
-    E = (V, m, p, w)
-  \end{displaymath}
-  \noindent where:
-  \begin{itemize}
+%\begin{definition}[Evaluation Run]
+%  \label{def:EvalRun}
+%  We define a single evaluation run as a tuple:
+%  \begin{displaymath}
+%    E = (V, m, p, w)
+%  \end{displaymath}
+%  \noindent where:
+%  \begin{itemize}
+%  
+%    \item $V$ is the input dataset of points, representing the taxi dropoffs 
+%in 
+%    our case.
+%    
+%    \item $m$ is the metric used, in our case either \SOHUP or \SOHDOWN.
+%    
+%    \item $p$ represents the pixel size for aggregating points from $V$, 
+%    e.g. $100 \times 100$ meters.
+%    
+%    \item $w$ represents the size of a weight matrix.
+%    In our case, we chose a weight matrix depicted in 
+%    Figure~\ref{fig:ExampleMatrices}(a) for both the G* and FocalG* cases.
+%  \end{itemize}
+%\end{definition}
 
-    \item $V$ is the input dataset of points, representing the taxi dropoffs in 
-    our case.
-
-    \item $m$ is the metric used, in our case either \SOHUP or \SOHDOWN.
-
-    \item $p$ represents the pixel size for aggregating points from $V$, 
-    e.g. $100 \times 100$ meters.
-
-    \item $w$ represents the size of a weight matrix.
-    In our case, we chose a weight matrix depicted in 
-    Figure~\ref{fig:ExampleMatrices}(a) for both the G* and FocalG* cases.
-  \end{itemize}
-\end{definition}
-
-%Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} show
+%Figure~\ref{fig:ComparisonMorning} and Figure~\ref{fig:ComparisonEvening} show
 %Standard and Focal $G^*$ computations for both morning and eventing datasets
@@
 %Example weight matrix $W$ and focal matrix $F$ are depicted in 
-%Fig.~\ref{fig:ExampleMatrices}.
+%Figure~\ref{fig:ExampleMatrices}.
 
@@
 Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
-The following conditions must hold dim(F)>dim(W) and dim(F)<dim(R) which leads e.g. to 460 results in the z dimension.
+The following conditions must hold $dim(F) > dim(W)$ and $dim(F) < dim(R)$ 
+which leads e.g. to 460 results in the z-dimension.
 We vary over the weight matrix W, the focal matrix F and the aggregation level, as motivated in the introduction.
-To compare the impact each of these parameters has we compute all variations over two parameter and holding one parameter fix.
-We then calculate the mean as well as the standard deviation for the SoH for the fixed value based on the two other parameters.
-This allows us to isolate the impact of the variation in the single parameter.
-The results are then plotted in Fig.
-1-6, one graphic for each fixed parameter and the direction of the SoH.
+To compare the impact each of these parameters has we compute all variations 
+over two parameter and holding one parameter fix. We then calculate the mean as 
+well as the standard deviation for the SoH for the fixed value based on the two 
+other parameters. This allows us to isolate the impact of the variation in the 
+single parameter. The results are then plotted in 
+Figures~\ref{fig:SoHFocal}--\ref{fig:SoHZoom}, one image for each fixed 
+parameter and the direction of the SoH.
 The hotspots to use the SoH on are computed by the focal $G^*$ and standard $G^*$ method.
@@
 \subsection{Clumping}
-The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
-1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
-For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
-Neigbours are are pixels with touching edges which leads for every pixel to 8 neigbours.
-The clustering can be expressed in R with clumping, TODO which package and parametrisations.
-In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
-It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
-Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
-The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.
 
-\begin{figure*}[htp]
+The SoH needs a parent and a child. Clusters can be calculated different. For
+$G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less
+then 1\% of the cases you are wrong. The values of Focal $G^*$ depend on the
+focal size F. Therefore, we decide all values in the top quantile belong to a
+clusters. For clustering we grouped the neighbourhood with values in the top
+quantile to one cluster. Neigbours are are pixels with touching edges which
+leads for every pixel to 8 neigbours. Fig.~\ref{fig:Clumping} depicts the 
+clusters using different colours. In this figure, Focal~$G^*$ has smaller 
+clusters which are distributed over the complete raster.
+
+\begin{figure}[htp]
   \centering
 
-  \begin{subfigure}{.35\linewidth}
+  \begin{subfigure}{.7\linewidth}
     \caption{G* clustering difference}
@@
   \hspace{3em}
-  \begin{subfigure}{.35\linewidth}
+  \begin{subfigure}{.7\linewidth}
     \caption{Focal G* clustering difference}
@@
   \label{fig:Clumping}
-\end{figure*}
+\end{figure}
 
@@
 
-The results can be found in figure ~\ref{fig:Zoom}. It can be seen that with an
+The results can be found in Fig.~\ref{fig:Zoom}. It can be seen that with an
 increase of the aggregation level the values increase. TODO if clusters
@@
 \end{definition}
-The blur results are plotted in Fig.~\ref{fig:Blur}. The weight matrix is shown in the first row, with increasing size.
-The scond and thrid row sho how $G^*$ and Focal $G^*$ changes based on W.
-This example is a slice plane of the weight dimension ploted in figure ~\ref{fig:SoHWeight}.
-It can be seen that increase of the weight size leads in general to better results for Focal $G^*$. 
-$G^*$ compared to the mean of our whiskerplot does not fit in the picture because it leads to better results than $G^*$.
+The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
+shown in the first row, with increasing size. The scond and thrid row sho how
+$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
+weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that
+increase of the weight size leads in general to better results for Focal $G^*$.
+$G^*$ compared to the mean of our whiskerplot does not fit in the picture
+because it leads to better results than $G^*$.
 

### 2017-06-16 paper-main.tex
Added degress in WGS84 after: https://www.deine-berge.de/Rechner/Koordinaten/Dezimal/40.769239,-73.948286

@@
 
-We evaluate our data on the New York city yellow cab data set \footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}.
-This data set includes all taxi drives from the yellow cabs in New York City, from location, to passengers and many more informations.
-In this study, we compare the total pickups over January from 2016 in the Manhattan area.
-The borders of the rasters are (40.699607, -74.020265) and (40.769239, -73.948286).
-By using this data set, we reduce the computational effort while still being able to show the applicability on real world data and problems.
+We evaluate our data on the New York city yellow cab data set 
+\footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}. 
+This data set includes all taxi drives from the yellow cabs in New York City, 
+from location, to passengers and many more informations. In this study, we compare the 
+total pickups over January from 2016 in the Manhattan area. 
+The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) and (40.769239, -73.948286).
+By using this data set, we reduce the computational effort while still 
+being able to show the applicability on real world data and problems.
 \subsection{Treatments}

### 2017-06-16 paper-main.tex
Minor fixes

@@
 total pickups over January from 2016 in the Manhattan area. 
-The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) and (40.769239, -73.948286).
+The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) 
+and (40.769239 \textdegree  (N), -73.948286 \textdegree  (E)) after WGS84.
 By using this data set, we reduce the computational effort while still 
@@
   \end{eqnarray*}
-  \begin{displaymath}
-    z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-  \end{displaymath}
   The SoH for a singled evalution run in the focal dimension is defined as:
@@
   \end{eqnarray*}
-  \begin{displaymath}
-    z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-  \end{displaymath}
-
   The SoH for a singled evalution run in the aggregation dimension is defined 
@@
   \end{eqnarray*}
+
   \begin{displaymath}
@@
 \begin{definition} Aggregation run:
+\begin{eqnarray*}
+    child & = & G^*(R_z, W_11, st, F_41) \\
+    parent & = & G^*(R_{z+1}, W_11, st, F_41)
+  \end{eqnarray*}
 \begin{displaymath}
-\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
-\end{displaymath}
-\begin{displaymath}
-z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
+z \in [1,6], G^* \in [Standard, Focal]
 \end{displaymath}
@@
 \begin{definition} Blur run:
+\begin{eqnarray*}
+    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_41) \\
+    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_41)
+  \end{eqnarray*}
 \begin{displaymath}
-\SOHUP( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
-\end{displaymath}
-\begin{displaymath}
-\SOHDOWN( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
-\end{displaymath}
-\begin{displaymath}
-z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
+i \in [0,11], G^* \in [Standard, Focal]
 \end{displaymath}

### 2017-06-16 paper-main.tex
minor fix
Removed appendix

@@
 The focal $G^*$ allows us, to isolate the impact that the size of the study area has on the stability of the results without recomputing the total dataset.
+\subsection{Clumping}
+
+The SoH needs a parent and a child. Clusters can be calculated different. For
+$G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less
+then 1\% of the cases you are wrong. The values of Focal $G^*$ depend on the
+focal size F. Therefore, we decide all values in the top quantile belong to a
+clusters. For clustering we grouped the neighbourhood with values in the top
+quantile to one cluster. Neigbours are are pixels with touching edges which
+leads for every pixel to 8 neigbours. Fig.~\ref{fig:Clumping} depicts the 
+clusters using different colours. In this figure, Focal~$G^*$ has smaller 
+clusters which are distributed over the complete raster.
+
+\begin{figure}[htp]
+  \centering
+
+  \begin{subfigure}{.7\linewidth}
+    \caption{G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
+    \label{fig:ClustDiffGstar}
+  \end{subfigure}
+  \hspace{3em}
+  \begin{subfigure}{.7\linewidth}
+    \caption{Focal G* clustering difference}
+    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
+    \label{fig:ClustDiffFocalGstar}
+  \end{subfigure}
+
+  \caption{
+    Example clustering for G* and Focal G* used as a input for SoH computation.
+  }
+  \label{fig:Clumping}
+\end{figure}
+
+\subsection{Aggregate}
+
+The aggregation level is a slice plane through our three dimensional space. 
+This is an example how the results can look with visualize representations of the calculated 
+rasters and the raw data.
+\begin{definition} Aggregation run:
+\begin{eqnarray*}
+    child & = & G^*(R_z, W_{11}, st, F_{41}) \\
+    parent & = & G^*(R_{z+1}, W_{11}, st, F_{41})
+  \end{eqnarray*}
+\begin{displaymath}
+z \in [1,6], G^* \in [Standard, Focal]
+\end{displaymath}
+\end{definition}
+
+The results can be found in Fig.~\ref{fig:Zoom}. It can be seen that with an
+increase of the aggregation level the values increase. TODO if clusters
+increase/decrease For the upward property, $G^*$ is always better than Focal
+$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
+reaches the same result as $G^*$ at aggregation level~5 . For the downward
+property, Focal $G^*$ leads to better results at aggregation level~5.
+
+\begin{figure*}[htp]
+  \centering
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{
+      Aggregation levels computed from original raster (log scale)
+    }\\
+    \hline
+    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
+    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
+    \includegraphics[width=4.6em]{images/gen-rawdata-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
+  \end{tabular}
+
+  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
+  \hspace{1em}
+  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+%  \hspace{1em}
+%  \includegraphics[width=.45\linewidth]{images/gen-???}
+
+  \caption{
+    This image shows all aggregation levels for G* and Focal G* together 
+    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
+  \label{fig:Zoom}
+\end{figure*}
+
+\subsection{Blur}
+We also made an example for the variation of the weight size W.
+Blur is a slice plane through our three dimensional space. 
+W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
+\begin{definition} Blur run:
+\begin{eqnarray*}
+    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_{41}) \\
+    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_{41})
+  \end{eqnarray*}
+\begin{displaymath}
+i \in [0,11], G^* \in [Standard, Focal]
+\end{displaymath}
+\end{definition}
+The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
+shown in the first row, with increasing size. The 2nd and 3th row show how
+$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
+weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
+increase of the weight size leads in general to better results for Focal $G^*$.
+
+\begin{figure*}[htp]
+  \centering
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
+    \hline
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
+    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
+  \end{tabular}
+  \begin{tabular}{cccccccc}
+    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
+    \hline
+    \vspace*{2mm}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
+  \end{tabular}
+
+  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
+  \hspace{1em}
+  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
+
+  \caption{
+    This image shows different weight matrix sizes for G* and Focal G* together 
+    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
+  }
+  \label{fig:Blur}
+\end{figure*}
 
@@
 
-\section{Appendix}
-
-\subsection{Clumping}
-
-The SoH needs a parent and a child. Clusters can be calculated different. For
-$G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less
-then 1\% of the cases you are wrong. The values of Focal $G^*$ depend on the
-focal size F. Therefore, we decide all values in the top quantile belong to a
-clusters. For clustering we grouped the neighbourhood with values in the top
-quantile to one cluster. Neigbours are are pixels with touching edges which
-leads for every pixel to 8 neigbours. Fig.~\ref{fig:Clumping} depicts the 
-clusters using different colours. In this figure, Focal~$G^*$ has smaller 
-clusters which are distributed over the complete raster.
-
-\begin{figure}[htp]
-  \centering
-
-  \begin{subfigure}{.7\linewidth}
-    \caption{G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
-    \label{fig:ClustDiffGstar}
-  \end{subfigure}
-  \hspace{3em}
-  \begin{subfigure}{.7\linewidth}
-    \caption{Focal G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
-    \label{fig:ClustDiffFocalGstar}
-  \end{subfigure}
-
-  \caption{
-    Example clustering for G* and Focal G* used as a input for SoH computation.
-  }
-  \label{fig:Clumping}
-\end{figure}
-
-\subsection{Aggregate}
-
-The aggregation level is a slice plane through our three dimensional space. 
-This is an example how the results can look with visualize representations of the calculated 
-rasters and the raw data.
-We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
-the water had to much influence.
-\begin{definition} Aggregation run:
-\begin{eqnarray*}
-    child & = & G^*(R_z, W_11, st, F_41) \\
-    parent & = & G^*(R_{z+1}, W_11, st, F_41)
-  \end{eqnarray*}
-\begin{displaymath}
-z \in [1,6], G^* \in [Standard, Focal]
-\end{displaymath}
-\end{definition}
-
-The results can be found in Fig.~\ref{fig:Zoom}. It can be seen that with an
-increase of the aggregation level the values increase. TODO if clusters
-increase/decrease For the upward property, $G^*$ is always better than Focal
-$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
-reaches the same result as $G^*$ at aggregation level~5 . For the downward
-property, Focal $G^*$ leads to better results at aggregation level~5.
-
-\begin{figure*}[htp]
-  \centering
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{
-      Aggregation levels computed from original raster (log scale)
-    }\\
-    \hline
-    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
-    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
-    \hline
-    \vspace*{2mm}
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
-    \hline
-    \vspace*{2mm}
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
-  \end{tabular}
-
-  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-%  \hspace{1em}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-
-  \caption{
-    This image shows all aggregation levels for G* and Focal G* together 
-    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
-  }
-  \label{fig:Zoom}
-\end{figure*}
-
-\subsection{Blur}
-We also made an example for the variation of the weight size W.
-Blur is a slice plane through our three dimensional space. 
-W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
-For blur we also included the negative clusters which resulted in a surprising result.
-\begin{definition} Blur run:
-\begin{eqnarray*}
-    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_41) \\
-    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_41)
-  \end{eqnarray*}
-\begin{displaymath}
-i \in [0,11], G^* \in [Standard, Focal]
-\end{displaymath}
-\end{definition}
-The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
-shown in the first row, with increasing size. The scond and thrid row sho how
-$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
-weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that
-increase of the weight size leads in general to better results for Focal $G^*$.
-$G^*$ compared to the mean of our whiskerplot does not fit in the picture
-because it leads to better results than $G^*$.
-
-\begin{figure*}[htp]
-  \centering
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
-    \hline
-    \vspace*{2mm}
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
-  \end{tabular}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
-    \hline
-    \vspace*{2mm}
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
-  \end{tabular}
-
-  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
-
-  \caption{
-    This image shows different weight matrix sizes for G* and Focal G* together 
-    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
-  }
-  \label{fig:Blur}
-\end{figure*}
-
 \bibliographystyle{plain}

### 2017-06-17 paper-main.tex
updated introduction

@@
 
-But, similar to a cluster analysis, there does exist a high dependency of the identified hotspots on the detection method and in particular the parametrization of this method.
-The identified areas as well as their shape can vary highly.
-This volatility can lead to a decrease in trust in the result or in suboptimal allocations of scarce resources.
-Therefore it is necessary to measure and evaluate the stability of a hotspot analysis as well as the different parametrizations.
-In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .
-Here, we build upon that work and examine in more detail the impact of the 
-different instantiations of the most typical parameter. We use the well known 
+But, similar to a cluster analysis, the identified hotspots highly depend on 
+the parametrization of the detection method. The identified areas as well as 
+their shape can vary highly. This volatility can lead to a decrease in trust in 
+the result or in suboptimal allocations of scarce resources. Therefore, it is 
+necessary to measure and evaluate the stability of a hotspot analysis as well 
+as the different parametrizations.
+
+In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the 
+stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed 
+its use on the basis of temperature data.
+Here, we build upon that work and examine the impact of the 
+different instantiations of the most typical parameters in more detail. We use 
+the well known 
 Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
-this statistic, the Focal $G^*$~\cite{SoH-GI-Forum}. Those parameter are the 
-size of the study area (focal matrix), the detail of the resolution 
-(aggregation level) and the size of the neighbourhood (weight matrix). By 
-varying over these parameter, we can compare the stability for all possible 
-combinations and isolate the effect of single parameter by aggregation over the 
-other parameter. 
-We evaluate on the well-known taxi data set to show the applicability on real world use cases as well as to enable a simple replication.
+this statistic, the Focal~$G^*$~\cite{SoH-GI-Forum}.
+Those parameters examined are
+\begin{inparaenum}[(1)]
+   \item size of the study area given as a focal matrix,
+   \item pixel resolution i.e. aggregation level and 
+   \item the size of the neighbourhood given as a weight matrix.
+\end{inparaenum}
+By varying over these parameter, we can compare the stability for all possible 
+combinations and isolate the effect of a single parameter.
+We evaluate the metrics on the well-known dataset of New York Taxi drives to 
+show the applicability to real world use cases as well as to foster 
+reproducibility.
 

### 2017-06-17 analysis.Rmd
updated code to generate quantile-based hotspots

@@
 
-```{r demo-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
-z <- 0
+```{r demo-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
 for (g in zoom_gstar) {
-  z <- z + 1
-  plot_zscore(g,
-              title = sprintf("Standard G*: zoom=%d", z),
-              sigma_thresh = 2)
+  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
 }
@@
 
-```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
-z <- 0
+```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
 for (g in zoom_focalgstar) {
-  z <- z + 1
-  plot_zscore(g,
-              title = sprintf("Focal G*: zoom=%d", z),
-              sigma_thresh = 2)
+  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
 }
@@
 
-```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
-for (i in seq_along(wsizes)) {
-  ws <- wsizes[i]
-  g <- blur_gstar[[i]]
-  plot_zscore(g,
-              title = sprintf("Standard G*: wsize=%d", ws),
-              sigma_thresh = 2)
+```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
+for (g in blur_gstar[RENDERED_IDX]) {
+  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
 }
@@
 ```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
-for (i in seq_along(wsizes)) {
-  ws <- wsizes[i]
-  g <- blur_focalgstar[[i]]
-  plot_zscore(g,
-              title = sprintf("Focal G*: wsize=%d", ws),
-              sigma_thresh = 2)
+for (g in blur_focalgstar[RENDERED_IDX]) {
+  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
 }

### 2017-06-17 R/hotspot_analysis_lib.R
added `show.legend` parameter to `plot_zscore` function

@@ -94,18 +94,29 @@ plot_temp_map <- function(
 plot_zscore <- function(
   r, sigma_thresh = 5,
   hotspot_quantile_thresh = .01,
-  title = NULL)
+  title = NULL,
+  show.legend = TRUE)
 {
 
   hotspots <- quantile(r, na.rm = TRUE,
                        probs = c(hotspot_quantile_thresh,
                                 1 - hotspot_quantile_thresh))
 
-  par(mar = c(4,5,4,2) + .1)
+  if (show.legend) {
+    par(mar = c(4,5,4,2) + .1)
+  } else {
+    par(mar = rep(0, 4))
+  }
+
   plot(r, axes = FALSE, alpha = .7,
        col = gray.colors(100),
-       legend.args = list(text = "z-score",
-                          side = 3, font = 2, line = 0, cex = 0.8))
+       legend = show.legend, box = show.legend,
+       colNA = "black",
+       legend.args = if (show.legend) {
+         list(text = "z-score", side = 3, font = 2, line = 0, cex = 0.8)
+       } else {
+         NULL
+       })
 
   rth <- r
   rth[abs(r) < sigma_thresh] <- NA
@@ -116,18 +127,20 @@ plot_zscore <- function(
   # contours + legend
   contour(rth, lwd = 4, add = TRUE, levels = hotspots, col = c("blue", "red"))
 
-  e <- extent(r)
-  legend(e@xmax, e@ymin,
-         xjust = 1,
-         yjust = 0,
-         bg = rgb(1, 1, 1, 0.85),
-         legend = c(sprintf("top %g%% quantile hotspots (%g)",
-                            round( hotspot_quantile_thresh * 100, 2),
-                            round( hotspots[2], 2)),
-                    sprintf("bottom %g%% quantile hotspots (%g)",
-                            round( hotspot_quantile_thresh * 100, 2),
-                            round( hotspots[1], 2)) ),
-         fill = c("red", "blue"))
+  if (show.legend) {
+    e <- extent(r)
+    legend(e@xmax, e@ymin,
+           xjust = 1,
+           yjust = 0,
+           bg = rgb(1, 1, 1, 0.85),
+           legend = c(sprintf("top %g%% quantile hotspots (%g)",
+                              round( hotspot_quantile_thresh * 100, 2),
+                              round( hotspots[2], 2)),
+                      sprintf("bottom %g%% quantile hotspots (%g)",
[…]

### 2017-06-17 paper-main.tex
added quantile-based images to latex

@@
   \end{tabular}
+
+  \vspace{1em}
   \begin{tabular}{cccccccc}
@@
     \hline
-    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
@@
     \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}\\
+
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}\\
+
   \end{tabular}
+
+  \vspace{1em}
   \begin{tabular}{cccccccc}
@@
     \hline
-    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
@@
     \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}\\
+
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-8}\\
   \end{tabular}
 
+  \vspace{2em}
   \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
@@
   \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
-%  \hspace{1em}
-%  \includegraphics[width=.45\linewidth]{images/gen-???}
 
@@
     \hline
-    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
@@
     \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}\\
+
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-gstar-8}\\
   \end{tabular}
+
+  \vspace{1em}
   \begin{tabular}{cccccccc}
@@
     \hline
-    \vspace*{2mm}
     \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
@@
     \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
+    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}\\
+
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-1}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-2}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-3}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-4}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-5}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-6}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-7}&
+    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-8}\\
   \end{tabular}
 
+  \vspace{2em}
   \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}

### 2017-06-17 paper-main.tex
minor fixes

@@
 The first parameter we want to isolate is the size of the study area. This enables us to discuss the optimal size of the study area for the given research/decision question. 
-To do so, we have to fix the focal size F and use it as the x-axis and plot the mean value as well as the mean +- the standard deviations of the SoH for all other parameter combinations as the y-axis.
+To do so, we have to fix the focal size F and use it as the x-axis and plot the 
+mean value as well as the mean +/- the standard deviations of the SoH for all 
+other parameter combinations as the y-axis.
 In this scenario, only the Focal $G^*$ can produce varied results as the standard $G^*$ has by definition a fixed study area by always using the total size of the study area. 
-In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and Focal $G^*$.
-Higher values indicate that the found hot spots are more stable. 
-The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
+In Figure~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and 
+Focal $G^*$.
+Higher values indicate that the hot spots found are more stable. 
+The \SOHUP in Figure~\ref{fig:fUp} growth with an increase of the focal size.
 It can see that an increase of the focal size leads to better results for \SOHUP. 
@@
 When F and W have similar size, there are no clusters. Because the values have no much variation. 
-\SOHDOWN (figure ~\ref{fig:fDown})shows a different picture then the \SOHUP.
+\SOHDOWN (Figure ~\ref{fig:fDown}) shows a different picture then the \SOHUP.
 It reaches its maximum SoH for a focal size F of 65x65 in our evaluation set. 
@@
 computational effort on future computations by using the maximal aggregation as useful.
-The results can seen in figure ~\ref{fig:SoHZoom}.
+The results can seen in Figure~\ref{fig:SoHZoom}.
 First, we can see that for the aggregation level, in contrast to previous 
@@
 
-With this work we made a step further to the optimal parametrisation for $G^*$ and Focal $G^*$.
-Our results indicate that the parametrisation for $G^*$ and Focal $G^*$ besides what is defined as parent and child has a huge impact on the
+With this work, we made a step further to the optimal parametrisation for $G^*$ 
+and Focal $G^*$.
+Our results indicate that the parametrization for $G^*$ and Focal $G^*$ besides 
+what is defined as parent and child has a huge impact on the
 stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
@@
 As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research.
-We evaluated our data on the aggregate of a singular month, but one could assume that at lunchtime there will be hotspots at restaurants and they are not consistent with the hotspots over one month.
-Therefore the impact of time on the results is important and could also influence the metric for stability in profound ways.
-As in the example the question is, how fine grained should the temporal clustering be and when is the result unstable for useful reasons?
-This leads to the final future work: To which hot spots should the comparison be made for the metric?
-In the current state only the next parametrization is compared for computational time reasons.
-How the comparison hot spots should be chosen and how many different comparisons have to be used is another quite interesting question for future work.
+We evaluated our data on the aggregate of a single month, but one could assume 
+that during the lunchtime there will be hotspots at restaurants and they are 
+not 
+consistent with the hotspots over one month. Therefore the impact of time on 
+the results is important and could also influence the metric for stability in 
+profound ways. As in the example, the question is, how fine grained should the 
+temporal clustering be and when is the result unstable? 
+This leads to the final future work: To which hot spots should the comparison 
+be made for the metric? In the current state, only the next parametrization is 
+compared due to the high computational complexity. How the comparison of hot 
+spots should be carried out and how many different comparisons have to be used 
+is another quite interesting research question.
 
@@
 \noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr}
+\verb|knitr|~\cite{cran:knitr},
 

### 2017-06-17 paper-main.tex
fixed some todos

@@
   \\
-  \email{todo@fzi.de},
+  \email{marcgassenschmidt@googlemail.com},
   \email{simko@fzi.de},
@@
 
-The results can be found in Fig.~\ref{fig:Zoom}. It can be seen that with an
-increase of the aggregation level the values increase. TODO if clusters
+The results can be found in Figure~\ref{fig:Zoom}. It can be seen that with an
+increase of the aggregation level the values increase. 
+%TODO: there was some todo in the text for the following sentence
+If clusters
 increase/decrease For the upward property, $G^*$ is always better than Focal

### 2017-06-17 paper-main.tex
Updated Blur and Aggregation

@@
 increase of the aggregation level the values increase. 
-%TODO: there was some todo in the text for the following sentence
-If clusters
-increase/decrease For the upward property, $G^*$ is always better than Focal
+If the aggregation level increases the number of cluster decreases. It can seen that
+small clusters are disappearing and some clusters are growing to big ones. From aggreagtion level~2 to
+aggreagtion level~3 there is no big change in the images of Focal $G^*$ which is consitent with our results.
+For the upward property, $G^*$ is always better than Focal
 $G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
-reaches the same result as $G^*$ at aggregation level~5 . For the downward
-property, Focal $G^*$ leads to better results at aggregation level~5.
+reaches the same result as $G^*$ at aggregation level~6 . For the downward
+property, Focal $G^*$ leads to better results at aggregation level~6.
 
@@
 The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
-shown in the first row, with increasing size. The 2nd and 3th row show how
+shown in the first row, with increasing size. The 2nd and 4th row show how
 $G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
 weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
-increase of the weight size leads in general to better results for Focal $G^*$.
+increase of the weight size leads in general to better results for $G^*$.
+Also it can bee seen that for focal $G^*$ the clusters are more distributed over the raster.
 

### 2018-05-23 Alt_Stuff/lipics-v2018-sample-article.tex
Ideas, new stuff, etc.

--- 2017-06-17 paper-main.tex
@@
-\documentclass{itatnew}
-
+\documentclass[a4paper,UKenglish]{lipics-v2018}
+%This is a template for producing LIPIcs articles. 
+%See lipics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+% for section-numbered lemmas etc., use "numberwithinsect"
 \usepackage{paralist} % inparaenum support
@@
 \usepackage{xcolor} % added by Viliam for \textcolor
+\usepackage{microtype}%if unwanted, comment out or use option "draft"
+
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 
@@
 \usepackage{booktabs}
-\usepackage[british]{babel}
+%\usepackage[british]{babel}
 
@@
 
+\bibliographystyle{plainurl}% the recommnded bibstyle
+
+\title{Dummy title}
+
+\titlerunning{Dummy short title}%optional, please use if title is longer than one line
+
+\author{John Q.
+Public}{Dummy University Computing Laboratory, [Address], Country}{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{[funding]}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+
+\author{Joan R. Public}{Department of Informatics, Dummy College, [Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}
+
+\authorrunning{J.\,Q. Public and J.\,R. Public}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
+
+\keywords{Dummy keyword}%mandatory
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{I want to thank \dots}%optional
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+%\nolinenumbers %uncomment to disable line numbering
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\title{Stable Hot Spot Analysis (Draft)}
-
-\author{
-  Marc Gassenschmidt \and
-  Viliam Simko  \and
-  Julian Bruns
-  \\
-  \email{marcgassenschmidt@googlemail.com},
-  \email{simko@fzi.de},
-  \email{bruns@fzi.de}
-}
-
-\institute{
-  FZI Forschungszentrum Informatik\\
-  am Karlsruher Institut f\"ur Technologie\\
-  76131, Haid-und-Neu-Str. 10-14\\
-  Karlsruhe, Germany
-}
-
-\maketitle              % typeset the title of the contribution
+\maketitle
 
@@
 \noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr},
+\verb|knitr|~\cite{cran:knitr}, %% Please use bibtex,
 
-\bibliographystyle{plain}
-\bibliography{bibfile}  % sigproc.bib is the name of the
+\bibliography{bibfile}
 

### 2018-05-23 Workshop_GIScience_BigData_Vision.tex
Ideas, new stuff, etc.

--- 2017-06-17 paper-main.tex
@@
-\documentclass{itatnew}
+\documentclass[a4paper,UKenglish]{lipics-v2016}
+%This is a template for producing LIPIcs articles. 
+%See lipics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+% for section-numbered lemmas etc., use "numberwithinsect"
 
-\usepackage{paralist} % inparaenum support
-\usepackage{varioref} % added by Viliam for \vref
-\usepackage{xcolor} % added by Viliam for \textcolor
-
+\usepackage{microtype}%if unwanted, comment out or use option "draft"
 \usepackage{caption}
@@
 \usepackage{booktabs}
-\usepackage[british]{babel}
+\usepackage{paralist} % inparaenum support
+\usepackage{varioref} % added by Viliam for \vref
+\usepackage{xcolor} % added by Viliam for \textcolor
+%\usepackage[british]{babel}
 
@@
 
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+
+\bibliographystyle{plainurl}% the recommended bibstyle
+
+% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Vision Paper: Efficient Spatio-Temporal Geo-Statistics for Exploratory Data Analysis}
+%\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
+\titlerunning{Efficient Spatio-Temporal Geo-Statistics} %optional, in case that the title is too long; the running title should fit into the top page column
+
+%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
+\author[1]{Julian Bruns}
+\author[1]{Joan R. Access}
+\affil[1]{GIScience Research Group, Institute of Geography, Heidelberg University, Heidelberg, Germany\\
+  \texttt{firstname.lastname@uni-heidelberg.de}}
+
+\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+
+\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
+E.g., cite as "F.1.1 Models of Computation".
+\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Acces}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\title{Stable Hot Spot Analysis (Draft)}
-
-\author{
-  Marc Gassenschmidt \and
-  Viliam Simko  \and
-  Julian Bruns
-  \\
-  \email{marcgassenschmidt@googlemail.com},
-  \email{simko@fzi.de},
-  \email{bruns@fzi.de}
-}
-
-\institute{
-  FZI Forschungszentrum Informatik\\
-  am Karlsruher Institut f\"ur Technologie\\
-  76131, Haid-und-Neu-Str. 10-14\\
-  Karlsruhe, Germany
-}
-
-\maketitle              % typeset the title of the contribution
+\maketitle
 
@@
 
-\section{Introduction}
+\section{Introduction and Related Work}
 The goal of hotspot analysis is the detection and identification of interesting areas.
@@
 
-\section{Related Work}
+\section{State of the Art}
+
+\section{Vision}
+
+\section{Challenges}
+
+\section{Conclusion}
 
@@
 \noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr},
+\verb|knitr|~\cite{cran:knitr}, %% Please use bibtex,
 
-\bibliographystyle{plain}
-\bibliography{bibfile}  % sigproc.bib is the name of the
+\bibliography{references}
 

### 2018-05-23 lipics-v2016-sample-article.tex
Ideas, new stuff, etc.

--- 2018-05-23 Workshop_GIScience_BigData_Vision.tex
@@
 \usepackage{microtype}%if unwanted, comment out or use option "draft"
-\usepackage{caption}
+e{caption}
 \usepackage{subcaption}
@@
 \usepackage{booktabs}
-\usepackage{paralist} % inparaenum support
-\usepackage{varioref} % added by Viliam for \vref
-\usepackage{xcolor} % added by Viliam for \textcolor
 %\usepackage[british]{babel}
@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Vision Paper: Efficient Spatio-Temporal Geo-Statistics for Exploratory Data Analysis}
-%\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
-\titlerunning{Efficient Spatio-Temporal Geo-Statistics} %optional, in case that the title is too long; the running title should fit into the top page column
+\title{A Sample Article for the LIPIcs series\footnote{This work was partially supported by someone.}\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
+\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
 
 %% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{Julian Bruns}
-\author[1]{Joan R. Access}
-\affil[1]{GIScience Research Group, Institute of Geography, Heidelberg University, Heidelberg, Germany\\
-  \texttt{firstname.lastname@uni-heidelberg.de}}
-
+\author[1]{John Q. Open}
+\author[2]{Joan R. Access}
+\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
+  \texttt{open@dummyuniversity.org}}
+\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
+  \texttt{access@dummycollege.org}}
 \authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
@@
 
-\section{Introduction and Related Work}
+\section{Introduction}
 The goal of hotspot analysis is the detection and identification of interesting areas.
@@
 
-\section{State of the Art}
-
-\section{Vision}
-
-\section{Challenges}
-
-\section{Conclusion}
+\section{Related Work}
 

### 2018-05-24 Workshop_GIScience_BigData_Vision.tex
updated paper

@@
 Hot spot analysis is essential for geo-statistics.
-It supports decision making by detecting points
-as well as areas of interest in comparison to their
-neighbourhood. However, these methods are dependent
-on different parameters, ranging from the resolution
-of the study area to the size of their neighbourhood.
-This dependence can lead to instabilities of the detected
-hotspots, where the results can highly vary between
-different parameters. A decision maker can therefore ask
-how valid the analysis actually is.
-%
-In this study, we examine the impact of key parameters
-on the stability of the hotspots, namely the size of
-the neighbourhood, the resolution and the size of the
-study area, as well as the influence of the ratio between
-those parameters.
-%
-We compute the hotspots with the well known Getis-Ord ($G^*$)
-statistic as well as its modification, the \emph{Focal $G^*$} statistic.
-We measure the stability of the hotspot analysis using
-a recently introduced \emph{stability of hotspots} metric (SoH)
-and compare the results to intuitive visual analysis.
-%
-We evaluate the results on real world data with the well-known
-yellow cab taxi data set from New York, Manhattan.
-Our results indicate a negative impact on the stability with
-a reduction of the size of the neighbourhood as well as
-a reduction of the size of the study area, regardless of
-the resolution.
+
 \end{abstract}
@@
 
-But, similar to a cluster analysis, the identified hotspots highly depend on 
-the parametrization of the detection method. The identified areas as well as 
-their shape can vary highly. This volatility can lead to a decrease in trust in 
-the result or in suboptimal allocations of scarce resources. Therefore, it is 
-necessary to measure and evaluate the stability of a hotspot analysis as well 
-as the different parametrizations.
+Huge in increase in data, e.g. even without incorporating spatial structures the OSM\cite{OpenStreetMap} data, as example for VGI, is over 1 TB
 
-In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the 
-stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed 
-its use on the basis of temperature data.
-Here, we build upon that work and examine the impact of the 
-different instantiations of the most typical parameters in more detail. We use 
-the well known 
-Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
-this statistic, the Focal~$G^*$~\cite{SoH-GI-Forum}.
-Those parameters examined are
-\begin{inparaenum}[(1)]
-   \item size of the study area given as a focal matrix,
-   \item pixel resolution i.e. aggregation level and 
-   \item the size of the neighbourhood given as a weight matrix.
-\end{inparaenum}
-By varying over these parameter, we can compare the stability for all possible 
-combinations and isolate the effect of a single parameter.
-We evaluate the metrics on the well-known dataset of New York Taxi drives to 
-show the applicability to real world use cases as well as to foster 
-reproducibility.
+\subsection{Examples}
+
+Spatio-temporal sentiment hotspot detection using geotagged photos \cite{Zhu:2016:SSH:2996913.2996978}
+
+A framework for evacuation hotspot detection after large scale disasters using location data from smartphones: case study of Kumamoto earthquake \cite {Yabe:2016:FEH:2996913.2997014}
+
+\cite{Wiener:2016:BCR:2996913.2996931} BigGIS Vision Paper
+
+\cite{7129542} The era of big spatial data : 
+"Unfortunately, the urgent need to manage and analyze big
+spatial data is hampered by the lack of specialized systems,
+techniques, and algorithms to support such data." "We
+provide general guidelines to show the four components that
+are needed in a system for big spatial data." 
+In general an overview of approaches in 2015 and overall targets for systems
+
+\cite{mehta2016spatio}   Spatio-Temporal Hotspot Computation on Apache Spark (GIS Cup)
+
+Giscup 2016 \footnote{http://sigspatial2016.sigspatial.org/giscup2016/home}
 
 \section{State of the Art}
+\subsection{Geostatistic}
+While the standard hot spot analysis approaches allow for a fast and automated exploratory analysis of spatial data sets, they are highly dependent on their parametrizations and underlying data.
+This is quite similar to the challenges in clustering, in particular for the well-known k-means, first coined in \cite{macqueen1967some}, or DBScan (\cite{ester1996density}) algorithm.
+This leads to an instability of the analysis results, which are then difficult to use with high certainty.
+Here, a selection of approaches and discussions of the last 15 years are presented how to tackle this instability.
+
+The most general approach is to pre-determine and calculate spatial dependencies, based on the a-priori knowledge of the analyst, the empirical data set or best-practices from previous, similar analyses.
+A good example for this approach can be found in \cite{suomi2012effects}.
+In their work, the authors examine the effects of scale on temperature and in particular urban heat island modeling.
+The pre-determined range of spatial influences is called \emph{buffer zones}; these buffer zones indicate the range of impact in an inner-city temperature measurement scenario.
+They found that for their empirical data set a buffer zone of 1000m provides the best results.
+This is familiar to the well-known approach to solve the inherent problem of DBScan, the determination of its distance: OPTICS (\cite{ankerst1999optics}).
+The disadvantage of this approach is that it has to be manually pre-determined, which results in similar problems as the semi-supervised methods to detect points of interest.
+It can not be done automatically without introducing an element of uncertainty, which is opposed to our goal to create a more stable approach.
+
+An automated approach is presented with the \emph{A Multidirectional Optimal Ecotope-Based Algorithm} (AMOEBA) in \cite{aldstadt2006using}.
+The idea behind this approach is to automatically create the optimal, scale-invariant weight matrix and then use this weight matrix in conjunction with a clustering approach to create a graphical overview map of areas of interest.
+The term ecotope is used for this areas, which is the technical term from the field of biology for the habitat of species.
+The result is a consistent identification of spatial clusters on a map.
+In their work they use the $G^*$ statistic as the underlying statistic.
+The clustering approach is quite similar to DBScan in its approach of creating ecotopes.
+
+A true modification of the $G^*$ statistic is presented in a later work (\cite{getis2010constructing}) of the same authors called the LSM (local statistics model).
+They base their modification on the Kriging approach and its ability to model the spatial autocorrelation as a function dependent on the distance.
+The idea is to model the weight matrix W as a function of the spatial autocorrelation, where each entry of the matrix is a value derived from the empirical  (semi-)variogram.
+This leads to continuous values up to the so called \emph{critical distance}, which is "defined as the distance beyond which no discernible increase in clustering exist" (\cite{getis2010constructing}).
+They compare their configuration to other, well-known spatial configuration approaches for the weight matrix W.
+These are taken from \cite{griffith1996some} and in the words of \cite{getis2010constructing}:
+''Research on W has been reviewed by Griffith (1996, p. 80), who concludes that five rules of thumb aid in the specification of weights matrices: 
+\begin{enumerate}
+\item “It is better to posit some reasonable geographic weights matrix than to assume independence.” This implies that one should search for or theorize about an appropriate W and that better results are obtained when distance is taken into account.
+\item “It is best to use surface partitioning that falls somewhere between a regular square and a regular hexagonal tessellation.” Griffith suggests that for planar data, a specification between four and six neighbors is better than something either above six or below four.
+Of course, the configuration of the planar tessellations will play a role here (\cite{boots2000global}).
+\item “A relatively large number of spatial units should be employed, n > 60.” Following from the law of large numbers, most spatial research, especially due to unequal size spatial units, would require fairly large samples.
+\item “Low-order spatial models should be given preference over higher-order ones.” Following from the scientific principle of parsimony, it is always wise to choose less complicated models when the opportunity presents itself.
+\item “In general, it is better to apply a somewhat under-specified (fewer neighbors) rather than an over-specified (extra neighbors) weights matrix.” \cite{florax1995impacts} found this result by identifying the power of tests.
+Overspecification reduces power.
+They recognize that “Uncertainty with respect to proper specification has long been recognized as a fundamental problem in applied spatial econometric modeling” (p.
+132).
+\end{enumerate}
+''
+
+\cite{ord2001testing} discuss the question in how to formulate the $G^*$ statistic to focus more on local pattern, while still accounting for the global autocorrelation.
+They propose the $O$ statistic which uses the (semi-)variogram to subdivide the data set into several '' 'relatively homogeneous' subregions'' (\cite{ord2001testing}).
+This allows the identification of smaller, more local hot spots, which can be overshadowed in bigger data sets.
+Finally, they restrict the general applicability in that the version presented in their work requires spatial stationarity.
+
+\cite{westerholt2015local} present a scale-sensitive version of the local $G^*$ statistic, which they call the \emph{GS statistic}.
+The motivation for this modification is to account for the differences in the scale (the impact of the area under investigation) of the data set, i.e.
+whether a data set includes only the inner city or also its surrounding area.
+The problem lies in the detection and use of the local context of the gathered data.
+A fixed weight matrix W does not include the difference in context, e.g.
+in Twitter feeds.
+Their approach is to redefine the neighborhood of a data point with upper and lower distance thresholds, which are then used in pairwise comparisons.
+Only sufficiently connected data points within their thresholds are considered to be viable as a hot spot and only those points are used for the global mean and global deviation values.
+They evaluated their approach on Twitter data of the city of San Francisco, USA and show that this leads to reduction or even negation of cross-scale interference.
+The main restrictions of this approach lies in its increased computational costs as well as its reliance on continuous distance functions.
+
+For futher literature regarding the creation of optimal weight matrices for spatial associations we refer to the work of \cite{aldstadt2006using}, where they provide an exhaustive overview of the state of the art.
+
+\cite{Bruns2017} for focal $G^*$ and efficient parametrization of $G^*$
+
+\subsection{Frameworks and Methods}
+An Effective High-Performance Multiway Spatial Join Algorithm with Spark \cite{ijgi6040096}
+"In this paper, we present an effective
+high-performance multiway spatial join algorithm with Spark (MSJS) to overcome the multiway
+spatial join bottleneck." "Spatial analysis is the core engine that drives research and applications of GIS."
+
+GeoSpark: a cluster computing framework for processing large-scale spatial data \cite{Yu:2015:GCC:2820783.2820860}
+
+Spatio-Temporal Join on Apache Spark \cite{Whitman:2017:SJA:3139958.3139963}
+
+Algorithmically-Guided User Interaction \cite{vanDijk:2017:AUI:3139958.3140032}
+
+GeoMesa: a distributed architecture for spatio-temporal fusion \cite{hughes2015geomesa}
+
+geotrellis\footnote{https://geotrellis.io/}
 
@@
 \section{Conclusion}
-
-\subsection{Quality of Clustering}
-The problem of assessing the quality in unsupervised learning is well known.
-In the case of the k-mean algorithm, the quality of the clustering is mostly dependent on the value of the \emph{k} and a miss-specification can lead to highly irregular clusters.
-In a simple 2D clustering, they can be easily recognized by visual analysis, but in higher dimensionality, this is impossible.
-One method, to measure the quality of such a clustering is the compactness of the clusters, see e.g.
-\cite{CompactnessDataClustering}.
-This enables the comparison between different clusters.
-Another possibility is the Silhouette Coefficient by Kaufman et Rousseeuw 1990.
-This metric measures the similarity of objects in a cluster in comparison to other clusters.
-For density based clustering, e.g.
-for DBSCAN~\cite{Ester96adensity-based}, OPTICS~\cite{Ankerst:1999:OOP:304181.304187} gives a simple method to tune the essential parameter for this clustering.
-This is only a small overview of methods to influence and measure the quality of different clustering methods.
-But it shows that this problem is not easily solved and dependent on the chosen algorithm.
-To our knowledge, there does not exist a method to overall measure the stability of a clustering.
 
@@
 values, but instead to focus on local hotspots and to measure the significance
-of those local areas. A more in depth overview of methods to identify and visualize spatial patterns and areas of interest can be found in \cite{shekhar2011identifying}.
-
-\section{Stability of Hot Spot Analysis}
-\label{sec:Metric}
+of those local areas.
 
@@
 increasing the size of a weight matrix has a "blurring" effect on the raster
-(Figure~\ref{fig:BlurExample:a}) whereas decreasing the size can be 
-seen as a form of "sharpening" (Figure~\ref{fig:BlurExample:b}).
-
-%TODO: add image showing and blurring/sharpening effects
-
-%As we can see, hot spots are oftentimes disappearing or appearing unrelated to
-%previously found hot spots. While these computations indeed show hot spots and
-%the results are correct, they lack stability.
-
-For a data analyst, when exploring the data interactively by choosing different
-filter sizes (weight matrices) or point aggregation strategies (pixel sizes), it
-is important that the position and size of a hot spot changes in a predictable
-manner. We formalize the intuition in our stability metric.
-
-%
-%Consider the real-world example depicted in Figure~\ref{fig:TempMaps}.
-%%TODO: thermal flight -> NY taxi
-%The temperature map of a morning thermal flight dataset 
-%(Figure~\ref{fig:TempMaps:a}) has been processed using $G^*$.
-%
-%%TODO: thermal flight -> NY taxi
-%%TODO: need two images - G* and FocalG*
-\begin{figure}[htp]
-  \centering
-  \begin{subfigure}{.3\linewidth}
-    \caption{Small matrix}
-    \includegraphics[width=\linewidth]{images/gen-raw-blur-gstar-2}
-    \label{fig:BlurExample:a}
-  \end{subfigure}
-  \begin{subfigure}{.3\linewidth}
-    \caption{Large matrix}
-    \includegraphics[width=\linewidth]{images/gen-raw-blur-gstar-8}
-    \label{fig:BlurExample:b}
-  \end{subfigure}
-  \caption{
-    Example of G* statictics computed for the same raster with different weight 
-    matrix sizes.
-  }
-\end{figure}
-
-We define a hot spot found in comparably more coarse resolutions as
-\emph{parent} (larger weight matrix or larger pixel size) and in finer
-resolutions as \emph{child} (smaller weight matrix or smaller pixel size).
-
-Stability assumes that every parent has at least one child and that each child
-has one parent. For a perfectly stable interaction, it can be easily seen that
-the connection between parent and child is a injective function and between
-child and parent a surjective function. To measure the stability,
-we propose a metric called the \emph{Stability of Hot spot} (SoH). It measures
-the deviation from a perfectly stable transformation between the parent and 
-chaild rasters (like frames of an animation).
-
-In its downward property (from parent to child, injective) it is defined as:
-\begin{equation}
-  \label{eq:SoH-down}
-  \SOHDOWN
-    = \frac{ParentsWithChildNodes}{Parents}
-    = \frac{|Parents \cap Children|}{|Parents|}
-\end{equation}
-And for its upward property (from child to parent, surjective):
-\begin{equation}
-  \label{eq:SoH-up}
-  \SOHUP
-    = \frac{ChildrenWithParent}{Children}
-    = 1 - \frac{|Children - Parents|}{|Children|}
-\end{equation}
-where $ParentsWithChildNodes$ is the number of parents that have at least one 
-\emph{child}, $Parents$ is the total number of \emph{parent}, 
-$ChildrenWithParent$ is the number of children and $Children$ as the total 
-number of children.
-The SoH is defined for a range between 0 and 1, where 1 represents a perfectly 
-stable transformation while 0 would be a transformation with no stability at 
-all.
-If $|Children|=0$ or $|Parents|=0$ SoH is 0.
-
-%\section{Focal Getis-Ord}
-%\label{sec:FocalGetisOrd}
-%
-%In paper~\cite{SoH-GI-Forum}, we have defined the measure Focal G*.
-%We use the notation \FOCAL{R}{M}{op} to denote a focal
-%operation $op$ applied on a raster $R$ with a focal window determined by a
-%matrix $M$. This is rougly eqivalent to a command \verb|focal(x=R, w=M, 
-%fun=op)|
-%from package \emph{raster} in the R programming language \cite{cran:raster}.
-
-%\begin{definition}[$G^*$ function on rasters]
-%  \label{def:GenericGetisOrdFunc}
-%  
-%  The function $G^*$ can be expressed as a raster operation:
-%  
-%  \begin{displaymath}
-%    G^*(R, W, st) =
-%    \frac{
-%      \FOCAL{R}{W}{sum} - M*\sum_{w \in W}{w}
-%    }{
-%      S \sqrt{
-%        \frac{
-%          N*\sum_{w \in W}{w^2} - (\sum_{w \in W}{w})^2
-%        }{
-%          N - 1
-%        }
-%      }
-%    }
-%  \end{displaymath}
-%  \noindent where:
-%  \begin{itemize}
-%    
-%    \item $R$ is the input raster.
-%    
-%    \item $W$ is a weight matrix of values between 0 and 1.
-%    
-%    \item $st = (N, M, S)$ is a parametrization specific to a particular 
-%version
-%    of the $G^*$ function. (Def.\vref{def:StdGetisOrdVersion} and
-%    \vref{def:FocalGetisOrdVersion}).
-%    
-%  \end{itemize}
-%\end{definition}
-%
-%\begin{definition}[Standard $G^*$ parametrization]
-%  \label{def:StdGetisOrdVersion}
-%  
-%  Computes the parametrization $st$ as global statistics for all pixels in the
-%  raster $R$:
-%  
-%  \begin{itemize}
-%    \item $N$ represents the number of all pixels in $R$.
-%    \item $M$ represents the global mean of $R$.
-%    \item $S$ represents the global standard deviation of all pixels in $R$.
-%  \end{itemize}
-%\end{definition}
-%
-%\begin{definition}[Focal $G^*$ parametrization]
-%  \label{def:FocalGetisOrdVersion}
-%  
-%  Let $F$ be a boolean matrix such that: $all(dim(F) \geq dim(W))$.
-%  This version uses focal operations to compute per-pixel statistics given by 
-%  the focal neighbourhood $F$ as follows:
-%  
-%  \begin{itemize}
-%    
-%    \item $N$ is a raster computed as a focal operation \FOCAL{R}{F}{sum}. Each
-%    pixel represents the number of pixels from $R$ convoluted with the matrix
-%    $F$. 
-%    
-%    \item $M$ is a raster computed as a focal mean \FOCAL{R}{F}{mean}, thus 
-%each
-%    pixel represents a mean value of its $F$-neighbourhood.
-%    
-%    \item $S$ is a raster computed as a focal standard deviation
-%    \FOCAL{R}{F}{sd}, thus each pixel represents a standard deviation of its
-%    $F$-neighbourhood.
-%    
-%  \end{itemize}
-%  
-%\end{definition}
+(
 
@@
 
-%\begin{definition}[Evaluation Run]
-%  \label{def:EvalRun}
-%  We define a single evaluation run as a tuple:
-%  \begin{displaymath}
-%    E = (V, m, p, w)
-%  \end{displaymath}
-%  \noindent where:
-%  \begin{itemize}
-%  
-%    \item $V$ is the input dataset of points, representing the taxi dropoffs 
-%in 
-%    our case.
-%    
-%    \item $m$ is the metric used, in our case either \SOHUP or \SOHDOWN.
-%    
-%    \item $p$ represents the pixel size for aggregating points from $V$, 
-%    e.g. $100 \times 100$ meters.
-%    
-%    \item $w$ represents the size of a weight matrix.
-%    In our case, we chose a weight matrix depicted in 
-%    Figure~\ref{fig:ExampleMatrices}(a) for both the G* and FocalG* cases.
-%  \end{itemize}
-%\end{definition}
-
-%Figure~\ref{fig:ComparisonMorning} and Figure~\ref{fig:ComparisonEvening} show
-%Standard and Focal $G^*$ computations for both morning and eventing datasets
-%with weight matrix $W$ of size 3, 5, 7, 9, 15 and 31. In this figures, when 
-%computing Focal
-%$G^*$, the focal matrix $F$ has a constant size of $61{\times}61$ cells. 
-%Example weight matrix $W$ and focal matrix $F$ are depicted in 
-%Figure~\ref{fig:ExampleMatrices}.
-
-Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
-For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
-%
-For our measurements we specified the following data series:
-\begin{itemize}
- \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
- \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
- \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
-\end{itemize}
-\begin{definition}
-
-  \begin{displaymath}
-    \SOHUP(child, parent)
-  \end{displaymath}
-  \begin{displaymath}
-    \SOHDOWN(child, parent)
-  \end{displaymath}
-
-  The SoH for a singled evalution run in the weight dimension is defined as:
-  \begin{eqnarray*}
-    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
-    parent & = & G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
-  \end{eqnarray*}
-  The SoH for a singled evalution run in the focal dimension is defined as:
-  \begin{eqnarray*}
-    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
-    parent & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
-  \end{eqnarray*}
-  The SoH for a singled evalution run in the aggregation dimension is defined 
-  as:
-  \begin{eqnarray*}
-    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
-    parent & = & G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
-  \end{eqnarray*}
-
-  \begin{displaymath}
-  z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
-  \end{displaymath}
-\end{definition}
-
-Therefore we would calculate $10 \cdot 10 \cdot 5 + 10 \cdot 5=550$ results for each dimension.
-The following conditions must hold $dim(F) > dim(W)$ and $dim(F) < dim(R)$ 
-which leads e.g. to 460 results in the z-dimension.
-We vary over the weight matrix W, the focal matrix F and the aggregation level, as motivated in the introduction.
-To compare the impact each of these parameters has we compute all variations 
-over two parameter and holding one parameter fix. We then calculate the mean as 
-well as the standard deviation for the SoH for the fixed value based on the two 
-other parameters. This allows us to isolate the impact of the variation in the 
-single parameter. The results are then plotted in 
-Figures~\ref{fig:SoHFocal}--\ref{fig:SoHZoom}, one image for each fixed 
-parameter and the direction of the SoH.
-The hotspots to use the SoH on are computed by the focal $G^*$ and standard $G^*$ method.
-The focal $G^*$ allows us, to isolate the impact that the size of the study area has on the stability of the results without recomputing the total dataset.
-\subsection{Clumping}
-
-The SoH needs a parent and a child. Clusters can be calculated different. For
-$G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less
-then 1\% of the cases you are wrong. The values of Focal $G^*$ depend on the
-focal size F. Therefore, we decide all values in the top quantile belong to a
-clusters. For clustering we grouped the neighbourhood with values in the top
-quantile to one cluster. Neigbours are are pixels with touching edges which
-leads for every pixel to 8 neigbours. Fig.~\ref{fig:Clumping} depicts the 
-clusters using different colours. In this figure, Focal~$G^*$ has smaller 
-clusters which are distributed over the complete raster.
-
-\begin{figure}[htp]
-  \centering
-
-  \begin{subfigure}{.7\linewidth}
-    \caption{G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
-    \label{fig:ClustDiffGstar}
-  \end{subfigure}
-  \hspace{3em}
-  \begin{subfigure}{.7\linewidth}
-    \caption{Focal G* clustering difference}
-    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
-    \label{fig:ClustDiffFocalGstar}
-  \end{subfigure}
-
-  \caption{
-    Example clustering for G* and Focal G* used as a input for SoH computation.
-  }
-  \label{fig:Clumping}
-\end{figure}
-
-\subsection{Aggregate}
-
-The aggregation level is a slice plane through our three dimensional space. 
-This is an example how the results can look with visualize representations of the calculated 
-rasters and the raw data.
-\begin{definition} Aggregation run:
-\begin{eqnarray*}
-    child & = & G^*(R_z, W_{11}, st, F_{41}) \\
-    parent & = & G^*(R_{z+1}, W_{11}, st, F_{41})
-  \end{eqnarray*}
-\begin{displaymath}
-z \in [1,6], G^* \in [Standard, Focal]
-\end{displaymath}
-\end{definition}
-
-The results can be found in Figure~\ref{fig:Zoom}. It can be seen that with an
-increase of the aggregation level the values increase. 
-If the aggregation level increases the number of cluster decreases. It can seen that
-small clusters are disappearing and some clusters are growing to big ones. From aggreagtion level~2 to
-aggreagtion level~3 there is no big change in the images of Focal $G^*$ which is consitent with our results.
-For the upward property, $G^*$ is always better than Focal
-$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
-reaches the same result as $G^*$ at aggregation level~6 . For the downward
-property, Focal $G^*$ leads to better results at aggregation level~6.
-
 \begin{figure*}[htp]
   \centering
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{
-      Aggregation levels computed from original raster (log scale)
-    }\\
-    \hline
-    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
-    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
-    \includegraphics[width=4.6em]{images/gen-rawdata-8}
-  \end{tabular}
-
-  \vspace{1em}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}\\
-
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}\\
-
-  \end{tabular}
-
-  \vspace{1em}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}\\
-
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-demo-zoom-focalgstar-8}\\
-  \end{tabular}
-
-  \vspace{2em}
-  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
-
-  \caption{
-    This image shows all aggregation levels for G* and Focal G* together 
-    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
-  }
-  \label{fig:Zoom}
-\end{figure*}
-
-\subsection{Blur}
-We also made an example for the variation of the weight size W.
-Blur is a slice plane through our three dimensional space. 
-W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
-\begin{definition} Blur run:
-\begin{eqnarray*}
-    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_{41}) \\
-    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_{41})
-  \end{eqnarray*}
-\begin{displaymath}
-i \in [0,11], G^* \in [Standard, Focal]
-\end{displaymath}
-\end{definition}
-The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
-shown in the first row, with increasing size. The 2nd and 4th row show how
-$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
-weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
-increase of the weight size leads in general to better results for $G^*$.
-Also it can bee seen that for focal $G^*$ the clusters are more distributed over the raster.
-
-\begin{figure*}[htp]
-  \centering
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
-    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
-  \end{tabular}
 
@@
 
-  \vspace{1em}
-  \begin{tabular}{cccccccc}
-    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
-    \hline
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}\\
-
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-1}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-2}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-3}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-4}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-5}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-6}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-7}&
-    \includegraphics[width=4.6em]{images/gen-demo-blur-focalgstar-8}\\
-  \end{tabular}
-
-  \vspace{2em}
-  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}
-  \hspace{1em}
-  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
-
   \caption{
@@
 
-\section{Results and Discussion}
-
-% Focal size  
-%	Increase of focal size leads to better results in the upward property
-% 	Standard deviation decrease with higher focal size 
-%	No standard deviation af F 17x17 because of missing clusters
-%	The downward property reaches its maximum at 65x65
-%
-%	Conclusion: F should be around 65x65 or higher
-\subsection{Impact of study area}
-The first parameter we want to isolate is the size of the study area. This enables us to discuss the optimal size of the study area for the given research/decision question. 
-To do so, we have to fix the focal size F and use it as the x-axis and plot the 
-mean value as well as the mean +/- the standard deviations of the SoH for all 
-other parameter combinations as the y-axis.
-In this scenario, only the Focal $G^*$ can produce varied results as the standard $G^*$ has by definition a fixed study area by always using the total size of the study area. 
-In Figure~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shown for $G^*$ and 
-Focal $G^*$.
-Higher values indicate that the hot spots found are more stable. 
-The \SOHUP in Figure~\ref{fig:fUp} growth with an increase of the focal size.
-It can see that an increase of the focal size leads to better results for \SOHUP. 
-With a higher focal size you can see that the dotted line, which represent the standard deviation, is getting smaller.
-This indicates that an increase in the size of the study area does not only lead to an overall increase of stability but also that the it reduces the volatility of the variations in other parameters.
-When F and W have similar size, there are no clusters. Because the values have no much variation. 
-\SOHDOWN (Figure ~\ref{fig:fDown}) shows a different picture then the \SOHUP.
-It reaches its maximum SoH for a focal size F of 65x65 in our evaluation set. 
-The standard deviation is not decreasing with an increase of the 
-focal size.
-
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{SoH up for focal size}
-    \includegraphics[width=\linewidth]{images/gen-focal-1}
-    \label{fig:fUp}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{SoH down for focal size}
-    \includegraphics[width=\linewidth]{images/gen-focal-2}
-    \label{fig:fDown}
-  \end{subfigure}
-  \caption{SoH for focal matrix size}
-  \label{fig:SoHFocal}
-\end{figure}
-
-%
-% Weight size
-%	Increase of weight leads to increase of downward property
-%	Small break downs for G* for upward and downward property
-%	For the upward property Focal G* is better than G*
-%
-%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
-\subsection{Impact of Neighbourhood size}
-Next, we want to isolate the effect of the neighbourhood size by fixing the weight matrix size W 
-and using it as x-axis. With the impact of the weight matrix W we gain information on how far the 
-interconnectness is between different points as indicated in \cite{Getis.1992}. 
-The results for the weight matrix can be seen in figure ~\ref{fig:wUp} for \SOHUP and figure ~\ref{fig:wDown} for \SOHDOWN.
-Here it can be seen that in general for both evaluations metrics as well as the different hot spot methods 
-an increase in the size of the weight matrix W leads to more stable results as well as that the Focal $G^*$ 
-matrix is slightly more stable in most cases for the mean values. 
-An interesting phenomena is the dip in stability for the standard $G^*$ for the value of 39. Despite our 
-effort we could not determine the reason behind this result, as no overall trend could be extracted.
-The standard deviation shows similar no particular trend, but for the values above 37 is increasing. 
-We assume that the reason behind this effect is the inclusion of the water near Manhattan, which leads to a stronger differentiation between areas near water and areas more in the inner city.
-by increasing the weight matrix, the number of points which are influenced increase in number.
-The other parameter can regulate this impact and therefore the variance is stronger.
-
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{SoH up for weight size}
-    \includegraphics[width=\linewidth]{images/gen-weight-1}
-    \label{fig:wUp}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{SoH down for weight size}
-    \includegraphics[width=\linewidth]{images/gen-weight-2}
-    \label{fig:wDown}
-  \end{subfigure}
-  \caption{SoH for weight size}
-  \label{fig:SoHWeight}
-\end{figure}
-%
-% Zoom
-%	G* alwas better than Focal G* for upward and downward property
-%	Focal G* has different focal sizes because zoom is compared
-%	At zoom level 4 G* increase much more than Focal G*
-%
-%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
-%	influence on the value
-\subsection{Impact of Aggregation level}
-Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. 
-We fix the aggregation and use it as x-axis. This allows us to examine the impact
-the resolution of a data set has on the results and allow us indirectly to reduce the 
-computational effort on future computations by using the maximal aggregation as useful.
-The results can seen in Figure~\ref{fig:SoHZoom}.
-First, we can see that for the aggregation level, in contrast to previous 
-results, the standard $G^*$ seems to be more stable.
-
-For the \SOHUP there is a huge increase between aggregation level 4 and 5. This increase can't be seen for \SOHDOWN.
-One can see that $G^*$ is always better than Focal $G^*$. 
-This could be beacause the target area of Focal $G^*$ increases with every aggregation step.
-
-\begin{figure}[htp]
-  \begin{subfigure}{\linewidth}
-    \caption{SoH up for focal size}
-    \includegraphics[width=\linewidth]{images/gen-aggregation-1}
-    \label{fig:zUp}
-  \end{subfigure}
-  \hspace{1em}
-  \begin{subfigure}{\linewidth}
-    \caption{SoH down for focal size}
-    \includegraphics[width=\linewidth]{images/gen-aggregation-2}
-    \label{fig:zDown}
-  \end{subfigure}
-  \caption{SoH for focal size}
-  \label{fig:SoHZoom}
-\end{figure}
-
-\section{Conclusions and Future Work} \label{sec:Conclusion}
-In this work we examined the influence of different parameter on the stability
-of hot spot analysis on the basis of the Getis-Ord and Focal Getis-Ord
-statistic. We validated our results with the use of the SoH metric on a well
-known real world data set to ensure external validity and easy replication.
-Based on the result we can show several insights, given the restrictions of this
-work, for future use of hot spot analysis. First, the greater the area size, the
-more stable the results seem to be. The same relation seem to be given for the
-size of the weight matrix. The greater the comparable area, the more stable are
-the results. Given the study are, the focal range should be at least be a size
-of 65x65 tiles, to have a good trade-off between \SOHUP and \SOHDOWN. In the
-case of the aggregation level, the stability does not seem to be impacted in the
-case of the Focal $G^*$, but for the standard $G^*$ statistic we see an increase
-in stability for higher aggregation levels. We assume that the high aggregation
-of data and the inherent increase of examined area reduce the impact of
-outliers, but reduce the potential to differentiate. The worse results for the
-Focal $G^*$ statistic compared to the $G^*$ statistic are most likely a result
-of the increased focus on a smaller region. A more in depth look at the
-interaction between focal size and aggregation level would be an interesting
-question for the future, but this is beyond the scope of this work.
-
-With this work, we made a step further to the optimal parametrisation for $G^*$ 
-and Focal $G^*$.
-Our results indicate that the parametrization for $G^*$ and Focal $G^*$ besides 
-what is defined as parent and child has a huge impact on the
-stability of hotspots. We can see the increase of up to 0.6 \SOHUP for e.g. the focal matrix size.
-This emphasizes the importance of a metric for the stability of hotspots.
-But this work also shows the shortcomings of the existing metric, as the trade-off between \SOHUP and \SOHDOWN is not yet fully explored and should be the focus of future work.
-Another interesting field for future research is the stability of spatio-temporal hot spots and their different parametrizations.
-As $G^*$ is often applied with regard to temporal impacts, the efficient computation of the focal $G^*$ for spatio-temporal and the impact on stability is the second main path for future research.
-We evaluated our data on the aggregate of a single month, but one could assume 
-that during the lunchtime there will be hotspots at restaurants and they are 
-not 
-consistent with the hotspots over one month. Therefore the impact of time on 
-the results is important and could also influence the metric for stability in 
-profound ways. As in the example, the question is, how fine grained should the 
-temporal clustering be and when is the result unstable? 
-This leads to the final future work: To which hot spots should the comparison 
-be made for the metric? In the current state, only the next parametrization is 
-compared due to the high computational complexity. How the comparison of hot 
-spots should be carried out and how many different comparisons have to be used 
-is another quite interesting research question.
-
-\section{Acknowledgements}
-This work is part of the research project BigGIS (reference number: 01IS14012)
-funded by the Federal Ministry of Education and Research (BMBF) within the
-frame of the programme "Management and Analysis of Big Data" in "ICT 2020 --
-Research for Innovations".
-%
-\noindent R-packages used: \verb|raster|~\cite{cran:raster}, 
-\verb|knitr|~\cite{cran:knitr}, %% Please use bibtex,
-
 \bibliography{references}

### 2018-05-24 Workshop_GIScience_BigData_Vision.tex
paper name changed

@@
 
-A framework for evacuation hotspot detection after large scale disasters using location data from smartphones: case study of Kumamoto earthquake \cite {Yabe:2016:FEH:2996913.2997014}
+A framework for evacuation hotspot detection after large scale disasters using location data from smartphones: case study of Kumamoto earthquake \cite {Yabe:2016:FEH:2996913.2997014} :
 
